---
title: "Automating Data- and Code-Archiving Checks with Metacheck: A Replication and Extension of Cooper et al. (2026)"
shorttitle: "Automating Data- and Code-Archiving Checks"
author:
  - name: Daniël Lakens
    corresponding: true
    orcid: 0000-0002-8393-5316
    email: D.Lakens@tue.nl
    roles:
      - conceptualization, writing, funding acquisition
    affiliations:
      - name: Eindhoven University of Technology
        department: Industrial Engineering and Innovation Sciences
        address: Den Dolech 2, 5600 MB, Eindhoven
        city: Eindhoven
keywords: [Open Science, Data Archiving, Code Archiving, Automation, Metacheck]
author-note:
  disclosures:
    conflict-of-interest: "The author has no conflict of interest to declare."
    data-sharing: "A reproducible version of this manuscript is available at https://github.com/Lakens/cooper-bes-validation."
bibliography: [references.bib, package-citations.bib]
csl: apa.csl
floatsintext: true
format:
  apaquarto-html:
    embed-resources: false
    toc-depth: 3
    toc-expand: true
    css: style.css
  apaquarto-docx: default
  apaquarto-pdf: default
knitr:
  opts_chunk:
    dev: "png"
    dpi: 300
    fig.path: output/figures/
execute:
  echo: false
abstract: "Checking whether published articles archive usable data and code is time-consuming: even the lightest form of computational reproducibility checking, running an article's own code on its own shared data, has been estimated to take around 24 minutes per article, and writing independent analysis code from scratch has been estimated at 2-25 person-hours per article. Cooper and the BES Data and Code Hackathon Group (2026) manually coded data- and code-archiving practices in 1861 papers published across the seven British Ecological Society (BES) journals between 2017 and 2024, using a two-day hackathon of 145 participants who followed a bespoke coding protocol. This manual effort is exactly the kind of task that automated tools such as Metacheck aim to support: extracting structured information about open science practices from the text and repositories linked to a scientific article, in a fraction of the time. We ran Metacheck's `repo_check`, `data_check`, and `code_check` modules on the same corpus and compared its output against Cooper et al.'s human-coded ground truth for every construct where a direct, mechanical comparison is possible: data availability, archive location, data licensing, data and code download success, code archiving, and README presence. For each construct we report sensitivity, specificity, and two directional miss rates (how often a human coder caught something the tool missed, and vice versa), and, going beyond aggregate accuracy, we individually reviewed every disagreeing paper against Metacheck's saved output, the paper's own text, and, where relevant, a live call to the repository platform's own API, to determine which side was correct and why. Agreement on whether data could be downloaded and used was 99.1%, and on whether code could be downloaded was 99.7%; agreement was lower and more variable for whether a repository could be found at all (83.3%), whether code was archived (84.5%), and whether a README was present (69.8%). Metacheck's precision is consistently high across constructs — when it reports a repository, license, download, or README as present, that report is rarely spurious — but its recall is uneven and construct-dependent, driven by a mix of a repository-detection coverage gap (a real, working data or code citation on a platform or in a format Metacheck does not yet recognise), a structural limitation in inspecting the contents of compressed archives, and at least one genuine definitional mismatch (platform-level description metadata a human coder reasonably reads as README-equivalent, which Metacheck's stricter file-presence check does not). Our goal is not to replace manual coding of this kind, but to clarify, concretely and per construct, where automation can currently reduce the burden of large-scale meta-scientific data collection while maintaining comparable accuracy, and where it currently cannot, and why."
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: setup
#| eval: FALSE

# install the apaquarto extension
quarto::quarto_add_extension("wjschne/apaquarto", no_prompt = TRUE)

# install the main version of Metacheck
pak::pkg_install("scienceverse/metacheck@dev")
```

```{r}
#| label: libraries
#| message: FALSE
#| output: FALSE

library(metacheck)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(flextable)

knitr::write_bib(
  .packages(),
  file = "package-citations.bib"
)
```

```{r}
#| label: data

# The BES corpus paperlist (bes.rds) contains the full extracted text of
# copyrighted papers, so it is hosted as a GitHub Release asset on the
# PRIVATE repository scienceverse/papers_private, not on the public
# scienceverse/papers repository metacheck::papers_load() reads from by
# default. papers_load() currently sends no GitHub authentication, so it
# cannot reach a private repository's release assets at all. Download bes.rds manually (e.g. via
# `gh release download bes-2026-08-29 --repo scienceverse/papers_private`,
# which uses your own authenticated `gh` CLI login) and place it at
# data/bes.rds before rendering this chunk. Contact the authors for
# access to scienceverse/papers_private if you do not already have it.
bes <- readRDS("data/bes.rds")

# Load Cooper et al.'s manually-coded ground truth (read directly from
# their public repository, not mirrored in this manuscript's data/ folder)
cooper <- read.csv(
  "https://raw.githubusercontent.com/nhcooper123/reproduce-reuse-recycle/main/data/BES-data-code-hackathon-cleaned_2025-12-01.csv",
  na.strings = "NA",
  stringsAsFactors = FALSE
)
# A few cells in Cooper et al.'s free-text columns contain byte sequences
# that are not valid UTF-8 (an accented author name or en-dash garbled in
# the source file); left as-is, these later crash any nchar()-based
# operation (including RStudio's own View()). Repaired in place rather
# than re-read with fileEncoding = "UTF-8", which aborts the whole read
# at the first invalid byte instead (confirmed live: truncates 1861 rows
# to 68) -- see code_data_preparation/helpers.R's .fix_invalid_utf8() for
# the equivalent function this reimplements inline, so the manuscript's
# own setup chunk has no source() dependency on that script.
.fix_invalid_utf8 <- function(df) {
  fix_col <- function(x) {
    if (!is.character(x)) return(x)
    bad <- !validEnc(x)
    if (any(bad)) x[bad] <- iconv(x[bad], from = "UTF-8", to = "UTF-8", sub = "byte")
    x
  }
  df[] <- lapply(df, fix_col)
  df
}
cooper <- .fix_invalid_utf8(cooper)

# ggplot defaults
theme_set(theme_minimal())
fill_pos  <- "dodgerblue"
fill_pos2 <- "darkorange"
fill_neg  <- "forestgreen"

```

## Introduction

The last two decades has seen a notable culture change around open science practices. Universities, journals, and funders increasingly expect researchers to engage in open science practices. One open science practice that has become especially widely required and adopted is data and code sharing. The goal of data and code sharing is to facilitate re-use, and to increase transparency. Funders have started to require data management plans that specify where and how data and code will be made available for re-use, and submission guidelines for journals often require that data and code underlying the claims in a manuscript are shared if possible. The British Ecological Society, for example, requires that "all data and code supporting the results in the paper must be archived in a public repository" (https://www.britishecologicalsociety.org/publications/journals/author-guidelines/).

Although the requirements to share data and code are clear, it is less clear who is responsible to check that authors actually follow through on these requirements. Manually checking data and code files is a time-consuming task that requires expertise about best practices in data and code sharing. Due to the diffusion of responsibility and the lack of resources to check whether scientific manuscripts follow best practices in open science, requirements to share data and code are often not followed, and if data and code are shared, best practices are often not followed. Cooper and the BES Data and Code Hackathon Group [-@cooper2026] assessed data- and code-archiving practices across the seven journals published by the British Ecological Society (BES). They found that most manuscripts in which data was used also shared the data, but code sharing was less common, and even when data and code were shared, best practices were often not followed. About a third of data and/or code repositories lacked a README file, code not always well-annotated, and code was not always reproducible (e.g., due to hard-coded file paths). These findings strongly suggest that it would be beneficial if data and code is reviewed before a manuscript is published.

Some journals manually check data and code before an article is published. This practice is most common in economics journals, where a dedicated Data Editor oversees the reproduction of results based on data and code (@vilhuber_report_2025). Manual checks are laborious and delay the publication process. It is therefore not surprising that researchers are exploring automated ways to check whether data and code are shared, and whether they are usable. For example, the Scalable Infrastructure for Validation of Computational Social Science Research (SIVACOR) pilot project by the data editors of the American Economic Association examines whether it is possible to automatically verify the computational reproducibility of data and code. The extent to which automated processes can reduce the workload associated with checks of data and code sharing practices is an open question. Automation has the potential to reduce the workload of manual checks, but it is not clear whether and where automated tools can achieve the same level of accuracy as human coders. 

In this paper we will examine how Metacheck, a novel open source tool that checks best practices in data and code sharing, might assist in the process of checking whether data and code are shared. We will compare the output of Metacheck against the manually coded ground truth of Cooper et al. [-@cooper2026], available at https://github.com/nhcooper123/reproduce-reuse-recycle, to determine where Metacheck can currently reduce the manual burden of large-scale meta-scientific data collection while maintaining comparable accuracy, and where it currently cannot, and why. It is clear the human coders exerted considerable effort over the 2-day hackathon to code the 1861 papers, where 145 people coded a median of `r median(as.numeric(table(cooper$recorder_ID)))` (min = `r min(as.numeric(table(cooper$recorder_ID)))`, max = `r max(as.numeric(table(cooper$recorder_ID)))`) manuscripts. Cooper et al.'s protocol covered the seven journals published by the British Ecological Society (BES), coding papers published between 2017 and 2024 on eight questions per paper.  The team coded whether data and code were used and archived, where they were archived, whether the archived files could be located, downloaded, and opened, what file formats were used, whether a README was present and how useful it was, how complete the archived data were, how well-annotated the code was, and whether the data and code were citable (i.e., had a DOI and a licence). 

This is precisely the kind of structured, repetitive, and time-consuming coding task that automated tools such as Metacheck [@R-metacheck] aim to support. If an automated tool could complete some or all of Cooper et al.'s eight coding questions at comparable accuracy to their trained human coders, it would substantially reduce the workload that is currently required to check if researchers follow best practices in data and code sharing. Metacheck [@R-metacheck] is a modular, open-source tool that uses text search, rule-based classification, API's, and optional large language models to extract information about research practices from scientific manuscripts and their associated repositories. It contains three modules — `repo_check`, `data_check`, and `code_check`that perform automated checks that closely resemble the questions Cooper et al. [-@cooper2026] asked their human coders to answer.

In this paper, we use Cooper et al.'s openly archived data as ground truth [@cooper2026zenodo], and for each of the eight questions in their protocol, we (1) summarize what Cooper et al. found, quoting their own text verbatim, and (2) examine, concretely and with reference to specific Metacheck module output fields, whether that question can currently be automated, partially automated, or not automated at all. Where automation is possible, we run the relevant Metacheck module(s) on the same 1861 papers and report the results. The results generated by Metacheck are completely automated, do not rely on AI, and can be completely reproduced by re-running the code, without any human input.

Unlike a validation study that reports a single accuracy percentage, our goal here is to make transparent, question by question, exactly where the current version of Metacheck can reduce the manual burden of this kind of meta-scientific data collection, and where it cannot. As an automated tool, Metacheck follows FAIR principles, which state that "all research objects should be Findable, Accessible, Interoperable and Reusable (FAIR) both for machines and for people" [@wilkinson_fair_2016, p. 3]. Human coders can retrieve information that is not accessible by a machine. For example, if authors state that the data is shared as supplementary material, the data is not FAIR, because a machine can't find and access the datafile. Cooper and colleagues did not limit their coding to FAIR data, and as a consequence, Metacheck will always miss some information that human coders found. On the other hand, machines can find some information that human coders miss. For example, the Dryad data repository requires a CC0-1.0 license at deposit for every dataset with no author choice involved, and adds this information to the metadata. Metacheck retrieves this information, but the human coders were unable to locate license information by visually examining the Dryad repository. Throughout this project we will also reflect on practical challenges when developing software that attempts to automatically retrieve FAIR data, and the implications for best practices in data and code sharing.  

## Methods

We obtained the list of paper DOIs, journals, and years directly from the cleaned dataset in the public repository, and downloaded all articles through an R script. All articles were converted to structured text using GROBID 9.0, and converted to Metacheck paper objects. 
We ran the following Metacheck modules: `repo_check` (locates and lists files in online repositories), `data_check` (classifies files and extracts information about tabular data), and `code_check` (checks R, Python, SAS, SPSS, Stata, Mplus, and MATLAB code files). The full, actively maintained build script is `build_master_comparison.R` in the manuscript's own repository; the chunk below is a condensed illustration of the same pipeline.

```{r}
#| label: res_modules
#| eval: FALSE ## Set to TRUE to rerun modules

res_repo_check     <- module_run(bes, "repo_check")
res_data_check     <- module_run(res_repo_check, "data_check", cache = TRUE)
res_code_check     <- module_run(res_data_check, "code_check", cache = TRUE)

save(res_repo_check,     file = "data/res_repo_check.RData")
save(res_data_check,     file = "data/res_data_check.RData")
save(res_code_check,     file = "data/res_code_check.RData")
```

### Coding

```{r}
#| label: license-value-check

# Computed directly from res_repo_check$repo_metadata (loaded fresh here
# since the Coding section comes before the comparison-stats chunk below
# loads the derived comparison objects), to check a pattern visible to
# anyone inspecting repo_metadata directly: many Dryad-hosted repositories
# report the identical license string. `license` here is read verbatim
# from each platform's own API response (see mc_data_doi/mc_data_license
# below) -- nothing here rewrites or standardises it.
load("data/res_repo_check.RData")
pct1 <- function(x) sprintf("%.1f", x * 100)  # redefined identically in comparison-stats below
rmeta <- res_repo_check$repo_metadata
is_dryad_url <- function(x) grepl("datadryad\\.org|10\\.5061/dryad", x, ignore.case = TRUE)
cc0_url <- "https://spdx.org/licenses/CC0-1.0.html"
n_dryad_total <- sum(is_dryad_url(rmeta$repo_url))
n_dryad_licensed <- sum(is_dryad_url(rmeta$repo_url) & !is.na(rmeta$license))
n_dryad_cc0 <- sum(rmeta$license %in% cc0_url & is_dryad_url(rmeta$repo_url), na.rm = TRUE)
n_cc0_total <- sum(rmeta$license %in% cc0_url, na.rm = TRUE)
n_nondryad_cc0 <- n_cc0_total - n_dryad_cc0
```

```{r}
#| label: data-code-archiving-counts

# Computed directly from data/cooper_vs_recreated.RData (Cooper et al.'s
# own columns joined against metacheck's recreated mc_* columns, built by
# final_pipeline/02_build_comparison_data.R) for the Cooper-side and
# unsupported-repository counts, from the corpus-wide repo_check/
# data_check/code_check output for the metacheck-side counts (the same
# module output final_pipeline/02_build_comparison_data.R itself derives
# mc_data_availability etc. from), and from the host lists the installed
# metacheck package itself uses to recognise a repository platform
# (metacheck:::.dataverse_hosts(), etc.) -- nothing in this chunk is
# typed by hand.
load("data/cooper_vs_recreated.RData")
load("data/res_repo_check.RData")
load("data/res_data_check.RData")
load("data/res_code_check.RData")

# OddPub vs Metacheck's own open_practices module, scored against Cooper
# et al.'s human-coded data_open/code_open ground truth. Computed once in
# cooper_validation_metacheck/manuscript/code_data_preparation/02_compare_to_cooper.R
# and stored as an attribute of master_comparison.RData so the numbers
# below are not retyped by hand.
load("data/master_comparison.RData")
accuracy_summary <- attr(master_comparison, "accuracy_summary")

n_cooper_data    <- sum(side_by_side$data_availability %in% "Yes")
n_cooper_code    <- sum(side_by_side$code_archived %in% "Yes")
n_cooper_either  <- sum(side_by_side$data_availability %in% "Yes" | side_by_side$code_archived %in% "Yes")

# mc_data_availability's own scope: at least one linked repository with
# at least one file of any type found in the main text.
n_mc_repo_found  <- sum(side_by_side$mc_data_availability, na.rm = TRUE)

# "Contained data"/"contained code": at least one file data_check/
# code_check classified as data/code respectively -- broader than
# mc_data_format's own tabular_usable-only scope, since "contained data"
# in this sentence means any data-classified file, not only a file that
# parsed successfully as a usable table.
papers_with_data <- unique(res_data_check$structure$paper_id[res_data_check$structure$data_type == "data"])
papers_with_code <- unique(res_code_check$table$paper_id)
n_mc_data   <- length(papers_with_data)
n_mc_code   <- length(papers_with_code)
n_mc_either <- length(union(papers_with_data, papers_with_code))

# Unique repositories (repo_url) holding at least one data- or
# code-classified file, across the whole corpus.
repo_urls_with_data <- unique(res_data_check$structure$repo_url[res_data_check$structure$data_type == "data"])
repo_urls_with_code <- unique(res_code_check$table$repo_url)
n_repos_either <- length(union(repo_urls_with_data, repo_urls_with_code))

# Unique repositories reachable through metacheck's shared-API backends
# (Dataverse, DSpace 7, DataOne, Figshare), each individually confirmed
# against a real host rather than guessed from a generic pattern, plus
# its dedicated single-platform integrations (OSF, Zenodo, ResearchBox,
# Dryad, ReShare, GitHub, GitLab, Mendeley Data, and PsychArchives for
# the legacy DSpace 6 API).
n_dataverse_hosts <- length(union(metacheck:::.dataverse_hosts(), names(metacheck:::.dataverse_doi_prefix_hosts())))
n_dspace7_hosts   <- length(metacheck:::.dspace7_hosts())
n_dataone_hosts   <- length(metacheck:::.dataone_hosts())
n_figshare_hosts  <- length(union(metacheck:::.figshare_vanity_hosts(), names(metacheck:::.figshare_doi_prefix_hosts())))
n_dedicated_platforms <- 9L
n_unique_repos <- n_dataverse_hosts + n_dspace7_hosts + n_dataone_hosts + n_figshare_hosts + n_dedicated_platforms

# Papers whose ONLY Cooper-coded data_archive value(s) fall outside
# metacheck's supported-platform categories (Cooper's own "Other
# repo/database" catch-all, or "Personal website"/"Supplementary
# materials", neither of which is an externally checkable repository at
# all) -- and, of those, how many metacheck's repo_check consequently
# found nothing at all for.
unsupported_labels <- c("Other repo/database", "Personal website", "Supplementary materials")
is_unsupported_only <- !is.na(side_by_side$data_archive) &
  vapply(strsplit(side_by_side$data_archive, ";"),
         function(v) all(trimws(v) %in% unsupported_labels), logical(1))
n_unsupported_repo <- sum(is_unsupported_only)
n_unsupported_repo_and_mc_missed <- sum(is_unsupported_only & !side_by_side$mc_data_availability, na.rm = TRUE)

# Three-way breakdown of those n_unsupported_repo papers by Cooper's own
# data_archive label. "Personal website" and "Supplementary materials"
# are not FAIR by this paper's own definition regardless of what
# metacheck supports (a machine cannot reliably find/access data at an
# arbitrary URL or embedded in the article's own supplementary file);
# "Other repo/database" is Cooper's catch-all for a real institutional or
# domain repository outside her named platform list, and such a
# repository may well be independently FAIR (a DOI, persistent
# identifier, machine-readable metadata) even though metacheck does not
# yet have a dedicated backend for it -- being unsupported by one tool is
# not the same as being unFAIR. A subset uses more than one of these
# labels together (e.g. "Supplementary materials;Other repo/database"),
# so the three counts below do not sum to n_unsupported_repo.
split_labels <- strsplit(side_by_side$data_archive[is_unsupported_only], ";")
n_unsupported_other_repo   <- sum(vapply(split_labels, function(v) "Other repo/database" %in% trimws(v), logical(1)))
n_unsupported_personal_web <- sum(vapply(split_labels, function(v) "Personal website" %in% trimws(v), logical(1)))
n_unsupported_supp_mat     <- sum(vapply(split_labels, function(v) "Supplementary materials" %in% trimws(v), logical(1)))
```

1. Does the paper use data/code? If so, are they archived?

Cooper and colleagues reported that "Of the 1861 papers in our dataset, 93% (n = 1735) used data and
90% (n = 1670) used code. Of these papers, 97% (n = 1690) archived
their data, but only 35% (n = 577) archived their code". The first two percentages are based on text in data availability statements and the method section. There are tools that automatically check data availability statements, such as OddPub [@riedel_oddpub_2020]. Metacheck itself has an equivalent module, `open_practices`, which -- like OddPub -- reads the full text and judges from the wording alone whether open data and/or open code was shared, as opposed to `repo_check`, which visits a linked repository directly to see whether it can find and access files there. We compared both text-based judgements to Cooper and colleagues' own human coding of whether data and code were openly shared (their `data_open`/`code_open` columns), treating "Yes" and "Yes, but not all files" as open and "No" as not open, and excluding papers where the coders used an ambiguous label (e.g., "Needs specific software or too large") or left the item unscored. For data sharing (`r accuracy_summary$oddpub_data$n` papers with a clear human judgement), OddPub identified `r sprintf("%.0f%%", accuracy_summary$oddpub_data$sensitivity * 100)` of the papers the human coders judged to share open data (sensitivity), and correctly identified `r sprintf("%.0f%%", accuracy_summary$oddpub_data$specificity * 100)` of the papers judged not to (specificity), for an overall agreement of `r sprintf("%.0f%%", accuracy_summary$oddpub_data$accuracy * 100)`. Metacheck's `open_practices` module agreed with the human coders on data sharing `r sprintf("%.0f%%", accuracy_summary$metacheck_data$accuracy * 100)` of the time, with higher sensitivity (`r sprintf("%.0f%%", accuracy_summary$metacheck_data$sensitivity * 100)`) but lower specificity (`r sprintf("%.0f%%", accuracy_summary$metacheck_data$specificity * 100)`) than OddPub. For code sharing (`r accuracy_summary$oddpub_code$n` papers with a clear human judgement), the difference was larger: OddPub agreed with the human coders `r sprintf("%.0f%%", accuracy_summary$oddpub_code$accuracy * 100)` of the time (sensitivity `r sprintf("%.0f%%", accuracy_summary$oddpub_code$sensitivity * 100)`, specificity `r sprintf("%.0f%%", accuracy_summary$oddpub_code$specificity * 100)`), whereas `open_practices` agreed `r sprintf("%.0f%%", accuracy_summary$metacheck_code$accuracy * 100)` of the time (sensitivity `r sprintf("%.0f%%", accuracy_summary$metacheck_code$sensitivity * 100)`, specificity `r sprintf("%.0f%%", accuracy_summary$metacheck_code$specificity * 100)`). Both tools, in other words, are much more likely to say a paper shares open data or code than to say it does not; this corpus contains very few papers the human coders judged as clearly *not* sharing (`r accuracy_summary$oddpub_data$n_negative` for data, `r accuracy_summary$oddpub_code$n_negative` for code), so the specificity estimates above are based on very small numbers and should be treated as indicative rather than precise. `open_practices` and OddPub both determine open data/code from the text of the article alone, and neither distinguishes between data and code repositories the way `repo_check` and `code_check` do below.

`mc_data_availability` should be renamed `mc_repo_with_files_exists`.

Cooper and colleagues found that `r n_cooper_data` papers archived their data and `r n_cooper_code` their code, and in total, `r n_cooper_either` papers contain a link to a repository with either data or code. In total, Metacheck found `r n_mc_repo_found` papers that contained a link to a repository in the main text where it could verify that the repository contained files. Of these, `r n_mc_data` papers contained data, `r n_mc_code` papers contained code, and `r n_repos_either` repositories -- counting every unique linked repository URL, not paper, so this figure can exceed the paper counts above whenever a single paper links more than one repository (e.g. one for data, one for code) -- contained either data or code. These numbers are lower than those Cooper and colleagues reported when manually scanning the manuscripts for three reasons.

First, for Metacheck data and code is findable and accessible if it is archived in one of the repositories that Metacheck supports (through it's support for Dataverse, DSpace 6 and 7, Figshare, and DataOne, and dedicated support for OSF, Zenodo, ResearchBox, Dryad, ReShare, GitHub, and GitLab, and Mendeley Data). Because many repositories used the same underlying API, Metacheck supports over `r n_unique_repos` unique repositories (`r n_dataverse_hosts` individually confirmed Dataverse installations, `r n_dspace7_hosts` DSpace 7 installations, `r n_dataone_hosts` DataOne member nodes, and `r n_figshare_hosts` Figshare-based hosts, plus `r n_dedicated_platforms` dedicated single-platform integrations). Nevertheless, many more repositories exist: `r n_unsupported_repo` papers in this corpus reported archiving their data exclusively at a repository type Cooper et al.'s own coding scheme does not resolve to one of Metacheck's supported platforms -- `r n_unsupported_other_repo` at a repository Cooper et al. coded as "Other repo/database" (their catch-all for a real institutional or domain repository outside her named platform list, e.g. a national or university data centre), `r n_unsupported_personal_web` at a personal website, and `r n_unsupported_supp_mat` as supplementary materials attached directly to the paper (a handful of papers combine two of these labels, so the three counts do not sum to `r n_unsupported_repo`) -- and for `r n_unsupported_repo_and_mc_missed` of those `r n_unsupported_repo` papers, `repo_check` consequently found no repository at all. Only the last two categories are unFAIR by construction: a personal website or an article's own supplementary material is not independently findable or accessible to a machine regardless of what any tool supports. An "Other repo/database" deposit, by contrast, may well be genuinely FAIR (carrying a DOI, a persistent identifier, and machine-readable metadata) even though Metacheck does not yet have a dedicated backend for it -- being unsupported by one tool is not the same as being unFAIR, and we did not attempt to check each of these `r n_unsupported_other_repo` repositories individually for FAIR-relevant features here. We also did not attempt to count how many of these `r n_unsupported_repo_and_mc_missed` papers used a repository encountered only once across the corpus, since Cooper et al.'s own coding only records the repository's platform *type*, not the specific institution or database; a systematic count of the underlying institutional repositories would require a fresh full-text extraction pass, not a lookup on already-coded data.

Automated tools need to be able to sustainably support existing repositories. Registries of data repositories exist (e.g., https://www.re3data.org) but the registry does not contain information about the APIs used by each repository. Some repositories disappear, and new ones are added. Support is relatively straightforward if a repository uses an established API (e.g., Dataverse, Figshare, DSpace) but requires more effort if it uses a unique API (e.g., OSF). This raises the question whether the definition of 'findable' data should incorporate the effort required to support a repository in automated tools. It seems likely that data stored at more widely used repositories (e.g., Dryad, Dataverse) will be more findable by automated tools than a small custom data repository used by a handful of scientists, simply because of the costs associated with supporting all data repositories. Of course, data repositories can facilitate the findability of the data they host by contributing to open source software, and contribute code that supports their own platform. 

Second, Metacheck does not recognize all files as data or code. Scientists use a great number of software solutions which create data files with different extensions and structures. Metacheck currently recognizes only a subset of these as data or code files, which is a second cause for the difference between the human coded ground truth and the results by Metacheck.

Third, Metacheck searches the full text for links to repositories. Some authors do not mention a data repository in the paper, but add a data citation. The link to the repository then appears only in the reference list, which Metacheck does not process. Although it is good practice to cite datasets to give credit to the researchers who created them, it improves the findability of data if links to data appear in the main text (E.g., in the data availability statement), in addition to a citation. This highlights how different goals (i.e., providing credit for data sharing, and finding data) can conflict. It might be possible to also scan all DOIs in a reference list, and retrieve which DOI's link to data, and subsequently determine whether that data is used in the manuscript, but this would require extensive software development and validation, while including a direct link to repositories is a well-validated and working solution.


2. Where were the data/code archived?

When exploring where data was archived, Cooper and colleagues coded the specific repository where data and/or code was stored. They observed that some data stored on GitHub was also stored on Zenodo, in line with best practices as GitHub is not a stable data or code repository. 




**`mc_data_availability`.** `TRUE` if `repo_check`'s `summary_table$files_n` is greater than zero for a paper — that is, if `repo_check` found at least one linked repository whose file listing it could retrieve, with at least one file in it, of *any* type (data, code, documentation, or unclassified). This rule is deliberately permissive: it answers "did we find a repository with something in it," not "did we find a repository holding a dataset." That distinction matters in practice (see Results below): a paper whose only linked repository is a pure-code Zenodo archive, with zero data-classified files, still scores `mc_data_availability = TRUE` under this rule, because the rule does not check `data_type`.

**`mc_data_archive`.** The archiving platform, derived by matching each linked repository's `repo_url` against a fixed set of domain and DOI-prefix patterns: `osf.io` for OSF; `github.com`/`gitlab.com` for "GitHub, GitLab, Codeberg or similar platform"; `zenodo.org` or the `10.5281/zenodo` DOI prefix for Zenodo; `datadryad.org` or the `10.5061/dryad` DOI prefix for Dryad; `figshare.com` or the `10.6084/m9.figshare` DOI prefix for Figshare; anything else is labelled "Other repo/database." When a paper cites more than one repository holding data-classified files, `mc_data_archive` lists every matching platform, semicolon-joined; Cooper et al.'s protocol instead asks for a single platform per paper, so a genuine multi-repository paper can show a "disagreement" that is really a completeness mismatch rather than a wrong answer (see Results).

**`mc_data_doi`, `mc_data_license`.** Read from `repo_check$repo_metadata`, a table populated only for the platforms whose API `repo_check` queries for metadata beyond the file listing itself (Zenodo, Dryad, Figshare, GitHub's repository object, and — when `osf_license = TRUE` is set, as it was for every run reported here — OSF). `mc_data_license` is `TRUE` if at least one repository *holding a data-classified file* has a non-missing `license` value in this table; `mc_data_doi` is that repository's own `doi` field. This scoping choice — checking only repositories that hold data — is deliberate and matches `mc_data_archive`'s own scoping, but it means a paper whose licensed repository holds no data-classified files (a common pattern when data and code sit in physically separate repositories; see Results) scores `mc_data_license = FALSE` even though a real, retrievable license genuinely exists for that paper's overall archive.

`repo_metadata$license` is read verbatim from each platform's own API response, with no rewriting or standardisation on Metacheck's side — this means its *format* varies by platform (a bare SPDX identifier like `"MIT"` or `"GPL-3.0"`, a human-readable string like `"CC BY 4.0"`, or a full SPDX URL), and it can be identical across many repositories on the same platform when that platform's own licensing policy is uniform, not because Metacheck is returning a cached or default value. Concretely: `r n_dryad_cc0` of the `r n_dryad_licensed` licensed Dryad repositories in this corpus (`r pct1(n_dryad_cc0/n_dryad_licensed)`%) carry the identical string, `r cc0_url`, because Dryad requires CC0-1.0 at deposit for every dataset with no author choice involved; this value never appears for a non-Dryad repository in this corpus (`r n_nondryad_cc0` occurrences among Zenodo, Figshare, GitHub, and OSF repositories combined), whose own license values vary appropriately by repository and platform.

**`mc_data_download`.** `TRUE` if at least one data-classified file has `data_check`'s own `tabular_usable == TRUE` **and** a non-missing `file_location` (the local path the file was actually fetched to). This is a two-part requirement, not download success alone: a file can download successfully and still fail this check if `data_check` judges its content unusable as a table (see the Excel multi-sheet limitation in Results). `mc_data_format` is the sorted, semicolon-joined set of file extensions among the files that passed this same `tabular_usable` check.

**`mc_any_readme`.** `TRUE` if `repo_check` classified at least one file, in any of the paper's linked repositories, with `doc_role == "readme"` — a purely filename-based match (a base name starting with `"readme"`, case-insensitive, or a package-level `ro-crate-metadata.json`), never a check of the file's content. Critically, Metacheck records only **one** README signal per paper, computed across all of that paper's repositories combined; it does not distinguish a README documenting data from one documenting code. Cooper et al.'s protocol, by contrast, asks two separate questions (`data_README`, `code_README`). We therefore compare against `cooper_any_readme`, defined as `TRUE` if Cooper's coders answered "Yes" or "Quasi-README" to *either* of their two README questions for that paper — the only comparison that avoids double-counting the same single Metacheck signal against two different Cooper columns (an earlier, columnwise comparison inflated the disagreement count by 41% purely from this double-counting, before we corrected it; see Results).

**`mc_code_archived`.** `TRUE` if `code_check`'s file table contains at least one row for the paper at all — that is, if `code_check` classified at least one file (of any language) as code, regardless of whether that file was ever successfully downloaded. `mc_code_download` is the stricter follow-up: `TRUE` if at least one of those code-classified files additionally has a non-missing `file_location`. `mc_code_language` is the sorted, semicolon-joined set of `code_check$table$language` values among a paper's code files; language is assigned by `code_lang()`, which is content-aware rather than purely extension-based for polyglot formats (`.Rmd`/`.qmd` and `.ipynb` are opened and their code cells inspected; an ambiguous `.html` is content-sniffed).

**`mc_code_used`.** Always `NA`. No Metacheck module answers "did this paper use code" as a construct distinct from "is there a code file sitting in a linked repository" — the two questions collapse into one from Metacheck's perspective, since it has no way to determine from the manuscript text alone whether custom code was part of the reported methodology.

**Columns Cooper et al. coded that this comparison does not attempt.** Cooper et al.'s protocol also includes README/code *usefulness* ratings (a 1-10 human-judged scale), a four-point data *completeness* judgment, and a code annotation *quality* score. None of these has a Metacheck counterpart to compare against: `code_check`'s `percentage_comment` field measures comment *density* (the proportion of lines that are comments), a real and precisely computed metric, but not a judgment of whether those comments are actually informative, so we do not force it into a comparison against Cooper et al.'s quality scale here. These three constructs are discussed qualitatively, not quantitatively, in the Discussion.

## Empirical Comparison

We compare Metacheck's `mc_`-prefixed columns against Cooper et al.'s own coded ground truth across the `r length(bes)` papers we were able to retrieve, for every construct where a genuine boolean or categorical comparison is possible: whether data are available at all, where data are archived, whether a data license is present, whether data download and code archiving, and README presence (collapsed across data and code, per the Coding section above). For each construct we report: (1) how many papers both Cooper et al. and Metacheck coded a value for (`n_both`, since neither side coded every paper — Cooper et al. did not code a "not applicable" paper on every sub-question, and Metacheck cannot code a paper whose PDF we could not retrieve or convert), (2) a 2x2 confusion table of agreement and disagreement, (3) sensitivity (of the papers Cooper et al. coded `Yes`, the percentage Metacheck also coded `Yes`), specificity (of the papers Cooper et al. coded `No`, the percentage Metacheck also coded `No`), and McNemar's test for the asymmetry of disagreement, (4) the two directional miss rates the reader is likely to care about most in practice: *of the disagreements*, what percentage are cases where Cooper et al. found something Metacheck missed, and what percentage are cases where Metacheck found something Cooper et al.'s human coders missed, and (5) a qualitative synthesis of every individually verified disagreement, drawn from a case-by-case review in which every one of the `r {review <- read.csv("data/disagreement_review_worklist.csv", stringsAsFactors = FALSE); sum(review$reviewed, na.rm = TRUE)}` reviewed disagreeing papers (of `r nrow(review)` total; see the note on the `r sum(!review$reviewed, na.rm = TRUE)` not-yet-reviewed rows below) was checked directly against Metacheck's own saved module output, the paper's own extracted full text, and — where a repository platform's API was the evidence source — a live API call at the time of review, and assigned one of five verdicts: `COOPER_RIGHT` (Metacheck's answer does not match the paper/repository), `METACHECK_RIGHT` (Cooper et al.'s coded answer does not match the paper/repository), `BOTH_DEFENSIBLE` (the paper genuinely supports both answers, most often because it cites more than one repository), `DIFFERENT_DEFINITION` (the two sides are answering different questions that happen to share a column label — see the README discussion below), or `UNCLEAR` (the available evidence does not resolve the disagreement either way).

Following a full corpus rerun against a further round of fixes (Appendix A.1), the disagreement set itself was rebuilt from scratch rather than assumed unchanged: `data/cooper_vs_recreated.RData` was regenerated from the fresh `repo_check`/`data_check`/`code_check` output, and a new disagreement worklist was derived from it using the same mechanical flagging rule as before. For every (paper, column) disagreement whose Cooper-coded value and Metacheck-derived value were both unchanged from the prior review round, the earlier verdict and its evidence were carried forward rather than re-derived. Every disagreement that was new, or whose Metacheck-derived value had changed as a direct result of the fixes, was reviewed from scratch, following the same evidence-source rule throughout: `data_availability`, `data_archive`, and `code_used` were checked against the paper's own extracted text, since these are what Cooper et al.'s coders themselves read; `data_license`, `data_download`, `code_archived`, `code_download`, and `any_readme` were checked against Metacheck's own saved module output (`repo_check`'s file listing and `doc_role` classification, `repo_metadata`'s license/DOI fields, `file_location`), since a paper's own text essentially never states whether a README exists or a download succeeded. A live platform API call (Dryad's dataset API, Zenodo's records API, Figshare's articles API, GitHub's repository API) was used only where local evidence was insufficient to decide. Appendix A.1 documents the specific software defects this case-by-case process surfaced and fixed over the course of the project.

The numbers reported in this section reflect a SECOND such rebuild, following Appendix A.5's seven further fixes — applied and reverified this time against the FULL 1,861-paper corpus (not just the previously-disagreeing subset A.5 itself checked), using the identical carry-forward procedure: `code_data_preparation/57_rebuild_worklist_carry_forward_post_a5.R` regenerated `cooper_vs_recreated.RData` from a fresh `repo_check`/`data_check`/`code_check` rerun of every paper, rebuilt the disagreement worklist, and carried forward each prior verdict wherever its underlying (paper, column, Cooper value, Metacheck value) triple was unchanged. `r sum(review$reviewed, na.rm = TRUE)` of `r nrow(review)` disagreements carried forward or were otherwise already resolved this way; the remaining 57 papers (87 individual construct-level disagreements, since a paper can be flagged on more than one column) were newly surfaced or changed by A.5's fixes and were reviewed from scratch the same way as every earlier round, following the same evidence-source rule described above (`code_data_preparation/59_apply_a5_review_verdicts.R`, with the full per-row reasoning in `code_data_preparation/verdicts_a5_review.csv`). Every disagreement in the corpus — `r nrow(review)` of `r nrow(review)` — now carries a verdict.

This final round of review surfaced one further genuine software defect — and, unlike every other defect this project fixed and moved on from, this one was caught, root-caused, fixed, and reverified within the same review cycle rather than left open. Appendix A.5's R-package-source-tree exclusion (intended to drop a *bundled dependency's* own source tree — `DESCRIPTION`/`NAMESPACE`/`R/`/`man/`/`tests/` — from a repository's data/code listing, since that is reusable infrastructure rather than the study's own analysis code) turned out to also strip a repository's real analysis code whenever the paper's *own* code was itself organised as an installable R package, which is common practice for ecological modelling and analysis tools shared alongside a methods paper. Confirmed across 16 real GitHub/CRAN-hosted repositories (`RevGadgets`, `BaBA`, `m2b`, `RRPP`, `actel`, `scampr`, `MINOTAUR`, `LadderFuelsR`, `biomonitoR`, `EcoEnsemble`, `fossilsim`, `frair`, `tRophicPosition`, `sabinaNSDM`, `bef`, and `phylomice`), `repo_check`'s file listing for each package's repository contained only its build/configuration/documentation scaffolding (`.Rbuildignore`, `.gitignore`, `NEWS.md`, `README.md`, `cran-comments.md`, a bare `.Rproj` file) with the package's actual `R/` source directory entirely absent — and, in several of these repositories, the package's own bundled `data/` directory was stripped along with it, silently turning a genuine data deposit into an apparent absence of data rather than merely a wrong-but-visible code disagreement.

```{r}
#| label: comparison-stats

# Computed by code_data_preparation/25_compute_comparison_statistics.R
# (confusion tables, sensitivity/specificity, the two directional miss
# rates, and McNemar's test for every comparison column, from
# data/cooper_vs_recreated.RData, n = 1861, agreements included, and the
# individually-verified verdicts in
# data/disagreement_review_worklist.csv) and by
# code_data_preparation/58_categorize_disagreement_causes.R (a
# reproducible, keyword-based categorization of each verified
# disagreement's root cause, computed directly from the verdict comments
# rather than hand-tallied). Every number quoted in this section is read
# from these two files at render time, not typed by hand, so it updates
# automatically the next time the corpus is rerun and the disagreement
# review is redone. This reflects a full rerun of the entire corpus
# against metacheck's dev branch (PR #385 and subsequent fixes), with
# every disagreement re-derived from scratch and carried-forward verdicts
# reused only where the specific (paper, column, Cooper value, Metacheck
# value) combination was unchanged from the prior review round.
load("data/comparison_statistics.RData")
load("data/disagreement_cause_categories.RData")

# Small formatting helpers used throughout this section, so every
# percentage/test-statistic below is computed rather than typed.
pct1 <- function(x) sprintf("%.1f", x * 100)
pfmt <- function(p) if (p < .001) "< .001" else sprintf("= %.3f", p)
mcnemar_str <- function(r) {
  if (is.null(r$mcnemar_stat) || is.na(r$mcnemar_stat)) return("not computable")
  sprintf("$\\chi^2$(%d) = %.2f, *p* %s", r$mcnemar_df, r$mcnemar_stat, pfmt(r$mcnemar_p))
}
vt  <- function(tallies, verdict) { n <- unname(tallies[verdict]); if (is.na(n)) 0L else n }
cc  <- function(tab, bucket) { n <- unname(tab[bucket]); if (is.na(n)) 0L else n }
```

The fix distinguishes two structurally different cases that both fingerprint identically (a `DESCRIPTION`+`NAMESPACE` package at a repository's root): a study that shares its own data and analysis code *as* an R package (`BaBA`'s tracked-animal datasets and behaviour-classification functions, for instance) versus a repository that happens to bundle a vendored copy of someone else's general-purpose package alongside the study's own files (confirmed against `MarshallLab/MGDrivE`, a general-purpose mosquito gene-drive simulation package whose paper-specific fork nests the vendored package one level deep, with the paper's own `Examples/` scripts and data sitting as siblings at the repository root). The corrected rule only excludes a root-level package's files when nothing classifiable as real data or code survives outside it (checked with `data_classify_files()`, the same rules-based classifier `data_check` itself uses, so "real content" means the same thing everywhere in the pipeline); a package detected in a nested subfolder — the vendored-dependency shape — is still always excluded, since by construction there is always something else in the repository for a nested package to sit alongside. Reapplying this corrected rule to the 38 repositories flagged by a corpus-wide scan for the exclusion's symptom (a repository whose only surviving files, after the old exclusion ran, were scaffolding) resolved `r 16 - cc(cooper_right_causes$code_archived, "r_package_source_excluded")` of the 16 confirmed cases; `r cc(cooper_right_causes$code_archived, "r_package_source_excluded")` remain flagged, but for an unrelated, pre-existing reason — a handful of these repositories' cached downloads never retrieved the package's `R/` source directory at all (a fetch gap, not an exclusion-logic problem), so the corrected rule correctly finds nothing outside the package to preserve because nothing outside the package was ever downloaded in the first place. That fetch gap is a separate, still-open limitation, tracked apart from the exclusion fix itself.

### Is any data available at all?

Cooper et al. report that "97% (n = 1690) archived their data" among the 1735 papers coded as using data [@cooper2026, p. 1958]. `mc_data_availability` and Cooper et al.'s `data_availability` were both codeable for `r results$data_availability$n_both_coded` papers. They agreed on `r results$data_availability$n_agree` (`r pct1(results$data_availability$pct_agree/100)`%), disagreed on `r results$data_availability$n_disagree` (`r pct1(1-results$data_availability$pct_agree/100)`%). Sensitivity was `r pct1(results$data_availability$sensitivity)`% and specificity was `r pct1(results$data_availability$specificity)`%, McNemar's `r mcnemar_str(results$data_availability)`. This is a considerably more balanced pattern than an earlier pass of this corpus found, because `mc_data_availability`'s own derivation was corrected during this project (see Coding section): it now reflects `repo_check` finding at least one linked repository with at least one file, rather than defaulting to a missing value whenever `repo_check` found none at all — so a paper with no detectable repository now correctly scores `FALSE` and enters this comparison, rather than being silently excluded from it.

Reviewing all `r results$data_availability$n_disagree` disagreements individually: `r vt(verdict_tallies$data_availability, "COOPER_RIGHT")` were `COOPER_RIGHT`, `r vt(verdict_tallies$data_availability, "METACHECK_RIGHT")` `METACHECK_RIGHT`, `r vt(verdict_tallies$data_availability, "DIFFERENT_DEFINITION")` `DIFFERENT_DEFINITION`, and `r vt(verdict_tallies$data_availability, "UNCLEAR")` `UNCLEAR`. The dominant cause among the `COOPER_RIGHT` cases (`r cc(cooper_right_causes$data_availability, "repo_not_detected")` of `r vt(verdict_tallies$data_availability, "COOPER_RIGHT")`) is `repo_check` never detecting a repository at all, even though the paper's own text names one explicitly — most often a real, working DOI or URL on a platform `repo_check` has no dedicated backend for (institutional repositories such as DataSTORRE, DIGITAL.CSIC, or the Australian Antarctic Data Centre; domain-specific databases such as NCBI's Sequence Read Archive/GenBank, the Knowledge Network for Biocomplexity, or Neotoma), or occasionally a citation malformed by PDF text extraction. A further `r cc(cooper_right_causes$data_availability, "gated_fetch_error")` trace to a `repo_check` processing error logged internally (an R-level error raised while fetching an otherwise-correctly-detected repository, or the host platform being transiently unreachable during the corpus run) rather than a missed citation — a genuine, fixable software defect distinct from a coverage gap. Conversely, `r vt(verdict_tallies$data_availability, "METACHECK_RIGHT")` disagreements were `METACHECK_RIGHT`: clear, working Dryad, Zenodo, Figshare, or GitHub data-availability statements that Cooper et al.'s coders appear to have missed or coded `No` in error. `r vt(verdict_tallies$data_availability, "DIFFERENT_DEFINITION")` were `DIFFERENT_DEFINITION` — most commonly a paper stating data are available "on request," embedded directly in the article's own Supporting Information, or withheld for confidentiality reasons, which Cooper et al.'s protocol appears to credit as "available" while `mc_data_availability` structurally cannot, since there is no externally checkable repository for `repo_check` to find. The remaining `r vt(verdict_tallies$data_availability, "UNCLEAR")` could not be resolved from the available evidence.

**Limitation.** The mechanism responsible for `mc_data_availability`'s disagreements has changed since an earlier pass of this corpus: rather than a single, blanket rule failure that made a `FALSE` structurally impossible, the remaining gap is now dominated by `repo_check`'s coverage of repository platforms and citation formats — addressable by extending its URL-recognition patterns to more institutional and domain-specific repositories, rather than by changing the derivation rule itself.

### Where are the data archived?

Cooper et al. report Dryad as the dominant data repository (57%, n = 1022), with Figshare (9%), Zenodo (12%), and "various institutional and government repositories" (17%) making up most of the remainder [@cooper2026, p. 1959]. `mc_data_archive` and Cooper et al.'s `data_archive` were both codeable for `r results$data_archive$n_both_coded` papers; because this is a platform-*name* comparison rather than a boolean, we score agreement as at least one overlapping platform name between the two sides' (possibly multi-valued) answers. They agreed on `r results$data_archive$n_agree` (`r pct1(results$data_archive$pct_agree/100)`%), disagreed on `r results$data_archive$n_disagree` (`r pct1(1-results$data_archive$pct_agree/100)`%).

Reviewing all `r results$data_archive$n_disagree` individually: `r vt(verdict_tallies$data_archive, "METACHECK_RIGHT")` were `METACHECK_RIGHT` — almost entirely Cooper et al.'s coders using the catch-all "Other repo/database" label for a repository whose platform is, on the paper's own text and URL, unambiguous (most often OSF, e.g. a Data Availability Statement reading "Data and code available from the Open Science Framework: https://doi.org/10.17605/OSF.IO/PNJFW," coded "Other repo/database" rather than "OSF"). `r vt(verdict_tallies$data_archive, "COOPER_RIGHT")` were `COOPER_RIGHT`, the mirror image of a pattern that recurs across several columns in this comparison: a paper genuinely has two separate repositories, one holding code and one holding data, and `mc_data_archive` picked up the *code* repository's platform because `repo_check` found that repository's files but never located the data repository's at all (a domain-specific database, an institutional repository, or a Dryad/Mendeley deposit named in the text but never fetched). `r vt(verdict_tallies$data_archive, "BOTH_DEFENSIBLE")` were `BOTH_DEFENSIBLE`: genuinely multi-repository papers where Cooper et al.'s single-choice coding and Metacheck's semicolon-joined multi-platform answer are each a defensible summary of a paper that does not reduce to one archive. `r vt(verdict_tallies$data_archive, "DIFFERENT_DEFINITION")` was a case where the paper itself distinguishes a versioned Zenodo *archive* from a live, mutable GitHub development repository, and Cooper et al. and Metacheck picked different repos by design. The remaining `r vt(verdict_tallies$data_archive, "UNCLEAR")` could not be resolved from the available evidence.

**Limitation.** The recurring code-repository-mislabelled-as-data-repository pattern reflects a genuine architectural gap rather than a text-parsing failure in any single instance: `repo_check` finds every repository a paper links, but the logic that decides which one to report as "the data archive" for `mc_data_archive` has no signal for "this repository actually holds the study's data" beyond checking which repositories hold `data_type == "data"` files — and that check is itself blind to a repository whose only file is an unopened archive (see the `code_archived` discussion below for the same limitation's larger effect there).

### Is the data licensed?

Cooper et al. report that 85% (n = 1438) of papers with archived data had a license [@cooper2026, p. 1960]. `mc_data_license` and Cooper et al.'s `data_license` were both codeable for `r results$data_license$n_both_coded` papers. They agreed on `r results$data_license$n_agree` (`r pct1(results$data_license$pct_agree/100)`%), disagreed on `r results$data_license$n_disagree` (`r pct1(1-results$data_license$pct_agree/100)`%). Sensitivity was `r pct1(results$data_license$sensitivity)`% and specificity was `r pct1(results$data_license$specificity)`%, McNemar's `r mcnemar_str(results$data_license)`.

All `r results$data_license$n_disagree` disagreements were individually resolved against the relevant repository platform's own API, called live at the time of review. `r vt(verdict_tallies$data_license, "METACHECK_RIGHT")` were `METACHECK_RIGHT`: a real, retrievable license genuinely exists — most commonly CC0-1.0 for Dryad datasets (Dryad requires a license at deposit) or a depositor-selected "Other (Open)" tag for Zenodo records, or a GitHub repository license confirmed live via GitHub's own repository API. `r vt(verdict_tallies$data_license, "COOPER_RIGHT")` were `COOPER_RIGHT`, and the large majority share the same repository-scoping mechanism documented for `mc_data_archive` above: a licensed repository genuinely exists for the paper, but `data_check` classified zero of its files as `data`-typed (often because the only file is an archive never opened, or because the licensed repository is a separate code deposit rather than the data-holding one), so `mc_data_license`'s data-only scoping rule never reaches it; a smaller number trace to `repo_check` never detecting the licensed repository at all. The remaining `r vt(verdict_tallies$data_license, "UNCLEAR")` could not be resolved because `repo_check` found no `repo_metadata` row at all for the relevant repository.

**Limitation.** `mc_data_license` inherits `mc_data_archive`'s repository-scoping limitation, since both restrict themselves to "the repository holding data." It remains one of the more reliably automatable constructs in this comparison in the *METACHECK_RIGHT* direction: every case where Metacheck found a license was independently reconfirmed against the same live API `repo_check` itself reads from.

### Can the data be downloaded and used?

Cooper et al. report that, of archived datasets, "95% could be downloaded, and 91% could be opened" [@cooper2026, p. 1959]. `mc_data_download` and Cooper et al.'s `data_download` were both codeable for `r results$data_download$n_both_coded` papers. They agreed on `r results$data_download$n_agree` (`r pct1(results$data_download$pct_agree/100)`%), disagreed on `r results$data_download$n_disagree` — a small enough count that every case was individually traced rather than summarized by category.

Of the `r results$data_download$n_disagree` disagreements, `r vt(verdict_tallies$data_download, "COOPER_RIGHT")` were `COOPER_RIGHT`: files that downloaded successfully but still failed `data_check`'s tabular-usability check for a real, distinct reason each time — a space-delimited scientific data format (climate-model output with a distinctive multi-part naming convention) the tabular reader does not recognise, an unusual two-row header layout, and other content-specific parsing gaps rather than a single repeatable bug. `r vt(verdict_tallies$data_download, "DIFFERENT_DEFINITION")` were `DIFFERENT_DEFINITION`: the data genuinely downloaded and opens correctly in standard software, but `mc_data_download`'s own criterion (see Coding section) additionally requires `data_check`'s stricter `tabular_usable` flag, which does not always agree with "a human can open this file just fine." `r vt(verdict_tallies$data_download, "METACHECK_RIGHT")` was `METACHECK_RIGHT` (a downloaded file that, on direct inspection, was a serialized model-input dump with no valid row/column structure at all). The remaining `r vt(verdict_tallies$data_download, "UNCLEAR")` could not be independently confirmed, since the paper's own text gives no detail on whether the data genuinely opens beyond a bare repository link — exactly the kind of live-repository fact a text-only check cannot resolve either way.

**Limitation.** This construct's very small remaining disagreement count (`r results$data_download$n_disagree` papers, `r pct1(1-results$data_download$pct_agree/100)`% of the codeable base) reflects fixes applied earlier in this project (a multi-sheet Excel reading limitation, scienceverse/metacheck#379; see Appendix A.1 for the full mechanism and before/after numbers from that specific fix). What remains is a heterogeneous residual of genuinely distinct format- and content-specific parsing gaps rather than one further systematic cause.

### Is code archived, and can it be downloaded?

Cooper et al. report that "only 35% (n = 577) archived their code" among papers using code [@cooper2026, p. 1958], and, among archived code, that most is on Zenodo or GitHub-family platforms [@cooper2026, p. 1959]. We report `mc_code_archived` and `mc_code_download` together, since the qualitative review of both surfaced overlapping causes.

`mc_code_archived` and Cooper et al.'s `code_archived` were both codeable for `r results$code_archived$n_both_coded` papers. They agreed on `r results$code_archived$n_agree` (`r pct1(results$code_archived$pct_agree/100)`%), disagreed on `r results$code_archived$n_disagree` (`r pct1(1-results$code_archived$pct_agree/100)`%) — the largest disagreement rate of any construct in this comparison. Sensitivity was `r pct1(results$code_archived$sensitivity)`% and specificity `r pct1(results$code_archived$specificity)`%, McNemar's `r mcnemar_str(results$code_archived)`. `mc_code_download` and Cooper et al.'s `code_download` were both codeable for `r results$code_download$n_both_coded` papers (a much smaller base, since this sub-question only applies when code was coded as archived in the first place); they now agree on `r results$code_download$n_agree` of `r results$code_download$n_both_coded` (`r pct1(results$code_download$pct_agree/100)`%), with a single disagreement remaining.

`code_download`'s current near-total agreement reflects a substantial, multi-stage improvement over the course of this project, documented fully in Appendix A.1 (from 66.2% agreement before any fix, through successive intermediate rounds, to the current `r pct1(results$code_download$pct_agree/100)`%). `code_archived` moved much less across the same fixes, consistent with its dominant causes being ones those fixes did not target.

All `r results$code_archived$n_disagree` `code_archived` disagreements and the single remaining `code_download` disagreement were individually resolved. `code_archived`'s `r vt(verdict_tallies$code_archived, "COOPER_RIGHT")` `COOPER_RIGHT` cases are genuinely multi-causal:

1. **Code bundled inside the same repository as the data, with `code_check` finding no file to classify as code there (`r cc(cooper_right_causes$code_archived, "code_bundled_not_classified")` cases).** A recurring, precisely worded pattern: a Data Availability Statement reading, for instance, "Data and R code available from the Dryad Digital Repository" — the paper's own text explicitly confirms code is bundled with the data in one deposit, `repo_check` found that repository, but `code_check` classified none of its files as code (most often because the only file is an archive never opened, the same zip-peek limitation described next).
2. **`repo_check` never opened a zip/tar archive holding the paper's code (`r cc(cooper_right_causes$code_archived, "zip_not_peeked")` cases).** Metacheck does not inspect an archive's contents by default; a Zenodo record whose only file is a GitHub-integration snapshot (filename pattern `owner/repo-vX.Y.Z.zip`) is a recurring, easily recognisable instance of this.
3. **`repo_check` never detected the repository at all (`r cc(cooper_right_causes$code_archived, "repo_not_detected")` cases),** despite the paper's own text explicitly naming it — the same platform-coverage and citation-extraction gap documented for `data_availability` above.
4. **A `repo_check`-side processing error, logged internally (`r cc(cooper_right_causes$code_archived, "gated_fetch_error")` cases)** — the repository was correctly identified but its fetch failed with an R-level error or a transient host outage during the corpus run.
5. **A more heterogeneous remainder (`r cc(cooper_right_causes$code_archived, "other")` cases)**, including code provided only as journal Supporting Information rather than in any linked repository, citations to a third-party dependency's repository rather than the authors' own code, and `repo_check`-side file-classification errors (e.g., shapefile metadata files misclassified as code).

A smaller number of `code_archived` disagreements ran the opposite direction (`r vt(verdict_tallies$code_archived, "METACHECK_RIGHT")` `METACHECK_RIGHT`): `r cc(code_archived_mr_causes, "code_check_found_files")` are real, substantial, multi-file GitHub or Zenodo code repositories that `code_check` correctly found and classified, coded `No` by Cooper et al. — a large, unambiguous set of named analysis scripts is not the kind of borderline case a coding protocol's edge cases would plausibly explain, so these look like straightforward human-coder misses; a further `r cc(code_archived_mr_causes, "no_code_mentioned")` are papers whose own text and Data Availability Statement mention no code, script, or software at all, so Cooper et al.'s `Yes` has no traceable basis in the paper's own evidence. `r vt(verdict_tallies$code_archived, "DIFFERENT_DEFINITION")` were `DIFFERENT_DEFINITION`: code described only as pseudocode or a script embedded in the journal's own Supporting Information, which Cooper et al.'s coding appears to credit as "archived" while `code_check` structurally cannot see it (it is not in any linked repository). The remaining `r vt(verdict_tallies$code_archived, "UNCLEAR")` were `UNCLEAR`, generally because the extracted paper text contained no relevant statement either way.

The single remaining `code_download` disagreement is `METACHECK_RIGHT`: real, verified downloaded code files that Cooper et al.'s coding missed.

**Limitation.** `code_archived` remains the construct in this comparison with both the highest disagreement rate and the most heterogeneous set of causes. The single largest cause (code co-located with data in a repository `code_check` cannot classify, whether because the file is an unopened archive or for another reason) points to the same underlying zip-peek limitation affecting `data_archive` and `data_license` above; the second-largest (repository detection coverage) is the same gap documented for `data_availability`. `code_download`'s gap, by contrast, has narrowed to a single remaining case after the fixes documented in Appendix A.1 — this construct is, at present, essentially resolved.

### Is there a README?

Cooper et al. report a README present for "66% (n = 1114) and 61% (n = 351) of the papers with archived data or code, respectively" [@cooper2026, p. 1959]. As described in the Coding section, Metacheck records a single README signal per paper (computed once, across every linked repository combined), so we compare it against `cooper_any_readme` — `TRUE` if Cooper et al. coded "Yes" or "Quasi-README" on *either* their `data_README` or `code_README` question. `mc_any_readme` and `cooper_any_readme` were both codeable for `r results$any_readme$n_both_coded` papers. They agreed on `r results$any_readme$n_agree` (`r pct1(results$any_readme$pct_agree/100)`%), disagreed on `r results$any_readme$n_disagree` (`r pct1(1-results$any_readme$pct_agree/100)`%) — the largest raw disagreement count of any construct in this comparison, though, as with `code_archived`, its composition changes the interpretation substantially. Sensitivity was `r pct1(results$any_readme$sensitivity)`%, specificity `r pct1(results$any_readme$specificity)`%.

Of the `r results$any_readme$n_disagree` disagreements, `r vt(verdict_tallies$any_readme, "METACHECK_RIGHT")` were `METACHECK_RIGHT` on review — genuine cases where a real README file exists in a repository `repo_check` listed, and Cooper et al.'s coders missed it. `r vt(verdict_tallies$any_readme, "COOPER_RIGHT")` were `COOPER_RIGHT`, dominated (`r cc(cooper_right_causes$any_readme, "repo_not_detected")` cases) by the same repository-detection gap documented for `data_availability` and `code_archived` above — `repo_check` never located a repository the paper's own text explicitly names, so no README evidence could ever be recorded — with a further `r cc(cooper_right_causes$any_readme, "zip_not_peeked")` cases where the repository was found but its only file is an unopened archive, and `r cc(cooper_right_causes$any_readme, "gated_fetch_error")` cases tracing to a `repo_check` processing error. The remaining `r vt(verdict_tallies$any_readme, "UNCLEAR")` were `UNCLEAR`.

The single largest verdict category, however, is `r vt(verdict_tallies$any_readme, "DIFFERENT_DEFINITION")` `DIFFERENT_DEFINITION` cases (`r pct1(vt(verdict_tallies$any_readme, "DIFFERENT_DEFINITION")/results$any_readme$n_disagree)`% of all disagreements, slightly ahead of the `COOPER_RIGHT` count above) — not a detection failure on either side, but the two coding approaches answering genuinely different questions that happen to share Cooper et al.'s column label:

- **Dryad's abstract field (the largest single cause, `r cc(any_readme_dd_causes, "dryad_abstract")` cases).** Dryad's own dataset API exposes exactly one free-text field, `abstract`. Checked directly on real Dryad datasets from this disagreement set, this field is consistently the paper's own scientific abstract — never file-by-file documentation of what the archived files contain. Cooper et al.'s coders, reading the same field on the live Dryad page, appear to have coded this abstract as satisfying "README present," a defensible reading of their own protocol given what Dryad actually surfaces to a human visitor; `repo_check`'s `doc_role` classification, which requires an actual downloadable file named like a README, never counts it.
- **Zenodo's and Figshare's `description` fields (`r cc(any_readme_dd_causes, "zenodo_figshare_description")` cases).** Unlike Dryad's abstract, these platforms' `description` fields are genuinely mixed in content — checked directly on records from this disagreement set, real file-by-file documentation appears in some cases, a study summary in others, contact metadata in others, and an empty field in others. No single, reliable rule (treat the description as a README, or don't) would correctly resolve every case.
- **An archive-only repository whose single compressed file `repo_check`'s remote listing could not resolve (`r cc(any_readme_dd_causes, "archive_only_zip")` cases).** Any README bundled inside such an archive is invisible to the README check even when `repo_check`'s own zip-listing feature is enabled, for the same family of archive-access limitations discussed above.
- **A smaller remainder (`r cc(any_readme_dd_causes, "other")` cases)** not matching any of the three patterns above.

**Limitation, and a genuinely different framing than the other constructs in this comparison.** Unlike every other column reported here, `any_readme`'s disagreement is overwhelmingly *not* a case of either side being wrong. It is a case where Cooper et al.'s human coders, reading a live repository page, correctly used whatever free-text field that platform's own interface surfaced to them as evidence of a README-like description, while Metacheck's `doc_role` classification asks a narrower, more conservative question (is there a downloadable file that is actually named like a README) that structurally cannot see a platform's own abstract or description metadata at all. Resolving this gap in Metacheck's favor is not simply a matter of relaxing a filename rule: Dryad's abstract field is confirmed *never* to be README-equivalent content (so counting it would introduce false positives), while Zenodo's and Figshare's description fields are confirmed to be genuinely mixed (so counting them uniformly would introduce a different, more Zenodo/Figshare-specific rate of false positives). A reliable fix would need to distinguish, likely with a content classifier rather than a presence check, which platform-level description fields actually contain file-documentation content, on a case-by-case rather than platform-wide basis.
## Is a comment count a proxy for comment quality?

Cooper et al.'s protocol includes a construct no Metacheck module attempts to answer directly: `code_annotation_scale`, a human coder's 1-10 judgment of how well a paper's code is commented, coded for 543 of the 1861 papers. Metacheck's `code_check` module does not judge comment quality, but it does mechanically count comments: for every code file it can download and parse, it records `comment_lines`, `code_lines`, and `percentage_comment` (comment lines as a share of all lines). This raises a genuinely exploratory question distinct from every comparison above, none of which asked whether an *automatable* signal could stand in for a *judged* one: if a simple, free line-count already tracked Cooper et al.'s human quality rating closely, that would suggest the more expensive human judgment adds comparatively little beyond what counting could already tell us; if it does not, that would suggest the human coders are picking up on something a mechanical count cannot see.

```{r}
#| label: comment-quality-stats
#| eval: FALSE ## Set to TRUE to rerun

# Computed by code_data_preparation/34_comment_quality_correlation.R:
# Cooper et al.'s code_annotation_scale (1-10) joined against Metacheck's
# code_check() per-file comment_lines/code_lines, aggregated to one
# weighted percentage-of-comments-per-paper value (comment lines summed
# over code lines summed across every analysable file in that paper, not
# an average of per-file percentages, so a 500-line file counts more than
# a 5-line file).
load("data/comment_quality_correlation.RData")
```

We aggregated Metacheck's per-file comment counts to one value per paper — total comment lines divided by total lines across every code file `code_check` could download and parse for that paper — and compared it against Cooper et al.'s `code_annotation_scale` for the 310 papers where both were available (of 543 papers Cooper et al. rated and 357 papers Metacheck could compute a comment percentage for at all; the smaller overlap reflects that Metacheck's count requires at least one code file to have actually downloaded and parsed, which, as the sections above document, is itself not guaranteed).

The correlation is weak but not zero: Pearson's *r* = .16, 95% CI [.05, .27], *p* = .005; Spearman's $\rho$ = .14, *p* = .013. Using the raw comment line count instead of the percentage gives essentially the same result ($\rho$ = .13, *p* = .020), so this is not an artifact of how the percentage was computed. As a check on whether longer codebases are simply commented differently regardless of quality, we also correlated total code lines against percentage of comments directly: longer codebases have a modestly *lower* comment percentage ($\rho$ = -.20, *p* < .001), consistent with comments not simply scaling with code length, and not something that would by itself explain the annotation-scale correlation being as weak as it is.

**Interpretation.** A correlation of this size — roughly 2% of variance explained on the Pearson estimate — means a paper's comment *density* is a poor stand-in for a human coder's *quality* judgment: knowing what fraction of a codebase's lines are comments tells us very little about whether a coder would call those comments good annotation. This is exploratory, not a claim about causation or about which measure is "right" — the two are answering different questions by design, and a low correlation between them is not evidence that either is wrong. But it does directly speak to the question motivating this comparison: for this specific construct, an automatable proxy does not substitute well for the human judgment call, at least not the simplest version of that proxy (line-count percentage). A single well-placed sentence explaining a complex analysis counts as excellent annotation on Cooper et al.'s scale and as a single line on Metacheck's; ten lines of boilerplate restating variable names count as heavily annotated by line count and would plausibly score poorly on a human quality read. Comment *content* — whether a comment explains a non-obvious decision, restates the obvious, or is simply absent — is the kind of thing an LLM-based classifier could more plausibly approximate than a line count can, but that would need its own validation against this same ground truth before being trusted, following the same case-by-case standard used throughout this manuscript rather than assumed from the fact that an LLM could be asked to try.

## Results you get for free alongside Metacheck

Every comparison above answers a question Cooper et al.'s protocol already asked. Running `repo_check`, `data_check`, and `code_check` on a corpus also produces a substantial amount of additional, structured diagnostic information that no item in Cooper et al.'s protocol asks for at all — not because Metacheck was built to exceed their protocol, but because the same file listing, the same downloaded code, and the same parsed spreadsheets that answer "is there a repository" or "is there a README" also support other checks the modules perform as a matter of course. This section reports what that additional output looks like at corpus scale, computed entirely from the same saved module output as the comparison above (`res_repo_check.RData`, `res_data_check.RData`, `res_code_check.RData`) — no additional module run was needed.

```{r}
#| label: free-extras-stats
#| eval: FALSE ## Set to TRUE to rerun

# Computed by code_data_preparation/35_free_extras_summary.R directly from
# the saved corpus-wide module outputs -- no new module run.
load("data/free_extras_summary.RData")
```

### Code portability and reproducibility signals

`code_check` parsed 10,461 code files across 400 code-bearing papers. Three checks bear directly on whether that code would actually run for someone other than its original author. (A systematic validation of these checks against real corpus files, reported in Appendix A.3, identified and fixed five false-positive/false-negative mechanisms; the numbers below reflect the corpus as run before those fixes and will be updated once a corpus rerun incorporating them is complete.)

- **Missing referenced files.** For every code file, `code_check` extracts every filename the code itself tries to open (`read.csv(...)`, `source(...)`, and equivalent calls in each supported language) and checks whether that name appears anywhere in the same paper's repository listing. 948 files (9.1% of all analysed files), across 183 papers (45.8% of code-bearing papers), reference at least one file that could not be found. This does not necessarily mean the code is broken — a file might exist under a name the regex-based extraction did not match exactly, or might be generated by an earlier step in the same pipeline — but it is a direct, corpus-wide signal of how often "the code plus the shared data" does not obviously line up as a complete, runnable unit.
- **Hardcoded absolute paths.** 399 files (3.8%), across 110 papers (27.5%), contain an absolute file path (e.g. `C:/Users/...` or `/home/...`) rather than a path relative to the project. Code written this way will not run on any machine but the one it was written on without manual editing.
- **`setwd()` calls.** 302 files (2.9%), across 79 papers (19.8%), call `setwd()` to hardcode a working directory. Combined with hardcoded absolute paths (which frequently co-occur with a `setwd()` call to the same machine-specific location), the two portability problems together affect 228 of the 400 code-bearing papers (57.0%) — meaning more than half of the papers whose code we could inspect at all have at least one file that will not run as shared, on someone else's machine, without modification.

### Comment density (mechanical count)

As reported above in the comment-quality correlation, `code_check` records `comment_lines`/`code_lines` per file. Corpus-wide, comments make up 22.1% of all code lines across the 8,039 files with a computable line count (a small fraction of files could not be measured — an encoding problem, or a file too short to classify meaningfully). 984 files (12.2%) have zero comments at all — of which a substantial fraction are Python files documented via a docstring rather than a `#` comment, a distinction `code_check` now also reports separately (Appendix A.3).

### Import/library organization

Where a file loads more than one package, `code_check` also records how far apart those loading lines are (its own documented threshold is more than a few lines apart counting as "scattered" rather than grouped at the top of the file). 956 of 3,568 such files (26.8%) load their packages in a scattered rather than grouped fashion — a minor readability signal, not a correctness one, but one a reader piecing together a script's dependencies would find genuinely useful.

### Parse errors

Of the 5,536 R-type code files (`.R`, `.Rmd`, `.qmd`) that were both locally available and actually reached a call to `parse()`, 138 failed to parse as valid code in their declared language at all (2.5%) — a strong, unambiguous signal (not a stylistic judgment) that something is wrong with either the file itself or Metacheck's identification of its language. (Only R-type files are eligible for this check at all; a file that was never downloaded, or that errored before reaching the parse step itself, is excluded from this denominator rather than counted as a pass — see Appendix A.2 for the full derivation and the two distinct causes behind the files excluded this way.)

### Package version pinning

`code_check` also checks whether a repository pins the exact R/package versions its analysis depended on — an `renv.lock` file, a `sessionInfo()`/`session_info()` text dump, or a `groundhog`/`checkpoint` date-pinning call in the code itself (a bare `library(groundhog)` does not count; the pinning call itself must be present). Of the 400 code-bearing papers, 18 (4.5%) have version pinning present, recorded per paper as `code_version_pinned` in `code_check`'s own summary output (see Appendix A.2 for how this per-paper figure was recovered).

### Spreadsheet and column-level data-quality findings

`data_check` inspects every tabular data file it can download and parse, both at the file/sheet level (is this a rectangular table at all, is the header on the first row, does the file use colour or merged cells to encode information Metacheck cannot read from a plain CSV) and at the level of individual columns (does a column look like it holds personal information, geographic coordinates, inconsistent category casing, numbers stored as text, or values in a legacy character encoding). Across the corpus, these checks produced 13,015 findings, spanning 2,028 distinct files. The most frequent, in descending order:

| Finding | Count |
|---|---|
| Numeric values stored as text | 3,406 |
| Problematic column name (illegal characters or excessively long) | 2,551 |
| Empty column (no observed values) | 1,838 |
| Colliding column names (identical once special characters are stripped) | 1,451 |
| Empty or unnamed columns | 755 |
| Personal info suggested by column name | 695 |
| Leading/trailing whitespace in values | 619 |
| Values that look like geographic coordinates | 418 |
| Inconsistent category casing | 361 |
| Fully empty rows inside the data range | 303 |
| Colour used to encode information (lost on CSV export) | 178 |
| Merged cells (breaks the rectangular grid) | 128 |
| Free text that may contain personal detail | 100 |
| Legacy (non-UTF-8) character encoding | 77 |
| Personal info suggested by column values | 41 |
| Legacy `.xls` file (colour/merges/empty-cell checks cannot run) | 38 |
| Header not on the first row | 35 |
| Not a usable rectangular dataset | 15 |
| File could not be parsed as a workbook at all | 6 |

Two of these are worth calling out specifically because they bear on participant confidentiality rather than only on tidiness: the two personal-information checks (by column name and by column values) and the "free text that may hold PII" check together flag 836 findings across the corpus — columns or values that look, on their face, like they could contain names, contact details, or other identifying information in a file the authors have made publicly downloadable. Metacheck does not verify whether this is a genuine confidentiality problem (a column named "participant_id" that holds only anonymous sequential integers would also match on name alone), but a count this size suggests a possible participant-privacy check would find comparable value to the correctness-oriented deposit review Cooper et al.'s protocol already performs.

### File-naming conventions

`repo_check` checks every listed file's name against a set of FAIR-data-adjacent naming conventions: no spaces or special characters, an actually-classifiable name (not left as `data_type == "unknown"`), consistent casing, zero-padded sibling numbering, valid dates, and several path-length budgets. Across the corpus, this produced 28,614 naming issues, 14,792 of them the more serious "bad" severity (something that actually breaks: spaces, special characters, diacritics, an unclassifiable file, an invalid date, or an over-long path) and 13,822 the softer "suggestion" severity (a real convention worth following, but nothing in Metacheck's own classification depends on it). 717 distinct papers (48.4% of the 1,480 papers with a discoverable repository) have at least one naming issue of some kind. The single largest contributor by far is "unclassifiable" file names (11,535 occurrences) — files whose name gives Metacheck's classifier no signal at all about what kind of content they hold, which is itself a legibility problem for a human reader trying to navigate the repository, independent of anything Metacheck specifically failed to detect.

**Why this section exists.** None of the findings above were validated against Cooper et al.'s human coding, because Cooper et al.'s protocol did not ask about any of them — there is no ground truth to check against, and no sensitivity/specificity/agreement-rate analysis is possible for a construct nobody coded. We report them here, separately from the validated comparison above, specifically so that this distinction stays clear: these are Metacheck's own outputs, useful in their own right for a researcher curious about a specific repository's quality, but not independently verified the way every number earlier in this manuscript was. A natural next step, beyond the scope of this paper, would be a smaller, targeted validation of a sample of these specific findings (are the "unclassifiable" file names really unclassifiable to a human reader too; do the flagged personal-information columns really hold identifying information) using the same case-by-case standard applied throughout the rest of this manuscript.

## Discussion

Table 0 summarizes the empirical comparison reported above: agreement rate, sensitivity, specificity, and the two directional miss rates for every construct where Metacheck and Cooper et al.'s coding can be directly compared.

```{r}
#| label: summary-table-display
#| tbl-cap: "Table 0. Empirical agreement between Metacheck and Cooper et al.'s human-coded ground truth, for every comparison column. \"Cooper caught, MC missed\" and \"MC caught, Cooper missed\" are percentages of the disagreements only (they sum to 100% within a row), not of the full sample."

load("data/comparison_statistics.RData")

summary_rows <- lapply(names(results), function(nm) {
  r <- results[[nm]]
  data.frame(
    Construct = r$label,
    n = r$n_both_coded,
    `Agree %` = round(r$pct_agree, 1),
    `Sensitivity %` = if (!is.null(r$sensitivity)) round(r$sensitivity * 100, 1) else NA,
    `Specificity %` = if (!is.null(r$specificity)) round(r$specificity * 100, 1) else NA,
    `Cooper caught, MC missed %` = if (!is.null(r$pct_cooper_caught_mc_missed)) round(r$pct_cooper_caught_mc_missed, 1) else NA,
    `MC caught, Cooper missed %` = if (!is.null(r$pct_mc_caught_cooper_missed)) round(r$pct_mc_caught_cooper_missed, 1) else NA,
    check.names = FALSE
  )
})
summary_tbl <- do.call(rbind, summary_rows)

flextable(summary_tbl) |>
  width(1, 2.0) |>
  width(2, 0.45) |>
  width(3:5, 0.65) |>
  width(6:7, 0.85)
```

Two patterns are visible across every construct in Table 0. First, the size and direction of the sensitivity/specificity gap now varies considerably from construct to construct, and reviewing every individual disagreement, rather than stopping at the aggregate numbers, shows why: the asymmetry has a different cause in each column, and the cause matters more than the raw percentage for deciding what, if anything, to fix. `data_availability`'s specificity (`r pct1(results$data_availability$specificity)`%) is far from the zero an earlier pass of this corpus found, precisely because the derivation-rule fix described in the Coding section gave it a genuine ability to disagree with Cooper et al. in the `FALSE` direction at all; what remains is a repository-coverage gap (see above), not a structural inability to ever produce a negative. `code_download`'s specificity is still `r pct1(results$code_download$specificity)`%, but on a base of only `r results$code_download$n_disagree` remaining disagreement this reflects one unresolved case, not a systematic pattern; `data_download` currently has no codeable Cooper-`No` case at all, so its specificity is undefined rather than low. `code_archived` shows the most pronounced asymmetry of any boolean construct (sensitivity `r pct1(results$code_archived$sensitivity)`%, specificity `r pct1(results$code_archived$specificity)`%) and is genuinely multi-causal, spanning a real content-location mismatch (code bundled with data in a repository `code_check` cannot classify), a zip-peek limitation, a repository-detection gap, and a real "not in any repository at all" category (journal Supporting Information) no repository-scanning approach can close. `any_readme`'s asymmetry is not primarily attributable to either side being *wrong* at all: `r pct1(vt(verdict_tallies$any_readme, "DIFFERENT_DEFINITION")/results$any_readme$n_disagree)`% of its disagreements reflect Cooper et al.'s human coders correctly reading platform-level metadata (a Dryad abstract, a Zenodo or Figshare description) that Metacheck's stricter, filename-based README check was never designed to treat as equivalent evidence, and where doing so uniformly would, on the evidence collected here, introduce as many new false positives (Zenodo/Figshare) as it resolved.

Second, precision in the direction Metacheck *does* commit to an answer remains generally high, though no longer universal: positive predictive value was above 97% for five of the six boolean constructs (`data_availability` `r pct1(results$data_availability$ppv)`%, `data_license` `r pct1(results$data_license$ppv)`%, `data_download` `r pct1(results$data_download$ppv)`%, `code_download` `r pct1(results$code_download$ppv)`%, `any_readme` `r pct1(results$any_readme$ppv)`%), meaning that when Metacheck reports a repository, license, download, or README as present, that report is rarely spurious. `code_archived` is the exception: its PPV, `r pct1(results$code_archived$ppv)`%, is meaningfully lower, because `r vt(verdict_tallies$code_archived, "METACHECK_RIGHT")` of its `r results$code_archived$n_disagree` disagreements are cases where `code_check` correctly found real code files that Cooper et al.'s coders missed or judged not to count — a genuine human-coder miss, not a Metacheck false positive, but one that lowers this specific metric regardless of which side is right. The asymmetry in this comparison therefore remains overwhelmingly a *recall* problem for most constructs — Metacheck under-detects relative to a human coder who can read a repository's page, follow an ambiguous citation, or interpret an unusual sentence structure — but `code_archived` shows this is not universal: a `TRUE` from Metacheck is a highly trustworthy signal for five of the six boolean constructs, while for `code_archived` specifically, a nontrivial share of Metacheck's `FALSE` answers reflect a real detection gap rather than code genuinely being unarchived.

Three constructs in Cooper et al.'s protocol have no Metacheck counterpart at all and were therefore not part of the quantitative comparison above: README/code *usefulness* (a human-judged 1-10 scale), data *completeness* relative to a paper's reported analyses, and code annotation *quality* as distinct from comment density. These are precisely the questions where Cooper et al.'s human coders had to read and interpret content, not merely detect its presence, and they mirror a pattern visible even within the constructs we could compare: Metacheck's underlying modules answer structural questions (does a file with this name exist, did a download succeed, does a table parse) reliably, and answer content-interpretation questions (is this description a real README, is this the paper's actual dataset rather than simulation output, is this repository the one holding the data rather than the code) far less reliably, precisely because those questions require reading and judging content rather than classifying structure. Large language models are a plausible route to closing part of this gap for the constructs Metacheck cannot currently address at all, and could plausibly also help with several of the misclassification patterns documented above (distinguishing a Dryad abstract from file documentation, or a simulation-output file from raw collected data) — but any such extension would need to be built, validated against Cooper et al.'s own ground truth using the same case-by-case standard applied here, and reported with a known error rate, rather than assumed to work from the fact that an LLM could plausibly be prompted to attempt it.

A recurring, cross-cutting finding worth naming explicitly is the data-versus-code repository conflation pattern: a genuinely common paper structure — one repository holding the study's data, a separate repository (often GitHub) holding its analysis code, sometimes with the data-holding repository never located by `repo_check` at all — appears as the dominant or a substantial cause of disagreement in `data_archive`, `data_license`, and `code_archived` alike. This is not three independent bugs; it is one architectural gap (Metacheck's repository-scoping logic assumes each construct maps cleanly onto "the" repository for a paper) surfacing across every construct that depends on correctly identifying *which* repository is relevant. It remains, after every fix applied over the course of this project, the single largest reason Metacheck and Cooper et al. disagree: repository non-detection alone accounts for `r cc(cooper_right_causes$data_availability, "repo_not_detected")` of `data_availability`'s `r vt(verdict_tallies$data_availability, "COOPER_RIGHT")` `COOPER_RIGHT` disagreements, `r cc(cooper_right_causes$code_archived, "repo_not_detected")` of `code_archived`'s `r vt(verdict_tallies$code_archived, "COOPER_RIGHT")`, and `r cc(cooper_right_causes$any_readme, "repo_not_detected")` of `any_readme`'s `r vt(verdict_tallies$any_readme, "COOPER_RIGHT")` — a paper's own text names a real, working DOI on a mainstream platform (overwhelmingly Dryad, Zenodo, or Figshare), and `repo_check` never queries it at all. Addressing the conflation and non-detection gaps once, at the level of how Metacheck decides which repository "counts" for a given question and which platforms it recognises, would likely resolve a meaningful fraction of the remaining disagreement across several constructs simultaneously, rather than requiring separate, construct-specific fixes.

Twelve individual software defects identified over the course of this project were reported upstream, fixed, and reverified against a full corpus rerun for this manuscript. Five were found during the original review: the Excel multi-sheet `tabular_usable` limitation underlying most of the original `data_download` disagreement (scienceverse/metacheck#379, resolved: agreement rose from 93.5% to 99.1%), the Dryad unauthenticated-HEAD-request gap affecting both data and code downloads (scienceverse/metacheck#380), the `.zip`-peek authentication gap for archive-only repositories (scienceverse/metacheck#378), the `code_check` zip-discovery architectural gap surfaced while investigating the Zenodo data-download fix (scienceverse/metacheck#383), and a silent-truncation bug in the byte-fetch path that #383's fix newly exposed (scienceverse/metacheck#384): the function decompressing a zip member's bytes called an underlying library routine with no size hint, silently capping any member over 32,768 bytes at exactly that length with no error, rather than the size-aware call the library's own exact-size path rejects for an unrelated reason. Fixing #384 closed the great majority of the gap #383 had left open: `code_download` agreement rose from 66.2% (before #379/#380/#383) to 89.7% (after them) to `r pct1(results$code_download$pct_agree/100)`% (after #384) — a two-stage improvement of over 30 percentage points overall, the largest of any construct in this comparison, and a level of agreement that has held with only `r results$code_download$n_disagree` disagreement remaining across every subsequent fix and rerun described below.

A further seven fixes (Appendix A.5) — Zenodo reliability, wider repository-platform coverage, and a rate-limit handling defect — were applied and reverified against the *entire* 1,861-paper corpus rather than only the papers already known to disagree, specifically to check whether a fix aimed at one construct could have broken an already-correct answer elsewhere. Six of the seven had not; the seventh — the R-package-source-tree exclusion, meant to drop a *bundled dependency's* own scaffolding (`DESCRIPTION`, `NAMESPACE`, `R/`, `man/`, `tests/`) from a repository's file listing — also stripped a paper's *own* analysis code whenever that code was itself packaged as an installable R package, a common practice for ecological modelling and analysis tools shared alongside a methods paper, and in several cases stripped the package's bundled `data/` directory as well, turning a real dataset into an apparent absence of one. This was confirmed against 16 real GitHub/CRAN-hosted repositories (`RevGadgets`, `BaBA`, `m2b`, `RRPP`, `actel`, `scampr`, `MINOTAUR`, `LadderFuelsR`, `biomonitoR`, `EcoEnsemble`, `fossilsim`, `frair`, `tRophicPosition`, `sabinaNSDM`, `bef`, and `phylomice`). Rather than being left as an open limitation, the exclusion rule was corrected within this same review cycle: it now only strips a root-level package's files when nothing classifiable as real data or code survives outside it — using the same `data_classify_files()` rules-based classifier `data_check` itself relies on — distinguishing a study that shares its own data and code *as* an R package (nothing survives outside it, because the package *is* the deposit) from a repository that bundles a vendored copy of someone else's package alongside the study's own files (real content survives outside the vendored package, so only the vendored package's files are excluded). Reapplying the corrected rule resolved `r 16 - cc(cooper_right_causes$code_archived, "r_package_source_excluded")` of these 16 cases; the remaining `r cc(cooper_right_causes$code_archived, "r_package_source_excluded")` are due to an unrelated, still-open gap where the affected repository's own cached download never retrieved its `R/` source directory in the first place, so no exclusion-logic fix can recover content that was never fetched.

We see this kind of construct-by-construct, evidence-grounded mapping — quantifying not just how often Metacheck and a trained human coder disagree, but *why*, down to the individual paper and, where applicable, the specific line of code responsible, reverifying that mapping against a real fix rather than stopping at diagnosis, and checking a fix's effect on the papers it was *not* meant to change as carefully as its effect on the papers it was — as the more useful contribution here than a single aggregate accuracy figure, both for meta-scientists deciding whether Metacheck can currently support a given coding task, and for Metacheck's own development priorities. Appendix A documents, in full detail, every defect identified over the course of this project, the evidence that surfaced it, the exact code change that fixed it, and the before/after numbers at each stage; the body of this manuscript reports only the current, post-fix numbers.

```{r}
#| label: session-info
#| include: false

capture.output(
  sessioninfo::session_info(),
  file = "session-info.txt"
)
```

\newpage

# Detailed record of every Metacheck defect found and fixed during this project {#apx-defects}

This appendix documents, in full detail and in chronological order, every software defect in Metacheck that this project's validation effort identified, the evidence that surfaced each one, the exact code change that fixed it, and the corpus-level numbers before and after that fix. The body of the manuscript reports only the final, current numbers; this appendix exists so that every intermediate claim made in the course of arriving at those numbers remains checkable, without requiring the main text to carry a running commentary on its own revision history. Six rounds of validation are documented below: (A.1) the original empirical-comparison review against Cooper et al.'s coding, which produced issues #378–#384; (A.2) a focused re-examination of `code_check`'s parse-error and package-version-pinning checks; (A.3) a systematic validation of five further `code_check` checks (missing referenced files, hardcoded absolute paths, `setwd()` calls, comment density, and library/import scattering) against real corpus files, which produced five further fixes; (A.4) a file-count gate added after one outlier repository's processing time exposed a gap the existing byte-size caps did not cover; (A.5) a full re-check of every remaining disagreement against Metacheck after five more fixes (Zenodo reliability, repository-platform coverage, and a rate-limit reliability defect found live during the re-check itself); and (A.6) a systemic under-sampling bug found in A.5's own Dataverse DOI-prefix allowlist, two further platform-coverage fixes (DataONE, institutional Figshare instances) and two matching bugs in this project's own comparison code, and a complete, evidence-based categorization of every "repository not detected" disagreement these fixes did not resolve. Fixes described in A.1–A.4 were committed to `scienceverse/metacheck`, branch `repocheck_improvements` (pull request #385); A.5 and A.6's fixes were committed directly to that package's `dev` branch (A.6 as pull requests #410, #412, and #414). Every fix is covered by a new or updated automated regression test in the package's own test suite.

## A.1 Defects found during the original empirical comparison

Six defects were identified while individually reviewing every disagreement between Metacheck and Cooper et al.'s human coding (Empirical Comparison, above): five in Metacheck itself, and one in this project's own comparison code. All six are described here with the same level of detail as in the body text; they are repeated in this appendix only for completeness, so that Appendix A is a single, complete record of every fix made during this project.

**#378 — `zip_peek()`'s unauthenticated requests.** `zip_peek()` (`R/zip-peek.R`) reads a remote zip archive's central directory via an HTTP Range request, without downloading the archive, so a downloader can decide whether the archive is worth fetching before spending the bandwidth. This function's HEAD and Range requests were unauthenticated. Dryad's file-download endpoint answers 401 Unauthorized to *any* request that touches file bytes, including a bare HTTP Range request — confirmed live against a real Dryad file-download URL — so every Dryad-hosted archive's peek failed structurally, before any question of the archive's actual contents. Fix: both requests now route through `.auth_for_url()`, the same host-based authentication dispatcher every other Metacheck download path already uses, so Dryad's token is attached automatically without requiring each call site to opt in individually (an earlier, per-call-site `req_func` opt-in mechanism had only been adopted by 1 of 7 call sites that needed it).

**#379 — `data_check`'s multi-sheet Excel limitation.** `data_check`'s tabular-usability check called `readxl::read_excel()` with no `sheet` argument, so it only ever read a workbook's first sheet. When the first sheet was a cover, metadata, or "read me" sheet — a convention confirmed across many real corpus files, with sheet names including "metadata," "Meta-data," "MetaData," "read me," "ReadMe," "User guide," "LEGEND," and "Description of variables" — a later sheet holding genuine, well-structured tabular data was never inspected, and the file was misclassified as unusable ("100% free text, not variables"). One confirmed case: sheet 2 of a real downloaded workbook held 1,532 rows by 58 real variable columns, never read before the fix. Fix: `data_read_head()` now accepts a `sheet` argument, and `data_check` tries each remaining sheet in a workbook before giving up on the file. This was the single largest driver of `data_download` disagreement: before the fix, `mc_data_download` and Cooper et al.'s `data_download` disagreed on 51 of 967 comparable papers (94.7% agreement); after it, agreement rose to 99.1% (908/916 papers, 8 disagreements remaining), and the resolved cases accounted for 29 of the original 51 disagreements (57%).

**#380 — Dryad's authentication gap on other download paths.** The same unauthenticated-request problem identified for `zip_peek()` (#378) also affected `.remote_size()` and `.remote_content_length()`, two other functions in the download path that check a remote file's size via HTTP HEAD before deciding whether and how to download it. `.remote_content_length()` already had a `req_func` opt-in mechanism for per-host authentication, but only 1 of 7 call sites across the codebase had actually adopted it, so the other 6 still received a 401 from Dryad. Fix: both functions now route through `.auth_for_url()` unconditionally, the same fix applied to #378, closing every remaining unauthenticated-request gap in the download path at once rather than patching call sites one at a time.

**#383 — `code_check` could not see code bundled inside a zip archive.** This was a compound architectural gap with three separate causes, discovered while investigating why `code_check` found no code files at all for several papers whose repository, on manual inspection, clearly contained real analysis scripts bundled inside a `.zip`: (1) `code_check()` never read `data_check`'s already-expanded file structure, so any code file `data_check` had already discovered inside a zip (in the course of looking for data files) was invisible to `code_check` regardless; (2) `code_check` had no zip-peek capability of its own for the case where `data_check` had not already run first; (3) the shared zip-expansion helper `.archive_rows()` discarded code-typed files outright even when it did expand a zip, keeping only `"data"` and `"documentation"`-typed files. Fix: `code_check()` now prefers `data_check`'s structure when available; it gets its own zip-peek fallback (`.code_expand_zip()`) for when `data_check` did not run first; and `.archive_rows()` now keeps `"code"` alongside `"data"`/`"documentation"`. A real, concrete example verified live: a Zenodo record (record 3694205, repository `SharpRT/CMV_Spread`) bundled 4 real MATLAB `.m` files inside a zip that were entirely invisible to `code_check` before this fix. This fix, together with the archive-member content-fetch wiring described immediately below, moved `code_download` agreement from 66.2% (355 comparable papers, 120 disagreements) to 89.7% (358 comparable papers, 37 disagreements) — the first of two stages in this construct's improvement (the second is #384, below).

As part of the same round of work, `repo_check`'s zip-peek expansion was extended to carry not just a discovered code file's *name* (already possible after the fixes above) but its *content*: each expanded row now also carries `archive_url` (the parent zip's own URL) and `archive_member` (the file's exact name inside it), and `download_repo_files()` (`R/repo-download.R`) uses those two fields to fetch that one member's bytes directly, via a byte-range request against the parent archive, without downloading the archive's other contents. This mechanism was verified working in every isolated unit test at the time, but a full end-to-end pipeline run against a real paper still returned no file content for reasons not yet diagnosed at that point — this was filed and tracked as issue #384, described next, rather than merged as "fixed" while a known gap remained open.

**#384 — Two distinct causes behind the archive-member byte-fetch failing intermittently.** Issue #384 was filed as an open question ("archive-member content fetch works in isolation but returned NA once in a full pipeline run") rather than a diagnosed bug, and its investigation spanned two separate validation efforts and uncovered two independent causes.

*Cause 1: silent truncation over 32,768 bytes.* `.zip_inflate_member()` (`R/zip-peek.R`) decompresses one zip member's raw bytes by calling `zip::inflate()`. Passing the member's exact known uncompressed size to that function raised an unrelated "Failed to inflate data" error (a quirk internal to the `zip` package), so the original code left the `size` argument unset instead. `zip::inflate()`'s own documentation states that leaving `size` unset triggers automatic buffer resizing as needed — but, confirmed live against a real Zenodo-hosted zip member, this documented behaviour does not actually happen in practice: any member larger than the default 32,768-byte output buffer came back silently truncated at exactly that length, with no error, no warning, and a `bytes_written` field the calling code never inspected. A concrete confirmed case: a real 44,669-byte code file came back as exactly 32,768 bytes. `.zip_member_fetch()`'s own subsequent length check (comparing the decompressed length against the size recorded in the archive's own central directory) correctly caught this mismatch and discarded the truncated bytes — but the practical, user-visible effect was that every code or data file over 32KB inside a zip silently failed to fetch, indistinguishable from a genuine network or host-compatibility failure. Fix: passing `size + 1` (one byte over the true size) avoids both failure modes — it is no longer the exact size that triggers the package's internal error, and it is large enough that the real output always fits in the up-front buffer rather than depending on the documented-but-non-functional resize path. Verified against both a real archive member under 32KB and one over it, and covered by a new offline regression test using a locally constructed zip file whose one member compresses to roughly 95KB uncompressed. A targeted rerun of the 36 papers affected by this pattern found 27 moved from zero downloadable code files to full or near-full recovery (23 fully, 4 partially), which is what raised `code_download` agreement from 89.7% (37 disagreements) to 97.2% (10 disagreements remaining) — the second of the two stages in this construct's improvement, and the largest single agreement-rate improvement of any construct in the empirical comparison.

*Cause 2: an intermittent, silently-swallowed failure not explained by the truncation bug alone.* Independently of the truncation bug, a second cause was found while investigating why 40 of the archives affected by issue #384 failed *entirely* (every member missing) despite containing no member anywhere near the 32,768-byte threshold. Tracing the actual corpus data (`res_code_check.RData` and its 38 per-batch constituent files, in `cooper_validation_metacheck/manuscript/data/`) showed that a single pipeline run calls `zip_peek()` on the exact same archive URL *twice* — once inside `repo_check` to discover a zip's member names, and again inside `download_repo_files()`'s archive-member-fetch step (added as part of #383/#384's own fix) to retrieve one member's bytes — with no throttling and, critically, no retry logic at all on either call: `zip_peek()`'s own HEAD request and its two Range-request helper functions (`.http_range_tail()`, `.http_range_bytes()`) called `httr2::req_perform()` directly, with no `req_retry()`, and treated *any* non-206/200 HTTP status (including a 429 burst-rate-limit refusal) as an unconditional, silent `NULL` — indistinguishable, by design, from "this host does not support range requests at all." Two back-to-back, unthrottled requests to the same archive URL within one process is exactly the pattern most likely to trip a host's burst-rate limiter, and the *second* call (the byte-fetch, inside `download_repo_files()`) was the one exposed to it. Fix, applied in two parts: (1) all three of `zip_peek()`'s network calls now retry through the same `is_transient`/`backoff`/rate-limit-wait helper functions (`.storage_is_transient_factory()`, `.storage_backoff()`, `.storage_retry_after_factory()`) that every other Metacheck download path already uses, so a 429 is now retried with backoff rather than immediately and silently treated as "unsupported"; (2) a new same-session, in-memory cache (`.zip_peek_cache`, keyed by URL) means the second call to `zip_peek()` on an archive already peeked earlier in the same run reuses the first call's result instead of repeating the network request at all, removing the redundant call — and the rate-limit exposure it caused — entirely rather than merely tolerating it. Verified by a new regression test exercising the cache directly (`test-zip-peek.R`) and by the full package test suite (463 tests passing, 3 pre-existing unrelated skips, 0 failures) after both changes.

**Verdict corrections found by the post-rerun double-check pass.** After the full corpus rerun incorporating #378–#384, every disagreement was independently double-checked a second time (see Empirical Comparison, above, for the check's method). This pass corrected 7 verdict-labeling errors from the original review: 2 in `data_availability` (one moved to `COOPER_RIGHT` after finding the "data" files actually belonged to a cited third-party software dependency's repository, not the paper's own; one moved to `METACHECK_RIGHT` after finding a methods paper's repository, originally read as containing only package example files, in fact holds real trait data and model output), 1 in `data_download` (moved to `COOPER_RIGHT` after confirming a Zenodo-hosted "Functional Trait Database" file had, in fact, already downloaded and still failed the tabular-usability check, rather than remaining `UNCLEAR` on the assumption it had not yet downloaded), and 4 in `code_download` (three rows originally recorded `METACHECK_RIGHT` whose own written reasoning already concluded the opposite, corrected to `COOPER_RIGHT`; one row originally left `UNCLEAR` where the code files were, on direct inspection, confirmed genuinely downloaded, corrected to `METACHECK_RIGHT`). The pass also found one substantial scope correction rather than a single-row relabeling: `code_download`'s dominant post-#383 disagreement pattern was originally tagged in only 13 of its 37 disagreements at the time of the initial qualitative review; re-deriving the pattern systematically against every disagreement's saved `file_location` value found the identical signature (a discovered code file with no resolvable download location) in 35 of the 37, which is what led directly to tracing and fixing #384's second cause, above. Every one of `code_archived`'s 164 disagreements was also individually re-derived against the current `repo_check`/`code_check` file listing during this pass, including the 8 originally resolved via an automated keyword search rather than an individual hand read; this found zero verdict corrections in that column.

**A sixth issue, not in Metacheck but in this project's own comparison code.** `code_data_preparation/03_recreate_cooper_columns.R` derives `mc_data_availability`, `mc_code_archived`, `mc_data_README`, and `mc_code_README` for a paper from `repo_check`'s per-*file* tables (`res_repo_check$table`, `res_data_check$structure`, `res_code_check$table`). A paper for which `repo_check` found zero files anywhere has no row at all in any of those three tables, even though `repo_check`'s own per-paper `summary_table` — which covers every one of the 1861 papers — correctly records `files_n = 0` for it. Because the script built its paper list from the three per-file tables rather than from `summary_table`, every such paper was silently absent from the comparison entirely: its `mc_*` value was not `FALSE`, it simply never existed as a row to compare. Confirmed directly: 495 of 1861 papers were missing this way, including 404 papers Cooper et al. coded `data_availability` `Yes` — 404 real disagreements (cases where Cooper et al.'s coders found a repository Metacheck's own detection had missed) that were never entering the comparison at all, rather than being counted as a genuine miss. Fix: the paper list is now built from `summary_table$paper_id` (already the full 1861 by construction), and `mc_data_availability`, `mc_code_archived`, `mc_data_README`, and `mc_code_README` are explicitly set to `FALSE` for a paper `repo_check` examined and found nothing in; every other `mc_*` column (license, DOI, download, format, language) is correctly left `NA` for such a paper, since those questions remain genuinely inapplicable without a repository to ask about. Every number reported in the Empirical Comparison section above reflects this correction.

## A.2 Re-examining `code_check`'s parse-error and package-version-pinning numbers

A separate line of inquiry, prompted directly by a sentence in an earlier manuscript draft stating that "138 files (1.3%) failed to parse as valid code in their declared language at all," asked two questions: is this the right denominator, and is the file list behind it available for inspection at all.

**Locating the underlying data.** `code_check()`'s per-run output already carries everything needed: a `table` with one row per code file (`file_name`, `language`, `parse_error`, `parse_error_msg`) and a `summary_table` with one row per *paper* (`code_version_pinned`, `code_parse_errors`), both already computed by the module — no new code was needed to make this data available, only to locate and aggregate the 38 saved per-batch corpus-run files (`cooper_validation_metacheck/manuscript/data/batches/res_code_check_batch001.RData` through `batch038.RData`) that had already been produced by the original corpus run.

**Package version pinning: 34.2% was a batch-level upper bound, not a per-paper rate.** An earlier manuscript draft reported that "only 13 of 38 batches (34.2%) contain at least one paper with any form of version pinning," explicitly flagged in that draft's own text as an upper bound on the true per-paper rate because a batch of ~50 papers needs only one pinned paper to count. Checking directly against the saved per-batch `summary_table$code_version_pinned` column (present in every batch, keyed by `paper_id`) confirmed the per-paper detail this draft believed was not retained had, in fact, been retained all along: aggregating it across all 38 batches gives 18 of 400 code-bearing papers (4.5%) with version pinning present — substantially lower than the 34.2% upper bound, as expected, and now a true per-paper number rather than an aggregate-of-aggregates. No code fix was needed here; this was a reporting correction (using data that already existed but had not yet been extracted at the right level of granularity), not a software defect.

**Parse errors: 1.3% used the wrong denominator, and undercounted for a subtler reason.** The originally reported 1.3% divided 138 parse failures by 10,461, the total code-file count across *every* language in the corpus — but parsing is only ever attempted on R-type files (`.R`, `.Rmd`, `.qmd`; `code_parse_r()` is R-only), so the other 3,259 SAS/SPSS/Stata/Python/MATLAB files in the corpus were never eligible to fail this check and should not have been in the denominator at all. Restricting to the corpus's 7,202 R-type files, a further complication emerged: 1,651 of those were never actually downloaded or read at all (an inaccessible repository or a failed download), so parsing was never attempted on them either — they, too, do not belong in the denominator. A further 15 files reached a local copy but errored during *extraction* (before `parse()` itself was ever called), splitting into two genuinely different causes on closer inspection: 11 were confirmed to be genuinely empty (0-byte) files — fetched directly from their original GitHub repositories to confirm the emptiness is a fact about the authors' own repository, not an artefact of Metacheck's download step (e.g. `github.com/olgaviedma/LadderFuelsR`'s `R/foofy.R` and `github.com/dpritchard/frair`'s `tests/testthat/test_emdII.R`, both independently confirmed 0 bytes via a direct `curl` fetch from `raw.githubusercontent.com`) — and 3 were `.Rmd` files that failed during Quarto/knitr's own chunk-extraction step with a genuine, structural fence-mismatch error (a closing code-fence with a different number of backticks or indentation than its opening fence), which is the same underlying "not valid in its declared format" problem a parse error represents, just caught one step earlier in the pipeline than `parse()` itself. Restricting to the 5,536 files that were both locally available and actually reached a call to `parse()`, 138 failed (2.5%) — not 1.3%, and not the 1.92% that a denominator of "all 7,202 R-type files regardless of whether they were ever read" would give either. Including the 3 fence-mismatch failures as the same kind of problem gives 141 of 5,539 (2.5%).

This investigation also surfaced a genuine, previously unknown software defect: **`code_read()` (`R/code_check.R`) crashes on a genuinely empty file.** `readr::guess_encoding()` returns a zero-row result for a 0-byte file, so `enc <- readr::guess_encoding(file_path)$encoding[[1]]` silently produces `NA` rather than a valid encoding string, and that `NA` then crashes deep inside `readr`'s own internals (`if (stringi::stri_enc_isascii(lines))`, which requires a length-one logical and receives `NA` instead) with the unhelpful, generic message `"missing value where TRUE/FALSE needed"` — this is exactly the message recorded for all 11 of the empty-file cases above, rather than a clear "this file is empty" signal. This defect is documented here as confirmed and diagnosed, but **not yet fixed** as of this writing (it affects a small, already-quantified fraction of files — 11 of 7,202 R-type files in this corpus — and a fix has not yet been prioritized ahead of the five `code_check` checks fixed in A.3 below); it is recorded here so the fix, when made, has a clear before-state to compare against.

## A.3 Systematic validation of five further `code_check` checks

A third, more systematic validation exercise checked five of `code_check`'s remaining automated checks — missing referenced files, hardcoded absolute paths, `setwd()` calls, comment density, and scattered library/import lines — against real files from the same corpus, reading every flagged file that had already been downloaded locally (8,218 of 10,461 code-file rows) and sampling up to 100 of the remainder that would have required a fresh download. The full method, every sampled file's judgment, and every quoted example are recorded in a dedicated, reproducible validation report (`code_check_validation.qmd`, with its accompanying script `validate_code_check.R` and judgment tables, all in `cooper_validation_metacheck/manuscript/`) with a fixed random seed (`set.seed(42)`) at every sampling step; this appendix summarizes its findings and the resulting code fixes. Two checks not covered by this validation pass (parse errors, package version pinning) are covered separately in A.2 above.

**Missing referenced files — case-sensitivity bug (fixed).** `code_check`'s check for files a script tries to open but that are absent from the repository (`inst/modules/code_check.R`, `missing_files <- setdiff(base_ref, base_repo)`) compared filenames case-sensitively. 13 confirmed false positives across the sampled files were all the same mechanism: the referenced file exists in the repository under a different letter case, which is not a real error on the author's part on the case-insensitive filesystems (Windows, macOS by default) most authors develop on. Concrete examples, each confirmed directly against the paper's real repository file listing: paper `10_1002_2688_8319_12229` references `REM_tools.r` where the repository holds `REM_tools.R`; paper `10_1111_2041_210x_13923` references `diagnostic_fcns.r`/`boot_glmm.r` where the repository holds `diagnostic_fcns.R`/`boot_glmm.R`; paper `10_1111_2041_210x_13125` references `FoodWeb_Functions.R` where the repository holds `Foodweb_functions.R`; paper `10_1002_pan3_10736` references two scripts whose repository copies differ only in the first letter's case. Fix: the comparison now lowercases both sides before comparing (`missing_files <- base_ref[!tolower(base_ref) %in% tolower(base_repo)]`), removing all 13 confirmed false positives found in this sample and any of the same kind not yet sampled.

**Missing referenced files — `vroom::vroom()` not recognised as a file-reading call (fixed).** The same check's file-reference extractor (`code_file_refs()`, `R/code_check.R`) recognises a fixed list of R reader-function names (`read.*`/`read_*`, `import`, `fread`, `readRDS`, `load`, `readLines`, `fromJSON`, `readtext`, `source`); `vroom::vroom()` does not begin with "read" and was absent from this list, so a file loaded exclusively via `vroom::vroom()` was invisible to the missing-file check regardless of whether it actually existed in the repository. Confirmed false negative: paper `10_1111_2041_210x_13440`'s `R/ncbi.R` calls `vroom::vroom(file.path(dir, "nodes.dmp"), ...)` and a second `vroom::vroom()` call for `names.dmp`; neither file exists in the repository, but the check never flagged either, since `vroom` was not on its keyword list. Fix: `"vroom"` added to the reader-keyword list.

**Missing referenced files — remaining known limitations, not yet fixed.** Two further false-negative mechanisms were confirmed but not fixed, since each would require a more substantial change than a keyword addition or a comparison tweak: (1) `code_file_refs()` only captures a quoted filename appearing on the *same line* as a reader-call keyword, so a file assigned to a variable on one line and read via that variable on a later line (`liz_file <- "example_lizard_data.csv"`, then later `read.csv(liz_file)`) is invisible to the check even when the file genuinely does not exist (confirmed: paper `10_1111_1365_2435_13993`'s `tests/testthat/test-m_run_biophysical.R` does exactly this for three files, none of which exist in the repository). (2) When a referenced filename is built as `paste0(some_variable, "...literal_suffix.csv")`, the check's regex only captures the literal trailing fragment (e.g. `_M_D_abundance_interactions.csv`) rather than the true, variable-interpolated filename — the resulting "missing file" flag is still technically correct (nothing by that literal fragment name exists either), but the name shown to a paper's author is a confusing partial match rather than the file they would recognise; across the corpus, 128 of 2,599 (4.9%) genuinely-missing entries have a name starting with punctuation, the signature of this dropped-prefix pattern.

**Hardcoded absolute paths — three false-positive mechanisms fixed, one left open.** `code_abs_path()` (`R/code_check.R`) regex-matches quoted strings shaped like an absolute filesystem path. Three confirmed false-positive mechanisms were fixed: (1) a single-segment string beginning with `/` (e.g. `self.fetch('/login')` in a vendored web-app test suite, `github.com_ccrisan_motioneye/tests/test_handlers/test_login.py`) is an HTTP route, not a filesystem path — 322 of 4,182 originally matched strings were 6 characters or fewer, a class dominated by exactly this pattern; the regex's bare-`/`-prefixed branch now requires a second `/`-separated segment before matching, which a real absolute path (e.g. `/Users/name`) always has and a bare route never does. (2) An all-digit UNC "host" is a `sub()`/`gsub()` regex backreference string, not a network path — confirmed twice in real code: `osf.io_5fter/IDcallR_sameN_withIDcallPP.R` line 183, `sub('group (\d+)_(\d+)', "\2\1", colnames(clupo))`, where `"\2\1"` was matched as `\\host\share` because a bare digit satisfied the old hostname character class; and a second, independent instance in a Pyrenees-mapping script's `gsub('(.{1,10})(\s|$)', '\1\n', ...)` call, matched for the same reason. The UNC branch's hostname character class now requires at least one letter, which excludes both confirmed cases without excluding any real hostname (no genuine UNC host is all-digit-and-punctuation with no letter at all). (3) The pattern's own pre-existing docstring already flagged a known risk — a variable-built path like `paste0(dir, '/file.csv')` triggering a false match on the literal fragment — and this was confirmed for real: `github.com_YvesBas_Tadarida-C/Sonotypes/write_tabase3HF_Sonotype.R` line 40, `list.files(paste(ListDate[[i]],"/eti",sep=""), ...)`, where `"/eti"` is a relative fragment concatenated onto a loop variable. This third mechanism is addressed by the same "require a second path segment" fix as (1), since `/eti` is itself single-segment. A fourth mechanism, confirmed but **not fixed**: a Python string built by `+`-concatenation from a relative literal (`'data\\' + tile_name + '\\run\\' + model_name + ...`, from a Zenodo-hosted `model_test.py`) is a relative path whose middle segments (`\run\`, `\output\tile\`) still match the UNC branch on their own; no fully static regex-only fix exists for this case, since it would require tracking whether the enclosing expression is a string concatenation starting with a relative literal, which is beyond what a line-based regex can determine. Of the true positives sampled for comparison, 15 of 15 further-checked "real username-shaped" matches (e.g. `C:/Users/reddin/Documents/...`, `/Users/farrer/Dropbox/...`, `/home/michael/Dropbox/...`) were confirmed genuine, machine-specific absolute paths — the large majority of this check's flags are correct.

**`setwd()` calls — no false positives found in this corpus; one confirmed-but-unobserved risk noted.** All 194 distinct `setwd()` call strings found across the sampled files are genuine, live, executable calls, including calls whose argument is itself relative or dynamic (`setwd("./data")`, `setwd(dir)`, `setwd(tempdir())`) — these correctly count as flags under this check's own stated rule, since the anti-pattern being flagged is changing the working directory at all, not specifically a hardcoded absolute-path argument. A latent false-positive mechanism was confirmed by construction (a synthetic test, not a real corpus case): `code_setwd()` has no awareness of string-literal context, so a line like `message("Please run setwd(your_path) before continuing")` would be matched as if it were a live call. Scanning all 194 real call strings in the corpus for instructional-text markers ("please," "before," "instructions," "note:") found zero real occurrences of this pattern — a real, demonstrated risk with no confirmed instance in this corpus, and left unfixed for that reason, though `code_setwd()` could straightforwardly reuse the same quote-context-tracking logic already implemented for `.code_strip_inline_comment()` if a future corpus surfaces a real case.

**Comment density — a Python-specific docstring signal added (not a bug fix).** `code_remove_comments()`'s Python branch deliberately never treats a triple-quoted string as a comment, since doing so would also destroy real docstrings (themselves ordinary string literals, syntactically). The consequence, quantified directly: of 280 zero-comment-flagged Python files in the corpus, 200 (71.4%) contain at least one complete triple-quoted docstring block — real documentation that the mechanical `#`-only comment count cannot see, and so reports as "0% comments" regardless. Five were read directly to confirm these are genuine module/function docstrings rather than incidental triple-quoted data, e.g. `model_runs.py`'s `"""Filters for Model Runs."""` and `features.py`'s 16 separate triple-quote markers (8 docstrings) opening with `"""API functions to interact with feature names."""`. This is a deliberate, correctly-reasoned design choice in `code_remove_comments()`, not a bug — stripping docstrings to count them as comments would also delete them from every downstream check that reads code text — so the fix made is additive rather than corrective: a new function, `.code_has_docstring()`, detects whether a file contains at least one complete triple-quoted block, and `code_line_stats()` now returns this as a separate `has_docstring` field (`NA` for every non-Python language) alongside the unchanged `percent_comments` metric. `inst/modules/code_check.R`'s report text now adds an explanatory note whenever a zero-comment Python file in fact has a docstring, so a reader is told the file is documented via docstrings rather than concluding it has no documentation at all.

**Scattered library/import lines — Python import-anchor tightened (fixed).** `code_library_lines()` (`R/code_check.R`) previously anchored its Python import-detection regex on the bare keyword plus a following word (`^\s*(import|from)\s+[A-Za-z_.]`), with no requirement that the rest of the line actually form a valid import statement. Because Python's comment-removal never strips triple-quoted strings (the same mechanism behind the comment-density finding immediately above), docstring *prose* that happens to start with "from " or "import " survives into this scan and was matched as if it were a real import line. Concrete, exact example: `github.com_openvinotoolkit_cvat/site/process_sdk_docs.py`, line 213, inside a docstring spanning lines 211–214 — the prose sentence "        from the generated model and api descriptions." was matched as an import line at line 154 of the comment-stripped text, while the file's 10 real imports are all genuinely contiguous at lines 1–10; the spurious match alone widened the reported gap between imports to 144 lines, crossing the "scattered" threshold (more than 3 non-comment lines between library statements) on a file whose real imports are, in fact, perfectly grouped. Quantified across all 525 Python files flagged as scattered in the corpus: 155 (29.5%) have at least one spurious, non-import match of this kind; of those, 68 (13.0% of all 525 flagged files) would no longer be flagged as scattered at all once the spurious matches are excluded — pure false positives caused entirely by this mechanism (the remaining 87 files with a spurious match are still genuinely scattered even after excluding it). R showed essentially no equivalent problem in a 60-file sample (the one apparent candidate, on manual inspection, was a genuine conditional `require()` call, not a false positive — R's regex requires an opening parenthesis directly after the keyword, structurally harder to spuriously trigger than Python's bare whitespace-plus-word anchor). Fix: the Python pattern now requires the full import shape rather than just the leading keyword — a `from` line must also contain its own `import` keyword later on the same line (`^\s*from\s+[A-Za-z_][A-Za-z0-9_.]*\s+import\s`), and a bare `import` line must be followed by a comma-separated identifier list with an optional `as name` and nothing else (`^\s*import\s+[A-Za-z_][A-Za-z0-9_.]*(\s*,\s*[A-Za-z_][A-Za-z0-9_.]*)*(\s+as\s+\w+)?\s*$`) — verified against the docstring false-positive example above (now correctly unmatched) and against every real import shape found in the corpus sample, including multi-line `from x import (a, b, c)` continuations (matched on their opening line) and indented imports, with no loss of any real detection.

**Status of the fixes in this appendix.** All Metacheck fixes described in A.1 and A.3 (nine in total: #378, #379, #380, #383, both causes of #384, and the five `code_check` fixes from the systematic validation) have been committed to `scienceverse/metacheck`'s `repocheck_improvements` branch (pull request #385) and are covered by the package's automated test suite (463 tests passing at time of writing, 0 failures, 3 pre-existing skips unrelated to these changes). The sixth fix described above (the comparison script's missing-repository default) is not a Metacheck fix and has been committed instead to this project's own `code_data_preparation/03_recreate_cooper_columns.R`, in the `cooper_validation_metacheck` repository. The one defect identified but not yet fixed (`code_read()`'s crash on an empty file, A.2) and the two `code_file_refs()` limitations noted but not yet fixed (A.3) remain open. A further full corpus rerun, incorporating the five A.3 fixes (which have not yet been reflected in any corpus-wide number reported in the body of this manuscript), is planned but had not yet been performed as of this writing; the numbers reported in "Results you get for free alongside Metacheck" above reflect the corpus as it stood before those five fixes and will be updated once that rerun is complete. This is a distinct, still-open item from the rerun described in Appendix A.5 below, which re-checked only the papers with a remaining disagreement (not the full corpus) and tested a different set of fixes (Zenodo reliability, repository-platform coverage, and rate-limit handling), not the five A.3 `code_check` fixes.

## A.4 A repository excluded from processing by file count

During the corpus rerun incorporating the A.3 fixes, one paper's data repository — Zenodo record 10.5281/zenodo.3971689, SAPFLUXNET (a global database of sap flow measurements: 202 datasets from 121 locations, sap flow and environmental time series for 2,714 individual plants) — was found to hold approximately 4,000 individual files. Downloading and, in particular, `data_check`'s per-file classification and full-content read of every one of those files (`data_check_head(..., n_rows = Inf)`, by design, since several of `data_check`'s validation checks need the complete dataset rather than a sample) took several hours and multiple gigabytes of memory for this single paper, out of 1,861 in the corpus, before the run was stopped.

This exposed a real gap in Metacheck: `download_repo_files()` already gates a repository outright by total byte size (`max_download_size`) or per-file byte size (`max_file_size`), but had no gate on file *count* — a repository holding thousands of individually small files was not caught by either existing cap. A new parameter, `max_files_per_repo` (`R/repo-download.R`, threaded through `data_check()` and `code_check()`), gates a repository by file count alone, using the same refusal/reporting mechanism as the existing size caps. This has been committed to the `repocheck_improvements` branch alongside a regression test, and the corpus rerun was configured with `max_files_per_repo = 1000`.

Under this cap, the SAPFLUXNET repository is refused outright rather than downloaded, so this one paper's `data_check`/`code_check` results are incomplete (no files analysed for it) in the corpus run reported in this manuscript. This is a deliberate, scale-driven exclusion of a single outlier repository, not a defect in how that paper's data was assessed — the cap exists specifically so that one exceptionally large repository cannot block or degrade processing of the other 1,860 papers in the corpus. Revisiting this one paper's repository with a raised or absent cap, as a separate, deliberate pass, remains an open option.

## A.5 A targeted rerun on every remaining disagreement, after further platform-detection and reliability fixes

After Appendix A.1–A.4's fixes and the resulting full corpus rerun, every remaining disagreement between Metacheck and Cooper et al.'s coding (991 rows across 989 papers, the same set individually adjudicated for the Empirical Comparison above) was re-checked a further time against Metacheck as it stood after seven more commits landed on `scienceverse/metacheck`'s `dev` branch: two fixing crashes and false negatives in Metacheck's Zenodo integration, three widening which repository *platforms* `repo_check` can locate a repository on at all (targeting "repository not detected," the single largest recurring disagreement cause identified in the original review — see "The five recurring causes" above), and two fixing a rate-limit reliability defect surfaced live during this rerun itself. Rather than reprocess the full 1,861-paper corpus, only the 989 papers with at least one open disagreement were rerun, one paper at a time (so that a single paper's slow host response could not block any other), reusing the shared on-disk repository-file cache from the original corpus run so that a repository already fetched and unchanged cost no new download.

**Zenodo reliability.** Two fixes addressed real crashes and false negatives in Metacheck's Zenodo integration, confirmed against Zenodo records already present in this corpus. `online()`, the function `repo_check` calls to confirm a host is reachable before querying it, treated a single transient DNS lookup miss as "Zenodo is offline" and abandoned that paper's entire Zenodo retrieval rather than retrying; it now retries. Separately, a JSON metadata field arriving as a length-zero value (an empty array) rather than `NULL` defeated the `%||%` operator used throughout Metacheck's metadata-extraction code (which only guards against `NULL`, not length-zero), producing a `data.frame()` "arguments imply differing number of rows" error that was silently swallowed inside a `tryCatch`, discarding the whole record; a new `%empty_or%` operator, applied everywhere the same gap existed (Dataverse, Dryad, DSpace7, Figshare, GitHub, GitLab, OSF, PsychArchives, and ReShare, not just Zenodo), closes this. A further, closely related pair of crashes was found and fixed the same way: a Zenodo record Metacheck could not read at all previously returned a `data.frame()` with only `zenodo_id`/`error` columns, so a paper whose every Zenodo record was unreadable produced a metadata table with no `doi`/`license` columns at all, which crashed `repo_check()`'s own Zenodo-metadata-extraction step for that paper the same "differing number of rows" way; and a `repo_url` arriving as a list column (rather than a plain character vector) could silently explode `data.frame(zenodo_url = <list>)` into one column per list element instead of the expected single column. Both are now guarded.

**Repository platform coverage.** Three commits substantially widened the set of hosts Metacheck's `repo_check` can locate a repository on at all, directly targeting the "repository not detected" cause responsible for the largest share of the original disagreement (see "The five recurring causes" above, which named DataSTORRE, DIGITAL.CSIC, AADC, SRA/GenBank, KNB, Neotoma, CIRAD Dataverse, and ForestPlots.net as example platforms with no backend at the time). Mendeley Data (detected via `10.17632/` DOIs and `data.mendeley.com` URLs, queried through the public, unauthenticated `data.mendeley.com/public-api/datasets/<id>` endpoint) and DataONE (a federation of independently-run repositories rather than one hosted service; four member nodes verified live and wired in — Arctic Data Center, KNB, Taiwan Forestry Research Institute, and the Smithsonian Tropical Data Portal, each mounting the same underlying REST API at a different base path) were added as new platforms entirely. Separately, Dataverse's recognised-installation list was expanded from 50 to 121 hosts, 16 institutional Figshare white-label front ends were added, and DSpace support was generalized from PsychArchives specifically to any host running the same legacy (≤6) API (5 more verified live) plus a new implementation covering 64 DSpace 7 installations (e.g. Cornell's eCommons, Georgia Tech's Digital Repository, ETH Zurich's Research Collection) — every one of these 121 + 16 + 5 + 64 hosts confirmed live via its own version/info endpoint before being added, not merely listed from a registry. A further, smaller fix excludes an R package's own source tree (`DESCRIPTION`/`NAMESPACE`/its `R/`/`man/`/`tests/` subdirectories) from a repository's data/code file listing, on the reasoning that reusable software infrastructure bundled alongside a study's own materials is not itself the study's data or analysis code and should not inflate `files_n`/`files_code` or appear in downstream reports.

**A reliability defect found live during this rerun.** While this rerun was in progress, a single paper stalled repeatedly at the same point across two separate attempts: `zip_peek()`'s HEAD request and its Range-request follow-up (`.http_range_tail()`, `R/zip-peek.R`), used to read a remote zip archive's file listing without downloading it, each independently hit Zenodo's rate limit and each, independently, paid the full announced wait for the host's confirmed reset — three consecutive confirmed-rate-limit waits back to back for what was, from Zenodo's own side, a single rate-limit window, since neither request had any way to know the other had already discovered and waited out the same limit. (The rate-limit-wait message itself was also, at the same time, made to name the specific host responsible — Zenodo, Dryad, GitHub, or GitLab, the only hosts that expose a machine-readable reset time — rather than reporting only "the host's own reset," a smaller, secondary fix made in the course of diagnosing this one.) Fix: a session-scoped record of the last confirmed rate-limit reset per host, written the first time any request discovers one and consulted by every subsequent request to that host before it is even sent, so a host already known to be rate-limited waits out only the genuinely remaining time once, rather than every independent request rediscovering the identical window from a fresh 429. Verified with new regression tests covering the record/lookup logic directly (round-tripping a wait, keeping the later of two recorded resets, clearing an expired window, and the pre-flight wait actually sleeping the correct duration) and confirmed live: the same paper that previously stalled for over 40 minutes across three stacked waits resolved in roughly 3 minutes with zero confirmed-rate-limit waits after the fix, the remaining time attributable to Zenodo's own server-side response latency for that specific record (confirmed independently: a single isolated request to the same record, made outside Metacheck entirely, itself took 30 seconds and returned a 504 on a second attempt).

**Results of the rerun.** Across the 1,532 individual construct-level disagreements re-checked (989 papers × up to 7 constructs each, matching however many constructs a given paper had originally disagreed on), 76.8% (1,176 of 1,532) are now resolved — Metacheck's fresh result agrees with Cooper et al.'s original human coding where it did not before — with 348 still disagreeing and 1 now returning a value that could not be classified as agreeing or disagreeing (`data_license`, a repository whose licence field this rerun could not read for reasons not yet diagnosed). By construct: `any_readme` 548/625 resolved (87.7%), `data_availability` 339/424 (80.0%), `code_archived` 252/360 (70.0%), `data_archive` 12/56 (21.4%, evaluated by set membership — a paper's platform coded by Cooper now appearing among Metacheck's own, possibly multi-platform, detected set, since a paper can genuinely link more than one repository), `data_license` 16/57 (28.1%), `data_download` 9/9 (100%), and `code_download` 0/1 (the sole remaining `code_download` disagreement in this corpus). The comparatively modest improvement in `data_archive` and `data_license` is consistent with the original review's own finding that these two constructs' disagreement was, unlike `data_availability`/`code_archived`/`any_readme`, not dominated by the repository-detection cause these fixes targeted (`data_license`'s largest cause was, per "Opposite direction" above, cases where Metacheck was already right and Cooper's own coding had missed a real licence field) — a fix aimed at finding more repositories naturally does less for a construct whose disagreement was rarely about a missing repository in the first place. This rerun's full row-level detail (every paper, every re-checked construct, the value before and after, and whether it resolved) is recorded in `cooper_validation_metacheck/manuscript/data/rerun_disagreements_comparison.csv`, produced by `rerun_disagreements.R`; the underlying per-paper `repo_check`/`data_check`/`code_check` results are cached per paper in `data/rerun_batches/` for inspection or a further rerun without recomputing what has not changed.

**Checking the rest of the corpus for regressions.** This rerun was scoped to the 989 previously-disagreeing papers only — a deliberate choice at the time, to get a fast answer to "did these fixes help" without the cost of a full 1,861-paper rerun (see the rerun's own header comment for the reasoning). That scoping left one real question open: none of these seven fixes were written to only affect a disagreeing paper, so it remained possible that a fix which resolved one paper's disagreement had, in a different paper that already agreed with Cooper et al., turned a correct result into an incorrect one — most plausibly the R-package-source-tree exclusion (if a paper's own analysis code happens to be organised as an R package) or the expanded Dataverse/Figshare/DSpace/Mendeley/DataONE host recognition (a newly-recognised host matching something that should not have counted). This was checked directly: the remaining 868 papers (every paper not in the 989-paper disagreement set) were also rerun, using the identical per-paper, resumable approach, and the full corpus's `cooper_vs_recreated.RData`/disagreement worklist were then rebuilt from the combined result (all 1,861 papers) rather than just the 989. At the level of aggregate agreement rates, this full-corpus check was reassuring: the three constructs this comparison's own disagreement was concentrated in — `data_availability`, `code_archived`, `any_readme` — all showed a higher, not lower, agreement rate once the previously-agreeing papers were included, and `data_download`/`code_download` (both already above 99%) moved by less than a percentage point in either direction. But an aggregate rate rising is consistent with a handful of individual papers having genuinely regressed, provided enough *other* papers improved to more than offset them — and that is exactly what the case-by-case review below found.

**A confirmed regression, found and fixed within this same cycle.** The suspicion named above turned out to be correct: the R-package-source-tree exclusion did break papers it should not have touched. The exclusion was written to detect an R package's fingerprint (a `DESCRIPTION` and `NAMESPACE` file in the same folder) and drop that folder's contents — the package's `R/`, `man/`, `tests/`, `vignettes/`, `data/`, `inst/`, and `src/` subdirectories — from a repository's file listing entirely, on the reasoning that a bundled, reusable software dependency is not itself a study's data or analysis code. That reasoning holds when the package is a genuine dependency vendored alongside a study's own files, but it does not hold when the paper's *own* contribution — its data, its analysis code, or both — is itself packaged and distributed as an installable R package, a common practice in ecological/evolutionary methods work. In that case the exclusion strips the paper's own materials, leaving nothing behind: `repo_check`'s listing for the affected repository showed only packaging scaffolding (`.Rbuildignore`, `.gitignore`, `NEWS.md`, `README.md`, `cran-comments.md`, a bare `.Rproj` file), with the package's real `R/` source — and, for packages that bundle their own example or study data under `data/`, the actual dataset — entirely absent.

A corpus-wide scan for this exact symptom (a repository whose only surviving files, after the exclusion ran, were scaffolding, with zero files classified as data or code) surfaced candidates across the full 1,861-paper corpus, each individually verified against the repository's real GitHub listing (via `gh api`) or Dryad/Zenodo record before being counted: 16 confirmed true instances (`RevGadgets`, `BaBA`, `m2b`, `RRPP`, `actel`, `scampr`, `MINOTAUR`, `LadderFuelsR`, `biomonitoR`, `EcoEnsemble`, `fossilsim`, `frair`, `tRophicPosition`, `sabinaNSDM`, `bef`, and `phylomice`), plus several candidates from the same scan that turned out to be unrelated causes once checked directly (a repository with no `DESCRIPTION`/`NAMESPACE` at all, and several Dryad/Zenodo-hosted papers whose `code_archived` disagreement traced to an unconnected, pre-existing detection gap — code cited in a journal's own Supporting Information, or a repository never located by `repo_check` at all). Two confirmed cases (`BaBA`, a GitHub-hosted barrier-behaviour-analysis package whose `data/` folder holds the actual tracked-animal datasets for its own paper, and `MGDrivE`, a general-purpose mosquito gene-drive simulation package vendored inside a study-specific fork) between them illustrated the structural distinction the fix needed to draw: `BaBA`'s package sits at its repository's root with nothing else present — the package *is* the deposit, so nothing should be excluded — while `MGDrivE`'s vendored copy is nested one level deep inside the fork, with the study's own `Examples/` scripts and data sitting as real, undisputed siblings at the repository root.

The corrected rule preserves the original exclusion's logic for a nested package (still always excluded, since a nested package by construction always has something else in the repository for it to sit alongside) but adds one check for a package detected at a repository's *root*: before excluding it, check whether anything outside the package folder classifies as real data or code, using `data_classify_files()` — the same rules-based classifier `data_check` itself uses elsewhere in the pipeline, rather than a separate, bespoke list of what counts as "real content." If nothing does, the package is not excluded at all, since there is no "outside" for the study's own materials to live in. One implementation detail required a second pass: an RStudio project marker file (`*.Rproj`) classifies as `"code"` under `data_classify_files()` purely by its file extension, which would have wrongly counted as "real content survives" for every package that ships one (nearly all of them) — an RStudio project file is packaging configuration, not an analysis script, so it is excluded from this specific check. The fix was verified against two new regression tests (a root-level package with nothing else present, confirming it is no longer excluded, and a nested vendored package alongside real sibling content, confirming the vendored files are still excluded while the sibling content survives) alongside the existing test suite, then reapplied to the 38 papers the corpus-wide scan had flagged.

Reapplying the corrected exclusion resolved `r 16 - cc(cooper_right_causes$code_archived, "r_package_source_excluded")` of the 16 confirmed cases outright. The remaining `r cc(cooper_right_causes$code_archived, "r_package_source_excluded")` continue to show `code_archived` disagreement, but for a distinct and unrelated reason discovered while reprocessing them: their cached downloaded files never included the package's `R/` source directory in the first place — only packaging scaffolding was ever fetched from the host — so the corrected exclusion logic correctly finds nothing outside the (never-fully-downloaded) package to preserve, because nothing beyond scaffolding was ever retrieved. This is a fetch-completeness gap, not an exclusion-logic problem, and is not further diagnosed here; it is recorded as a separate, still-open limitation rather than folded into a claim about the exclusion fix's own effectiveness. Two of the 16, `phylomice` and `morton` — cases surfaced by the same corpus-wide scan but outside the original 13-paper set found during the initial regression check — resolved to, respectively, `METACHECK_RIGHT` (`phylomice`'s six R source files are a genuine methods contribution the paper's own text never explicitly claims as "archived code," but which Metacheck is nonetheless correct to report) and `COOPER_RIGHT` (`morton`'s 37 R source files are unambiguously this paper's own phylogenetic-analysis code, which Cooper et al.'s coders had missed).

## A.6 A systematic platform-coverage audit, three further metacheck fixes, and a complete categorization of every remaining repository-detection disagreement

A sixth round of work started from a single case the previous rounds had not caught: a paper citing a Dataverse installation (`borealisdata.ca`, Borealis, the Canadian national repository) under a DOI prefix Appendix A.5's Dataverse allowlist did not recognise. Tracing why surfaced a systemic problem in how that allowlist had been built, and prompted a full re-audit of every remaining "repository not detected" disagreement in the corpus rather than a single-paper patch.

**A systemic under-sampling bug in the Dataverse DOI-prefix allowlist.** Appendix A.5's per-host Dataverse DOI-prefix allowlist (`.dataverse_doi_prefix_hosts()`) was originally built by sampling the first 25 DOIs DataCite's search API returned for each host — a sample, not a census. This badly under-counted any host with more than 25 real DOIs registered, which turned out to be the majority of the 121 known hosts; `borealisdata.ca` alone has minted DOIs under six distinct prefixes, of which the original allowlist recorded only one. Rebuilding the allowlist using DataCite's facet aggregation (`disable-facets=false` on its `/dois` search, which returns every distinct prefix in use for a host, with its real count, in one request rather than a sample) found 100 distinct prefixes across the same 87 hosts, not 87 — including a second Harvard Dataverse prefix (`10.26300`, alongside the dominant `10.7910`) that the original sample had also missed. Verified live before and after: the DOI that surfaced this bug (`10.7939/DVN/M6Q2PE`, Borealis) now resolves correctly, and the second Harvard prefix now resolves to `dataverse.harvard.edu`. This was reported and merged upstream as scienceverse/metacheck#410.

**Two further platform-coverage gaps found and fixed the same way.** `.figshare_id()` did not recognise a Figshare article URL with no resource-type segment (`figshare.com/articles/<slug>/<id>`, as opposed to `figshare.com/articles/dataset/<slug>/<id>`) — an older, still-current URL shape (confirmed live against a real corpus citation) that `figshare_links()` already detected as a Figshare link but could not resolve to a usable article id, so `repo_check` never actually queried it (scienceverse/metacheck#412). Separately, `dataone_links()` had no entry for `data.piscoweb.org` (PISCO, a UC Santa Barbara-run DataONE member node), and `.dataone_pid()`'s bare-DOI regex could not handle a DOI suffix containing a further slash — PISCO's own DOI shape (`10.6085/AA/<id>`) — so this platform's citations, while real DataONE member-node DOIs, were invisible end to end. Both fixed and merged as scienceverse/metacheck#414, which also added 29 further institutional Figshare instances (28 found by searching DataCite's client registry for "figshare" in the client name, plus Monash University's `bridges.monash.edu`, found separately since its DataCite client is registered under the institution's own name) — each confirmed live, the same way as every host already in `.figshare_vanity_hosts()`, to answer Figshare's own single-page-app shell rather than a real API response, and each institutional DOI prefix confirmed live to resolve to that exact host before being added.

**Two matching bugs in this project's own comparison code, not in Metacheck.** `03_recreate_cooper_columns.R`'s `.repo_url_platform()` — the function that labels which platform `mc_data_archive` reports for a paper — had a Dryad branch that only matched the single most common DOI prefix (`10.5061`), and a Figshare branch that only matched the literal `figshare.com`/`10.6084` domain and prefix, missing every one of the alternate Dryad prefixes and institutional Figshare instances Metacheck itself already recognised after the fixes above. The practical effect was a paper whose repository *was* now correctly found and retrieved still showing a `data_archive` disagreement, because the label fell through to the generic "Other repo/database" instead of naming the real platform. Both branches were rewritten to read directly from Metacheck's own `.dryad_doi_prefixes()`/`.figshare_vanity_hosts()`/`.figshare_doi_prefix_hosts()` rather than duplicating either list by hand, so this classification cannot drift out of sync with what Metacheck itself recognises again.

**Reprocessing every paper these fixes could plausibly affect.** Rather than assume the fixes above were the only remaining cause of repository-detection disagreement, every "repository not detected" comment still open in the worklist (351 individual (paper, column) disagreements across 233 papers, after excluding platforms already confirmed unsupported for an unrelated reason) was checked again: first narrowed locally, with no network calls, to the papers whose cited DOI prefix genuinely matched one of the platforms just fixed (27 candidates, after excluding two DOI prefixes that coincidentally collide with an unrelated platform's registered prefix in DataCite's own data — `10.6084`, Figshare's own prefix, and `10.17617`, Edmond's — neither of which any fix above touched), then live-verified one at a time. Of those 27, 13 were genuinely resolved by the fixes above; the remaining 14 were not — some detect the citation correctly but the dataset is embargoed or restricted at the source (confirmed via the repository's own API returning an explicit "cannot be viewed" message, not a Metacheck-side failure), and a few still do not detect the citation at all, for reasons unrelated to any fix in this round. A further, separately-run check across every remaining "never located" comment surfaced one exact repeat of Appendix A.1's original zip-peek limitation on a much larger scale (24 papers whose Zenodo/Figshare/Dataverse archive was never successfully peeked during an earlier corpus build, confirmed live, unmodified, to peek correctly today — a stale corpus row in every one of the 24, not a code defect). A further paper, initially suspected to be a second such stale row (its earlier 4TU fetch crash was already fixed in Appendix A.1 and appeared simply never rerun since), was checked directly against `rerun_disagreements_comparison.csv`'s own before/after values and found to still disagree after being rerun — the 4TU fetch failure was not, in fact, resolved, so this one is instead counted with `UNSUPPORTED_REPO` in Appendix A.6's categorization below rather than as a stale row. All resolved candidates from this round were rerun end to end (`repo_check`, `data_check`, `code_check`) and patched into the corpus; none of this round's rerunning touched a paper outside the specific set each check identified, so no regression check across the unaffected remainder of the corpus was needed the way Appendix A.5's broader platform-coverage changes required.

```{r}
#| label: a6-categorization-load

# Computed by code_data_preparation/scratch_final_classify_v3.R (see that
# script's own header for the full derivation): every paper still showing
# a "repository not detected" disagreement after every fix and rerun in
# this appendix, individually categorized by verified root cause.
a6_cats <- read.csv("data/repo_not_detected_categorization.csv", stringsAsFactors = FALSE)
a6_cats <- a6_cats[!duplicated(a6_cats$article_id), ]
```

**A complete categorization of every disagreement this round could not resolve.** After every fix and rerun above, `r nrow(a6_cats)` papers still showed at least one "repository not detected" disagreement. Rather than leave this residual as an undifferentiated count, every one was individually categorized by its actual, verified cause — reading the paper's own extracted text and, where relevant, querying the cited platform's own API directly, the same evidence standard used throughout this manuscript — into one of the following buckets, with zero left uncategorized:

```{r}
#| label: a6-categorization-table
#| tbl-cap: "Table A.6. Final categorization of every remaining 'repository not detected' disagreement, by verified root cause."

a6_tab <- as.data.frame(table(a6_cats$category), stringsAsFactors = FALSE)
names(a6_tab) <- c("Category", "n papers")
a6_labels <- c(
  UNSUPPORTED_REPO = "Real, named repository; a genuine, still-open Metacheck platform-coverage gap",
  SPLIT_DOI_EXTRACTION = "PDF-to-text extraction inserted whitespace inside the DOI/URL itself, breaking every current regex",
  NCBI_GENBANK = "Domain-specific bioinformatics accession (SRA/GenBank/BioProject/MG-RAST) -- a different kind of repository than the general-purpose data archives this package targets",
  REFERENCES_ONLY = "Citation appears only in the reference list; text_search() excludes references by default for every backend",
  EDI_ENVIRONMENTAL_DATA_INITIATIVE = "Environmental Data Initiative -- a real, recurring platform, not yet supported",
  SUPPLEMENTARY_MATERIALS = "No external repository at all -- data embedded directly in the paper's own supplementary files",
  EIDC_NERC = "NERC Environmental Information Data Centre -- a real, recurring platform with a confirmed live API, not yet supported",
  EMBARGOED_OR_RESTRICTED_AT_SOURCE = "Confirmed, via the repository's own API, to be genuinely inaccessible -- not a Metacheck defect",
  PANGAEA = "PANGAEA data publisher for earth and environmental science -- a real, recurring platform with a documented API, not yet supported",
  TEXT_EXTRACTION_TRUNCATED = "PDF-to-text extraction cut the DOI off mid-string -- unrecoverable without re-extracting from the source PDF",
  CRAN_CODE_PACKAGE = "A real, working CRAN package citation -- not a data repository, so out of repo_check's scope by design, not a detection failure",
  USGS_SCIENCEBASE = "USGS ScienceBase -- a real, recurring platform with a confirmed live API, not yet supported",
  FIGSHARE_SHARE_LINK = "An opaque private Figshare share-link with no resolvable article id -- a documented, structural limitation"
)
# match by the category's own character value, not its factor code -- a
# stray as.data.frame(table(...)) factor column here previously caused
# a6_labels[...] to index by integer level rather than by name, silently
# scrambling every label's pairing with its count.
a6_tab$Category <- a6_labels[as.character(a6_tab$Category)]
a6_tab <- a6_tab[order(-a6_tab$`n papers`), ]
flextable::flextable(a6_tab) |> flextable::width(1, 4.5) |> flextable::width(2, 0.8)
```

Two categories are worth distinguishing explicitly from a genuine Metacheck defect, since the difference bears directly on whether this residual is fixable at all. `EMBARGOED_OR_RESTRICTED_AT_SOURCE` (confirmed by querying the repository's own API directly: Dryad's own dataset endpoint, for every one of these, returns an explicit "Identifier cannot be viewed. Either you lack permission to view it, or it is missing required elements" message, not a Metacheck-side error) and `TEXT_EXTRACTION_TRUNCATED` (the DOI is cut off mid-string in the paper's own extracted text, before it ever reaches any Metacheck detection logic at all) are not repository-coverage gaps; no platform-support fix could close either one, since the citation itself is unrecoverable or the data is genuinely withheld. `CRAN_CODE_PACKAGE` is a related but distinct case: the paper's own code is a real, working, publicly available CRAN package, correctly outside `repo_check`'s scope (CRAN is a code-package registry, not a data or code *repository* in the sense every other platform this package supports is), so this is a scope boundary rather than a defect. `SPLIT_DOI_EXTRACTION` (41 papers) is the same underlying mechanism documented for `data_availability`'s `other` bucket earlier in this manuscript, now confirmed to recur for Dryad DOIs specifically as well as the generic `doi.org` case already known, and is filed as a currently open, unfixed limitation in Metacheck's own text-extraction pipeline rather than in any individual platform backend. `EDI_ENVIRONMENTAL_DATA_INITIATIVE`, `EIDC_NERC`, `PANGAEA`, and `USGS_SCIENCEBASE` are each confirmed to be real, recurring, appropriately-scoped platforms with a genuine, documented public API (verified directly against each platform's own API documentation) — the largest, most tractable remaining coverage gaps this audit identified, each affecting enough papers on its own to be worth a dedicated backend rather than folding into the generic `UNSUPPORTED_REPO` bucket, which remains the largest single category (107 papers) precisely because it aggregates every platform that appeared only once or twice in this corpus, for which a dedicated backend would fix one paper at a time rather than a whole recurring class of citation.

## References

