---
title: "01-nutrient-targetting-SAUP"
output: html_document
date: "2024-07-10"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Analysis 1: Summarising biomass data in SAU available for comparison with SDMs

Our first analysis compares the catch tonnage in the Sea Around Us project database with the micronutrient properties from the species distribution and species biomass models. This script produces the results in section Figure 1 in the main manuscript and the summary statistics in the methods + results sections titled *Coupling known reef fish catch and micronutrient ecosystem potential*.

### Read in preamble

Packages:
```{r load packages, echo = F,  results = 'hide'}

my_packages <-  
  c('tidyverse', 'plyr', 'raster', 'sp', 'sf','tmap', 'tmaptools', 'scico', 'ggExtra',
    'factoextra', 'FactoMineR', 'corrplot', 'matrixStats', 'ggrepel', 'GGally', 'ncdf4',
    'scales')
not_installed <- my_packages[!(my_packages %in% installed.packages()[ , 'Package'])]   
if(length(not_installed)) install.packages(not_installed)  
lapply(my_packages, function(x) library(x, character.only = T))

```

Outputs:
```{r}
dir.create('figures-final-v4/03-nutrient-targetting/', recursive = T)
```


Pre-loaded data:
```{r load in data}

# load in preamble containing multiple datasets
load('scripts/results-final/01-main-analysis/preamble.RData')

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

```


Nutrient SDM model data:
```{r load in biomass and micronutrient data}

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

# load in species x site matrix for biomass and nutrients
biomass_index_wide      <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/biomass_index_wide.RDS')
calcium_wide            <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/calcium_wide_MASS.RDS')
iron_wide               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/iron_wide_MASS.RDS')
vitamina_wide           <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/vitamina_wide_MASS.RDS')
zinc_wide               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/zinc_wide_MASS.RDS')

# process nutrients to remove 0 values
calcium_wide[calcium_wide==0]   <- NA
iron_wide[iron_wide==0]         <- NA
vitamina_wide[vitamina_wide==0] <- NA
zinc_wide[zinc_wide==0]         <- NA

# subset the matrix to only fished species
biomass_index_wide <- cbind(cell = biomass_index_wide[,'cell'], biomass_index_wide[,colnames(biomass_index_wide) %in% fished_genus])
calcium_wide       <- cbind(cell = calcium_wide[,'cell'],       calcium_wide[,colnames(calcium_wide) %in% fished_genus])
iron_wide          <- cbind(cell = iron_wide[,'cell'],          iron_wide[,colnames(iron_wide) %in% fished_genus])
vitamina_wide      <- cbind(cell = vitamina_wide[,'cell'],      vitamina_wide[,colnames(vitamina_wide) %in% fished_genus])
zinc_wide          <- cbind(cell = zinc_wide[,'cell'],          zinc_wide[,colnames(zinc_wide) %in% fished_genus])

# get number of species
n_sdm <- ncol(biomass_index_wide)-1

```


> There are `r n_sdm` species used from the SDMs workflow.


## Summarise properties of the Sea Around Us Data used 

Here we compare the available sea around us data to the species that we also have species distribution models for. 

### Create a dataframe of fished species 

This contains data only at a species level where species are also directly consumed rather than discarded.

```{r}

# obtain the species that contribute the most to direct consumption reported in the SAUP
saup_country_tonnes <- readRDS('processed-data/fisheries-data/saup_country_tonnes.RDS')

# country dataframe of fished species in SAU
saup_country_tonnes_df <- bind_rows(saup_country_tonnes) %>% 
  filter(rank == 'species', direct_consumption == 1) %>% 
  dplyr::rename(., ISO_3 = iso_3, valid_name_FishBase = species_corrected) %>% 
  dplyr::select(ISO_3, valid_name_FishBase, tonnes) %>% 
  mutate(valid_name_FishBase = gsub(' ', '_', .$valid_name_FishBase)) %>% 
  # select only countries in our subset
  left_join(social %>% dplyr::select(GID_0, ISO_3), .,) %>% 
  unique() %>% 
  na.omit()

# species sum of capture in SAU
saup_sum_tonnes <- bind_rows(saup_country_tonnes) %>% 
  filter(rank == 'species', direct_consumption == 1) %>% 
  group_by(species_corrected) %>% 
  do(sum_tonnes = sum(.$tonnes, na.rm = T)) %>% 
  ungroup() %>% 
  unnest(cols = c(sum_tonnes)) %>% 
  arrange(sum_tonnes, decreasing = T) %>% 
  dplyr::rename(., 'valid_name_FishBase' = 'species_corrected') %>% 
  mutate(valid_name_FishBase = gsub(' ', '_', .$valid_name_FishBase))

# get number of species in our SAU project data
n_sau <- n_distinct(saup_sum_tonnes$valid_name_FishBase)

```

> The sea around us data contains `r n_sau` species in total

### How many species are caught in SAUP in our focal countries?

```{r}

## How many countries report our species as caught
n_countries <- saup_country_tonnes_df %>%  
  filter(valid_name_FishBase %in% keep_species$valid_name_FishBase, 
         GID_0 %in% reef_associated_nations$GID_0) %>% 
  .$GID_0 %>% 
  n_distinct

## How many species are caught in focal countries?
SAUP_final_species <- saup_country_tonnes_df %>%  
  filter(valid_name_FishBase %in% keep_species$valid_name_FishBase, 
         GID_0 %in% reef_associated_nations$GID_0) %>% 
  pull(valid_name_FishBase) %>% 
  unique

# get species in both
n_both <- n_distinct(SAUP_final_species)

```

> There are `r n_both` species that have tonnage information in the SAU from our SDM analysis.

### Calculate what proportion of modelled biomass is available in the focal species that are also in SAU

```{r}

## What is modelled biomass species also available in SAUP
# All species
biomass_sum_kgs <- sum(colSums(biomass_index_wide[,-1], na.rm = T)) / 1000
# Only fished species
fished_sum_kgs <- sum(colSums(biomass_index_wide[,colnames(biomass_index_wide) %in% SAUP_final_species], na.rm = T)) / 1000

# % biomass of focal species available in both
perc_total_biomass_in_fished <- round((fished_sum_kgs / biomass_sum_kgs)*100)

```

### Calculate the total number of our focal species that are reported as caught in SAU

```{r}

# sum of total catch for focal species in SAU
total_tonnes <- saup_country_tonnes_df %>%  
  filter(valid_name_FishBase %in% colnames(biomass_index_wide), 
         valid_name_FishBase %in% keep_species$valid_name_FishBase, 
         GID_0 %in% reef_associated_nations$GID_0) %>% 
  do(sum_tonnes_total = sum(.$tonnes, na.rm = T)) %>% 
  unnest() %>% 
  .$sum_tonnes_total

```


### What % of total catch tonnage for reef associated countries is not identified to species level 

```{r}

# How much tonnage is reported at the species level for our focal countries
species_level_sau_tonnes <- bind_rows(saup_country_tonnes) %>% 
  filter(rank == 'species') %>% 
  dplyr::rename(., ISO_3 = iso_3, valid_name_FishBase = species_corrected) %>% 
  left_join(social %>% dplyr::select(GID_0, ISO_3), .,) %>% 
  filter(GID_0 %in% reef_associated_nations$GID_0) %>% 
  do(sum_tonnes = sum(.$tonnes, na.rm = T)) %>% 
  unnest()
species_level_sau_tonnes

# How much tonnage is reported above the species level for our focal countries
aboveSpecies_level_sau_tonnes <- bind_rows(saup_country_tonnes) %>% 
  filter(rank != 'species') %>% 
  dplyr::rename(., ISO_3 = iso_3, valid_name_FishBase = species_corrected) %>% 
  left_join(social %>% dplyr::select(GID_0, ISO_3), .,) %>% 
  filter(GID_0 %in% reef_associated_nations$GID_0) %>% 
  do(sum_tonnes = sum(.$tonnes, na.rm = T)) %>% 
  unnest()
aboveSpecies_level_sau_tonnes

# what percentage is not reported at species level
percentage_tonnes_at_species_level <- round(aboveSpecies_level_sau_tonnes / (species_level_sau_tonnes + aboveSpecies_level_sau_tonnes)*100)


```


## Summary statistics for methods of manuscript based on above data

Using the Sea Around Us reconstructed landings data for small-scale fisheries for the `r n_countries` of `r n_distinct(reef_associated_nations$GID_0)` that reported catches, we identified `r n_both` of `r n_sdm` fish species within these countries that had both SDM models and species-level catch tonnage information available for comparison to modelled regional biomass estimates. Although low in number, we expect these focal species to be important biomass sources because they comprise `r perc_total_biomass_in_fished`% of the total global biomass in our models, even though they formed only `r round((n_both/n_sdm)*100)`% of species richness. Additionally, these species totalled `r total_tonnes` million tonnes of catch for direct human consumption...

As such, the reef fishes considered in our analysis form an important food, even though a high level of taxonomic uncertainty and underreporting exists in reef fish catch reporting (Derrick et al. 2023; Pauly & Zeller 2016; Zeller et al. 2015). This is also indicated in our analysis by the `r percentage_tonnes_at_species_level`% of total catch tonnage for the reef-associated countries reported above the species level. 


# Analysis 2: Comparison of catch tonnage and micronutrient availability predicted from SDMs and SBMs

Here we reproduce Figure 1 showing the relationship between catch tonnage and the predicted micronutrients. We also create the correlation values that provide insets to Figure 1. Here, the RDA values are based on species level properties but not the SDM outputs, whereas the micronutrient mass values are from our SDM and SBM modelling pipeline (i.e., local cell biomass prediction). 

### Read in and pre-process nutrient data

```{r}

# convert name for ease of matching
nuts$valid_name_FishBase <- gsub(' ','_',nuts$valid_name_FishBase)

# select only those species in our final analysis
nuts_2 <- nuts %>% filter(valid_name_FishBase %in% fished_genus)

# convert nutrients to % RDA
nuts_2$Calcium_mu   <- (nuts_2$Calcium_mu   / 700) * 100
nuts_2$Iron_mu      <- (nuts_2$Iron_mu      / 7)   * 100
nuts_2$Vitamin_A_mu <- (nuts_2$Vitamin_A_mu / 300) * 100
nuts_2$Zinc_mu      <- (nuts_2$Zinc_mu      / 3)   * 100

# join together data on tonnage and data on nutrient contents
nuts_country_tonnes <- left_join(saup_country_tonnes_df, nuts_2) %>% 
  filter(valid_name_FishBase %in% names(biomass_index_wide)) %>% 
  na.omit() %>% 
  pivot_longer(cols = Calcium_mu:Zinc_mu)

```


# Micronutrient RDA vs SAU tonnes
### Estimate correlation between RDA and tonnage from SAU

```{r}

# calculate correlation per nutrient using spearmans rank
country_RDA_tonnes_cors <- nuts_country_tonnes %>% 
  # select only relevant countries and fishes
  filter(GID_0 %in% reef_associated_nations$GID_0, 
         valid_name_FishBase %in% fished_genus) %>% 
  # group by nutrient and species
  group_by(valid_name_FishBase, name) %>% 
  na.omit() %>% 
  split(., .$name) %>% 
  lapply(., function(x){broom::tidy(cor.test(x$tonnes, 
                                             x$value, 
                                             method = 'spearman'))}) %>% 
  bind_rows

# print
country_RDA_tonnes_cors

# save output to excel
writexl::write_xlsx(country_RDA_tonnes_cors,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_rda_correlations.xlsx')

```


### Estimate linear model to obtain R2 values

```{r}

# Estimate a linear model between the mean country values
country_RDA_tonnes_lms <- nuts_country_tonnes %>% 
    # select only relevant countries and fishes
  filter(GID_0 %in% reef_associated_nations$GID_0, 
         valid_name_FishBase %in% fished_genus) %>% 
    # group by nutrient and species
  group_by(valid_name_FishBase, name) %>% 
  na.omit() %>% 
  split(., .$name) %>% 
  lapply(., function(x){cbind(broom::tidy(summary(lm(log10(x$tonnes+1) ~ x$value))), 
                              broom::glance(summary(lm(log10(x$tonnes+1) ~ x$value))))}) %>% 
  bind_rows

# print
country_RDA_tonnes_lms

# save output to excel
writexl::write_xlsx(country_RDA_tonnes_lms,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_rda_lm.xlsx')


```



### Plot RDA vs tonnes caught

```{r}
RDA_vs_tonnes <- ggplot(data = nuts_country_tonnes %>% 
         filter(valid_name_FishBase %in% unique(keep_species$valid_name_FishBase), 
                GID_0 %in% reef_associated_nations$GID_0)) + 
  geom_point(aes(y = tonnes, x = value, col = name), pch = 21, alpha = 1) + 
  stat_smooth(aes(y = tonnes, x = value, fill = name), col = 'black', alpha = 0.5, method = 'lm') + 
  scale_colour_manual(values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_fill_manual(values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  theme_bw() +
  facet_wrap(~name, scales = 'free', nrow = 1)  +
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.title = element_blank(), 
        panel.grid = element_blank(), 
        rect = element_rect(fill = "transparent"),
        panel.background = element_rect(fill = 'transparent'),
        aspect.ratio = 1, 
        legend.position = 'none') + 
  xlab('micronutrient RNI per 100g (%)') +
  ylab('tonnes caught') + 
  scale_y_log10(limits = c(NA, max(nuts_country_tonnes$tonnes,na.rm=T)*2), 
                breaks = c(1, 100, 10000))

# print to document
RDA_vs_tonnes

# save for editing in illustrator
png('figures-final-v4/03-nutrient-targetting/RDA-vs-tonnes.png', res = 600, width = 5000, height = 3000, bg = 'transparent')
RDA_vs_tonnes
dev.off()

```



# Micronutrient mass vs SAU tonnes

First we need to process the mass of micronutrients per country per species to then correlate with tonnage caught in SAU data.

```{r}

# Define a function that calculates micronutrient mass per country from the wide site-species nutrient matrix:
# 1. nutrient SDM model frame
# 2. biomass SBM model frame
# 3. conversion factor to grams for each micronutrient
# 4. Name of nutrient
# 5. x = list of country cells for consideration and aggregation over

nutrient_mass_converter <- function(nutrient_matrix, biomass_matrix, nutrient_factor, nutrient_name, x){
  
  # average across nutrients
  nutrient_country_mean <- colMeans(nutrient_matrix[which(nutrient_matrix$cell %in% x),-1]*nutrient_factor, na.rm = T)
  # exclude 0 nutrients
  nutrient_country_mean[nutrient_country_mean==0] <- NA
  # remove species not present
  nutrient_country_mean <- na.omit(nutrient_country_mean)
  # find the cumulative sum of nutrients

  # sum across nutrients
  nutrient_country_sum <- colSums(nutrient_matrix[which(nutrient_matrix$cell %in% x),-1]*nutrient_factor, na.rm = T)
  # exclude 0 nutrients
  nutrient_country_sum[nutrient_country_sum==0] <- NA
  # remove species not present
  nutrient_country_sum <- na.omit(nutrient_country_sum)
  
  # average across biomass
  biomass_country_mean <- colMeans(biomass_matrix[which(biomass_matrix$cell %in% x),-1], na.rm = T)
  # exclude 0 nutrients
  biomass_country_mean[biomass_country_mean==0] <- NA
  # remove species not present
  biomass_country_mean <- na.omit(biomass_country_mean)
  
  # average across biomass
  biomass_country_sum <- colSums(biomass_matrix[which(biomass_matrix$cell %in% x),-1], na.rm = T)
  # exclude 0 nutrients
  biomass_country_sum[biomass_country_sum==0] <- NA
  # remove species not present
  biomass_country_sum <- na.omit(biomass_country_sum)
  
  # convert into dataframe
  nutrient_country_df <- data.frame(mean_nutrient_yield = nutrient_country_mean, 
                                    sum_nutrient_yield = nutrient_country_sum,
                                    mean_biomass = biomass_country_mean, 
                                    sum_biomass  = biomass_country_sum)
  
  # get species names
  nutrient_country_df$valid_name_FishBase <- rownames(nutrient_country_df)
  # assigned fished categories
  nutrient_country_df$fished <- ifelse(nutrient_country_df$valid_name_FishBase %in% gsub(' ', '_', fished_list$fished_genus), 'fished', 'unfished')
  # give nutrient name
  nutrient_country_df$nutrient = nutrient_name
  return(nutrient_country_df)
  
}


## Extract the nutrient mass per country
# calcium
calcium_country <- bind_rows(lapply(country_cells, function(x) nutrient_mass_converter(calcium_wide, biomass_index_wide, 0.001, 'Calcium', x = x)), .id = 'GID_0')

# iron
iron_country <- bind_rows(lapply(country_cells, function(x) nutrient_mass_converter(iron_wide, biomass_index_wide, 0.001, 'Iron', x = x)), .id = 'GID_0')

# vitamin A
vitamina_country <- bind_rows(lapply(country_cells, function(x) nutrient_mass_converter(vitamina_wide, biomass_index_wide, 0.000001, 'Vitamin A', x = x)), .id = 'GID_0')

# zinc
zinc_country <- bind_rows(lapply(country_cells, function(x) nutrient_mass_converter(zinc_wide, biomass_index_wide, 0.001, 'Zinc', x = x)), .id = 'GID_0')

## head one as a example
head(as_tibble(calcium_country))

```

### Process combined nutrient mass data
```{r}

# bind together all outputs at nutrient level
all_nutrients_country <- bind_rows(calcium_country, iron_country, vitamina_country, zinc_country)

# join in tonnage information for country by species
all_nutrients_final <- left_join(all_nutrients_country, 
                                 saup_country_tonnes_df %>% dplyr::select(-ISO_3))

# select only our forcal species and focal countries
all_nutrients_subset <- all_nutrients_final %>% 
  filter(GID_0 %in% reef_associated_nations$GID_0, 
         !is.na(tonnes), 
         valid_name_FishBase %in% fished_genus)

```

### Calculate correlations between micronutrient mass and tonnes caught

```{r}

## Calculate the correlation between mean tonnage and RDA for species across alll countries. 
country_Nmass_tonnes_cors <- all_nutrients_subset %>% 
  group_by(valid_name_FishBase, nutrient) %>% 
  na.omit() %>% 
  split(., .$nutrient) %>% 
  lapply(., function(x){broom::tidy(cor.test(x$tonnes, 
                                             x$sum_nutrient_yield, 
                                             method = 'spearman'))}) %>% 
  bind_rows

# print for markdown
country_Nmass_tonnes_cors

# save outputs for text in figure
writexl::write_xlsx(country_Nmass_tonnes_cors,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_Nmass_correlations.xlsx')

```

### Calculate linear model between micronutrient mass and tonnes caught

```{r}

## Estimate a linear model between the mean country values
country_Nmass_tonnes_lms <- all_nutrients_subset %>% 
  group_by(valid_name_FishBase, nutrient) %>% 
  do(mean_tonnes = .$tonnes, 
     mean_value  = .$sum_nutrient_yield) %>% 
  unnest() %>% 
  na.omit() %>% 
  split(., .$nutrient) %>% 
  lapply(., function(x){cbind(broom::tidy(summary(lm(log10(x$mean_tonnes+1) ~ log10(x$mean_value+1)))), 
                              broom::glance(summary(lm(log10(x$mean_tonnes+1) ~ log10(x$mean_value+1)))))}) %>% 
  bind_rows

# print for markdown
country_Nmass_tonnes_lms


# write to excel
writexl::write_xlsx(country_Nmass_tonnes_lms,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_Nmass_lm.xlsx')

```

### Plot of nutrient mass vs. tonnes caught

```{r}
nm_vs_tonnes <- ggplot() + 
  geom_point(data = all_nutrients_subset %>% 
               filter(valid_name_FishBase %in% unique(keep_species$valid_name_FishBase), 
                      GID_0 %in% unique(reef_associated_nations$GID_0)), 
             aes(x = sum_nutrient_yield, y = tonnes, col = nutrient), 
             pch = 21, alpha = 1) + 
  stat_smooth(data = all_nutrients_subset %>% 
                filter(valid_name_FishBase %in% unique(keep_species$valid_name_FishBase), 
                       GID_0 %in% unique(reef_associated_nations$GID_0)), 
              aes(x = sum_nutrient_yield, y = tonnes, fill = nutrient), 
             alpha = 0.5, col = 'black', method = 'lm') + 
  scale_colour_manual(values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_fill_manual(values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  theme_bw() +
  facet_wrap(~nutrient, scales = 'free', nrow = 1)  +
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.title = element_blank(), 
        panel.grid = element_blank(), 
        aspect.ratio = 1, 
        legend.position = 'none') + 
  xlab('micronutrient mass (g)') +
  ylab('tonnes caught') + 
  scale_y_log10(breaks = c(1, 100, 10000), 
                limits = c(NA, max(all_nutrients_subset$tonnes,na.rm=T)*2)) +
  scale_x_log10(breaks = c(1e-5, 1e-3, 1e-1, 10), 
                labels = c(1e-5, 1e-3, 1e-1, 10))

# plot here
nm_vs_tonnes 

png('figures-final-v4/03-nutrient-targetting/site-Nmass-vs-tonnes.png', res = 600, width = 5000, height = 3000, bg = 'transparent')
nm_vs_tonnes
dev.off()
```




# Assess correlation of tonnes caught with biomass only object

### Calculate biomass per country from SBMs

```{r}

# biomass country summaries dataframe
biomass_country <- bind_rows(lapply(country_cells, function(x){
  
  # average across biomass
  biomass_country_mean <- colMeans(biomass_index_wide[which(biomass_index_wide$cell %in% x),-1], na.rm = T)
  # exclude 0 nutrients
  biomass_country_mean[biomass_country_mean==0] <- NA
  # remove species not present
  biomass_country_mean <- na.omit(biomass_country_mean)
  
  # average across biomass
  biomass_country_sum <- colSums(biomass_index_wide[which(biomass_index_wide$cell %in% x),-1], na.rm = T)
  # exclude 0 nutrients
  biomass_country_sum[biomass_country_sum==0] <- NA
  # remove species not present
  biomass_country_sum <- na.omit(biomass_country_sum)
  
  # convert into dataframe
  biomass_country_df <- data.frame(mean_biomass = biomass_country_mean, 
                                   sum_biomass  = biomass_country_sum)
  
  # get species names
  biomass_country_df$valid_name_FishBase <- rownames(biomass_country_df)
  # assigned fished categories
  biomass_country_df$fished <- ifelse(biomass_country_df$valid_name_FishBase %in% gsub(' ', '_', fished_list$fished_genus), 'fished', 'unfished')
  return(biomass_country_df)
  
}
), .id = 'GID_0')


```

### Link biomass data with SAU tonnes data

```{r}

# join in tonnage information for country by species
biomass_yield_comparison <- left_join(biomass_country, 
                                      saup_country_tonnes_df %>% dplyr::select(-ISO_3))

# subset to the focal countries and fished species in SAUP
biomass_yield_comparison_subset <- 
  biomass_yield_comparison %>% 
  filter(GID_0 %in% reef_associated_nations$GID_0, 
         !is.na(tonnes), 
         valid_name_FishBase %in% fished_genus)

```


### Calculate correlation between biomass and tonnage

```{r}

# Estimate the correlation between mean tonnage and biomass for species across all countries. 
country_biomass_tonnes_cors <- biomass_yield_comparison_subset %>% 
  na.omit() %>% 
  do(broom::tidy(cor.test(.$tonnes, 
                          .$sum_biomass, method = 'spearman')))

# print for markdown document
country_biomass_tonnes_cors

# write excel
writexl::write_xlsx(country_biomass_tonnes_cors,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_biomass_correlations.xlsx')

```


### Calculate linear model between biomass and tonnage

```{r}

## Estimate a linear model between the mean country values
country_biomass_tonnes_lms <- biomass_yield_comparison_subset %>% 
  na.omit() %>% 
  do(tidy_lm   = broom::tidy(summary(lm(log10(.$tonnes+1) ~ log10(.$sum_biomass+1)))), 
     glance_lm = broom::glance(summary(lm(log10(.$tonnes+1) ~ log10(.$sum_biomass+1))))) %>% 
  unnest()

# print for markdown
country_biomass_tonnes_lms

# write to excel
writexl::write_xlsx(country_biomass_tonnes_lms,  
                    path = 'figures-final-v4/03-nutrient-targetting/country_biomass_lm.xlsx')

```


### Make plot correlating two

```{r}

biomass_tonnes <- ggplot() + 
  geom_point(data = biomass_yield_comparison_subset %>% 
               filter(valid_name_FishBase %in% unique(keep_species$valid_name_FishBase), 
                      GID_0 %in% unique(reef_associated_nations$GID_0)), 
             aes(x = sum_biomass, y = tonnes), 
             col = 'gray50', pch = 21, alpha = 1) + 
  stat_smooth(data = biomass_yield_comparison_subset %>% 
                filter(valid_name_FishBase %in% unique(keep_species$valid_name_FishBase), 
                       GID_0 %in% unique(reef_associated_nations$GID_0)), 
              aes(x = sum_biomass, y = tonnes), 
              alpha = 0.5, col = 'black', method = 'lm') + 
  theme_bw() +
  theme(strip.background = element_blank(), 
        strip.text = element_blank(), 
        legend.title = element_blank(), 
        panel.grid = element_blank(), 
        aspect.ratio = 1, 
        legend.position = 'none') + 
  xlab('local biomass (kg)') +
  ylab('tonnes caught') + 
  scale_y_log10(breaks = c(1, 100, 10000), 
                limits = c(NA, max(biomass_yield_comparison_subset$tonnes,na.rm=T)*2)) +
  scale_x_log10(breaks = c(100000, 1000, 10), 
                labels = c(100000, 1000, 10))

biomass_tonnes


# save as png
png('figures-final-v4/03-nutrient-targetting/site-biomass-vs-tonnes.png', res = 600, width = 6000/3, height = 4000/3)
biomass_tonnes
dev.off()

```


