---
title: "02-optimality-and-selectivity"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Analysis of optimality and selectivity for RDA 

This script reproduces figures 2, 3, and 4

### Read in preamble

```{r load packages, echo = F, results = 'hide'}

my_packages <-  
  c('tidyverse', 'plyr', 'raster', 'sp', 'sf','tmap', 'tmaptools', 'scico', 'ggExtra',
    'factoextra', 'FactoMineR', 'corrplot', 'matrixStats', 'ggrepel', 'GGally', 'ncdf4',
    'scales')
not_installed <- my_packages[!(my_packages %in% installed.packages()[ , 'Package'])]   
if(length(not_installed)) install.packages(not_installed)  
lapply(my_packages, function(x) library(x, character.only = T))

```

Outputs:
```{r}
dir.create('figures-final-v4/05-nutrient-simulation/', recursive = T)
```


Pre-loaded data:
```{r load in data}

# load in preamble containing multiple datasets
load('scripts/results-final/01-main-analysis/preamble.RData')

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

```


Nutrient SDM model data for presence (micronutrient concentrations):
```{r load in micronutrient RNI data}

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

# load in species x site matrix for biomass and nutrients
calcium_wide_RNI            <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/calcium_wide_RNI.RDS')
iron_wide_RNI               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/iron_wide_RNI.RDS')
vitamina_wide_RNI           <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/vitamina_wide_RNI.RDS')
zinc_wide_RNI               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/zinc_wide_RNI.RDS')

# process nutrients to remove 0 values
calcium_wide_RNI[calcium_wide_RNI==0]   <- NA
iron_wide_RNI[iron_wide_RNI==0]         <- NA
vitamina_wide_RNI[vitamina_wide_RNI==0] <- NA
zinc_wide_RNI[zinc_wide_RNI==0]         <- NA

# subset the matrix to only fished species
calcium_wide_RNI       <- cbind(cell = calcium_wide_RNI[,'cell'],       calcium_wide_RNI[,colnames(calcium_wide_RNI) %in% fished_genus])
iron_wide_RNI          <- cbind(cell = iron_wide_RNI[,'cell'],          iron_wide_RNI[,colnames(iron_wide_RNI) %in% fished_genus])
vitamina_wide_RNI      <- cbind(cell = vitamina_wide_RNI[,'cell'],      vitamina_wide_RNI[,colnames(vitamina_wide_RNI) %in% fished_genus])
zinc_wide_RNI          <- cbind(cell = zinc_wide_RNI[,'cell'],          zinc_wide_RNI[,colnames(zinc_wide_RNI) %in% fished_genus])

```

Nutrient SDM model data for biomass and micronutrient mass (micronutrient concentrations):
```{r load in biomass and micronutrient mass data}

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

# load in species x site matrix for biomass and nutrients
biomass_index_wide      <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/biomass_index_wide.RDS')
calcium_wide_MASS            <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/calcium_wide_MASS.RDS')
iron_wide_MASS               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/iron_wide_MASS.RDS')
vitamina_wide_MASS           <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/vitamina_wide_MASS.RDS')
zinc_wide_MASS               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/zinc_wide_MASS.RDS')

# process nutrients to remove 0 values
calcium_wide_MASS[calcium_wide_MASS==0]   <- NA
iron_wide_MASS[iron_wide_MASS==0]         <- NA
vitamina_wide_MASS[vitamina_wide_MASS==0] <- NA
zinc_wide_MASS[zinc_wide_MASS==0]         <- NA

# subset the matrix to only fished species
biomass_index_wide <- cbind(cell = biomass_index_wide[,'cell'], biomass_index_wide[,colnames(biomass_index_wide) %in% fished_genus])
calcium_wide_MASS       <- cbind(cell = calcium_wide_MASS[,'cell'],       calcium_wide_MASS[,colnames(calcium_wide_MASS) %in% fished_genus])
iron_wide_MASS          <- cbind(cell = iron_wide_MASS[,'cell'],          iron_wide_MASS[,colnames(iron_wide_MASS) %in% fished_genus])
vitamina_wide_MASS      <- cbind(cell = vitamina_wide_MASS[,'cell'],      vitamina_wide_MASS[,colnames(vitamina_wide_MASS) %in% fished_genus])
zinc_wide_MASS          <- cbind(cell = zinc_wide_MASS[,'cell'],          zinc_wide_MASS[,colnames(zinc_wide_MASS) %in% fished_genus])

```

Sea around us project data:

```{r}

# finally, obtain the species that contribute the most to direct consumption reported in the SAUP
saup_country_tonnes <- readRDS('processed-data/fisheries-data/saup_country_tonnes.RDS')

# bind together, get the countries of interest, and remove non-fished species
saup_reef_tonnes <- bind_rows(saup_country_tonnes) %>% 
  
  # clean names
  dplyr::rename(., ISO_3 = iso_3, valid_name_FishBase = species_corrected) %>% 
  
  # clean species names to match with site x species nutrient matrix
  mutate(valid_name_FishBase = gsub(' ', '_', .$valid_name_FishBase)) %>% 
  
  # join in social data 
  left_join(social %>% dplyr::select(ISO_3, GID_0), .) %>% 
  
  # filter to focal countries and fishes consumed for direct consumption
  filter(GID_0 %in% reef_associated_nations$GID_0,
         direct_consumption == 1) %>% 
  
  # split by countries to loop over
  split(., .$GID_0)

```

Species nutrient data:

```{r}
# read in the raw specices list information
species_list <- read.csv('processed-data/nutrient-content/Spp_NutrientPred_REEF_FUTURESJune2021.csv')

species_list$valid_name_FishBase <- gsub(' ','_',species_list$valid_name_FishBase)

# keep only valid species 
species_list <- species_list %>% 
  filter(valid_name_FishBase %in% keep_species$valid_name_FishBase, 
         valid_name_FishBase %in% fished_genus)

```


### Convert to Reference Nutrient Intakes (RNI in code) 

Here we convert back to 100g portions (x100) from g, and then convert to proportions of daily reference intakes for each nutrient. 

```{r}

# convert back to per 100g portion
calcium_wide_RNI[,-1]  <- calcium_wide_RNI[,-1]*100
iron_wide_RNI[,-1]     <- iron_wide_RNI[,-1]*100
vitamina_wide_RNI[,-1] <- vitamina_wide_RNI[,-1]*100
zinc_wide_RNI[,-1]     <- zinc_wide_RNI[,-1]*100

# express each as percentage of RNI per species
calcium_wide_RNI[,-1] <- (calcium_wide_RNI[,-1]/700) * 100
iron_wide_RNI[-1] <- (iron_wide_RNI[,-1] / 7) * 100
vitamina_wide_RNI[,-1] <- (vitamina_wide_RNI[,-1] / 300)*100
zinc_wide_RNI[,-1] <- (zinc_wide_RNI[,-1] / 3)*100

```


Combine the species x site nutrient matrix into a list for application of function over.

```{r}

# set up as a list of objects for the later loop to work over
nutrient_list_MASS <- list(calcium_wide  = calcium_wide_MASS, 
                           iron_wide     = iron_wide_MASS, 
                           vitamina_wide = vitamina_wide_MASS, 
                           zinc_wide     = zinc_wide_MASS)


# set up as a list of objects for the later loop to work over
nutrient_list_RNI <- list(calcium_wide = calcium_wide_RNI, 
                      iron_wide        = iron_wide_RNI, 
                      vitamina_wide    = vitamina_wide_RNI, 
                      zinc_wide        = zinc_wide_RNI)

```


## Analyse optimality and selectivity for RNI (micronutrient concentrations per species)

Here we perform our analysis of optimality and selectivity. We loop through each country and assess the species caught, and then the metrics for this fishery compared to the modelled pool of nutrients available in our site x species nutrient matrices. 

```{r, results = 'hide'}

if(!file.exists('figures-final-v4/05-nutrient-simulation/OptimalitySelectivitySave.RData')){

## Create loop across all countries in the SAUP dataset
country_nutrient_simulation_RNI <- list() 
country_species_RNI <- list()

# Run loop across each country
for(i in seq_along(saup_reef_tonnes)){

   # 1. Get the species list for the GID_0 based on the nutrient maps
   test_saup <- saup_reef_tonnes[[i]]
   
   # 2. Get the taxonomic namese of valid species
   test_taxa <- na.omit(unique(c(test_saup$valid_name_FishBase, test_saup$genus, test_saup$family)))
   
   # 3. Read in the species list 
   test_country_fished <- species_list$valid_name_FishBase[which(species_list$valid_name_FishBase %in% test_taxa | 
                                                                 species_list$Genus_FishBase %in% test_taxa)]
   test_country_fished <- gsub(' ', '_', test_country_fished)
   
   # 4. Obtain the country cells that are of interest
   test_country_cells <- country_cells[[which(names(country_cells) %in% unique(test_saup$GID_0))]]
   
   # 5. Loop through each nutrient
   nutrient_output_country <- lapply(nutrient_list_RNI, function(x){
     
     # 5a. Filter the nutrient and nutrients down to the country
     nutrient_country  <- 
       x[which(x[,1] %in% test_country_cells),-1]
     
     biomass_country   <-
       biomass_index_wide[which(x[,1] %in% test_country_cells), -1]
     
     # 5b. Remove species that don't have any occurrences in the countries to make the code later more streamlined
     nutrient_country <- nutrient_country[ , which(colSums(nutrient_country, na.rm = T) != 0)]
     biomass_country  <- biomass_country[ , which(colSums(biomass_country, na.rm = T) != 0)]
     
     # 5c. Filter the nutrient and nutrient information down to the identified potentially fished species (defined above)
     # ensure also that only systems with > 1 fishable species are considered in these simulations
     if(length(which(colnames(nutrient_country) %in% test_country_fished)) < 2){     
       
       # return empty data if < 2 species
       return(data.frame(GID_0 = unique(test_saup$GID_0), 
                         n_fished_species = NA,
                         max_nutrient = NA, 
                         nutrient_trueFished_raw = NA, 
                         nutrient_nullFished_raw = NA, 
                         nutrient_trueFished = NA,
                         nutrient_nullFished = NA, 
                         nutrient_selectivity = NA, 
                         mean_nutrient_selectivity = NA ,
                         sd_nutrient_selectivity = NA, 
                         biomass_trueFished_raw = NA, 
                         biomass_nutrient_optimal = NA))
       
     }
     
     # 5d. Get the fished species
     test_nutrient_trueFished  <- nutrient_country[, which(colnames(nutrient_country) %in% test_country_fished)] 
     test_biomass_trueFished  <- biomass_country[, which(colnames(biomass_country) %in% test_country_fished)] 
     
     # 5e. Get the number of species which are classified as fished
     n_fished_species <- sum(colMeans(test_nutrient_trueFished, na.rm = T) != 0)
     
     # 5f.Get the mean potential of the system when fishing the most RDA species at n_fished_species
     max_nutrient  <- mean(sort(colMeans(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species], na.rm = T)
     optimal_species <- names(sort(colMeans(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species])

     # 5g. Get true values of nutrients for country-specific fished species
     nutrient_trueFished_raw <- mean(apply(test_nutrient_trueFished, 2, function(x){unique(na.omit(x))}), na.rm = T)
     nutrient_trueFished     <- nutrient_trueFished_raw / max_nutrient
     
     # 5h. Get true values of the biomass for country-specific fished species
     biomass_trueFished_raw     <- mean(unlist(test_biomass_trueFished), na.rm = T)
     biomass_nutrient_optimal <- mean(unlist(biomass_country[,optimal_species]), na.rm = T)
     
     # 5i. Get distribution of nutrients considering random sampling of fishes
     nutrient_nullFished_raw  <- sapply(1:999, 
                                        function(x){
                                          mean(
                                            apply(nutrient_country[,sample(seq_along(colnames(nutrient_country)),n_fished_species)],
                                                  2,
                                                  function(x){unique(na.omit(x))}), na.rm = T)})
     
     # 5j. Express null fishes in reference to the maximum nutrients possible
     nutrient_nullFished <- nutrient_nullFished_raw / max_nutrient
     
     # 5k. Output table
     return(data.frame(GID_0 = unique(test_saup$GID_0), 
                       n_fished_species = n_fished_species,
                       max_nutrient = max_nutrient, 
                       nutrient_trueFished_raw = nutrient_trueFished_raw, 
                       nutrient_nullFished_raw = nutrient_nullFished_raw, 
                       nutrient_trueFished = nutrient_trueFished,
                       nutrient_nullFished = nutrient_nullFished, 
                       nutrient_selectivity = nutrient_trueFished - nutrient_nullFished, 
                       mean_nutrient_selectivity = mean(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       sd_nutrient_selectivity   = sd(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       biomass_trueFished_raw = biomass_trueFished_raw, 
                       biomass_nutrient_optimal = biomass_nutrient_optimal))
     
   })
   
   # 6. Bind outputs across nutrients
   country_nutrient_simulation_RNI[[i]] <- bind_rows(nutrient_output_country, .id = 'nutrient')
   
   # 7. Get the coountries fished species list based on our analysis
   country_species_RNI[[i]] <- test_country_fished

}

# combine outputs from the simulation
nutrient_sim_all_RNI <- bind_rows(country_nutrient_simulation_RNI)

}

```


## Analyse optimality and selectivity for mass based nutrient values

Here the key difference from the RDA assessment is that we sum nutrient values for mass rather than taking the mean values.

```{r, results = 'hide'}

if(!file.exists('figures-final-v4/05-nutrient-simulation/OptimalitySelectivitySave.RData')){

## Create loop across all countries in the SAUP dataset
country_nutrient_simulation_MASS <- list() 
country_species_MASS <- list()
for(i in seq_along(saup_reef_tonnes)){

   # 1. Get the species list for the GID_0 based on the nutrient maps
   test_saup <- saup_reef_tonnes[[i]]
   
   # 2. Get the taxonomic namese of valid species
   test_taxa <- na.omit(unique(c(test_saup$valid_name_FishBase, test_saup$genus, test_saup$family)))
   
   # 3. Read in the species list 
   test_country_fished <- species_list$valid_name_FishBase[which(species_list$valid_name_FishBase %in% test_taxa | 
                                                                 species_list$Genus_FishBase %in% test_taxa)]
   test_country_fished <- gsub(' ', '_', test_country_fished)
   
   # 4. Obtain the country cells that are of interest
   test_country_cells <- country_cells[[which(names(country_cells) %in% unique(test_saup$GID_0))]]
   
   # 5. Loop through each nutrient
   nutrient_output_country <- lapply(nutrient_list_MASS, function(x){
     
     # 5a Filter the nutrient and nutrients down to the country
     nutrient_country  <- 
       x[which(x[,1] %in% test_country_cells),-1]
     biomass_country   <- 
       biomass_index_wide[which(x[,1] %in% test_country_cells), -1] 
     
     # 5b. Remove species that don't have any occurrences in the countries to make the code later more streamlined
     nutrient_country <- nutrient_country[ , which(colSums(nutrient_country, na.rm = T) != 0)]
     biomass_country  <- biomass_country[ , which(colSums(biomass_country, na.rm = T) != 0)]
     
     # 5c. Filter the nutrient and nutrient information down to the identified potentially fished species (defined above)
     # ensure also that only systems with > 1 fishable species are considered in these simulations
     if(length(which(colnames(nutrient_country) %in% test_country_fished)) < 2){  
       # Output if species are fewer than 2
       return(data.frame(GID_0 = unique(test_saup$GID_0), 
                         n_fished_species = NA,
                         max_nutrient = NA, 
                         nutrient_trueFished_raw = NA, 
                         nutrient_nullFished_raw = NA, 
                         nutrient_trueFished = NA,
                         nutrient_nullFished = NA, 
                         nutrient_selectivity = NA, 
                         mean_nutrient_selectivity = NA, 
                         sd_nutrient_selectivity = NA, 
                         biomass_trueFished_raw = NA, 
                         biomass_nutrient_optimal = NA))
       
     }
     
     # 5d. Get the fished species
     test_nutrient_trueFished  <- nutrient_country[, which(colnames(nutrient_country) %in% test_country_fished)] 
     test_biomass_trueFished  <- biomass_country[, which(colnames(biomass_country) %in% test_country_fished)] 
     
     # 5e. Get the number of species which are classified as fished
     n_fished_species <- sum(colSums(test_nutrient_trueFished, na.rm = T) != 0)
     
     # 5f. Get the maximum potential of the system when fished at n_fished_species
     max_nutrient  <- sum(sort(colMeans(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species], na.rm = T)
     optimal_species <- names(sort(colMeans(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species])
     
     # 5g. Get true values of nutrients for country-specific fished species
     nutrient_trueFished_raw  <- sum(colMeans(test_nutrient_trueFished, na.rm = T), na.rm = T) 
     nutrient_trueFished  <- nutrient_trueFished_raw / max_nutrient 
     
     # 5h. Get true values of the biomass for country-specific fished species
     biomass_trueFished_raw   <- mean(unlist(test_biomass_trueFished), na.rm = T)
     biomass_nutrient_optimal <- mean(unlist(biomass_country[,optimal_species]), na.rm = T)
     
     # 5i. Get distribution of random values
     nutrient_nullFished_raw  <- sapply(1:999, 
                                        function(x){
                                          sum(
                                            colMeans(nutrient_country[,sample(seq_along(colnames(nutrient_country)), 
                                                                                n_fished_species)],
                                                     na.rm=T), 
                                            na.rm = T)}
                                        )
     
     # 5j. Calculate randomised fishing as a % of maximum
     nutrient_nullFished  <- nutrient_nullFished_raw / max_nutrient
     
     
     # 5k. Return outputs
     return(data.frame(GID_0 = unique(test_saup$GID_0), 
                       n_fished_species = n_fished_species,
                       max_nutrient = max_nutrient, 
                       nutrient_trueFished_raw = nutrient_trueFished_raw, 
                       nutrient_nullFished_raw = nutrient_nullFished_raw, 
                       nutrient_trueFished = nutrient_trueFished,
                       nutrient_nullFished = nutrient_nullFished, 
                       nutrient_selectivity = nutrient_trueFished - nutrient_nullFished, 
                       mean_nutrient_selectivity = mean(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       sd_nutrient_selectivity = sd(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       biomass_trueFished_raw = biomass_trueFished_raw, 
                       biomass_nutrient_optimal = biomass_nutrient_optimal))
     
   })
   
   # 6. Combine outputs
   country_nutrient_simulation_MASS[[i]] <- bind_rows(nutrient_output_country, .id = 'nutrient')

   # 7. Return country catches
   country_species_MASS[[i]] <- test_country_fished
   
}


# combine outputs from the simulation
nutrient_sim_all_MASS <- bind_rows(country_nutrient_simulation_MASS)

}

```


#### Save image of the nutrient optimality and selectivity runs

Remember, if running with different set up, then delete the old data to recrete new optimality and selectivity simulations.

```{r load in runs of data}

if(!file.exists('figures-final-v4/05-nutrient-simulation/OptimalitySelectivitySave.RData')){
  save.image(file = 'figures-final-v4/05-nutrient-simulation/OptimalitySelectivitySave.RData')
  }else{
  load('figures-final-v4/05-nutrient-simulation/OptimalitySelectivitySave.RData')
  }

saveRDS(nutrient_sim_all_MASS, 'figures-final-v4/05-nutrient-simulation/nutrient_sim_all_MASS.RDS')


```


#### Summary statistics of the simulations
Here we summarise some of the properties of the simulations based on the number of species input, for example, that are relevant in the methods section of the manuscript. 

```{r}

# how  many species per country
country_species_count <- sapply(country_species_RNI, function(x) length(unique(x)))

# number of coutries with more than 2 species
n_countries <- length(country_species_count[!country_species_count<2])

# mean number of species per country
n_sp_per_country <-
  round(mean(country_species_count[!country_species_count<2]))

# sd of number of species per country
sd_sp_per_country <-
  round(sd(country_species_count[!country_species_count<2]))

# min number of species per country
min_sp_per_country <-
  round(min(country_species_count[!country_species_count<2]))

# max number of species per country
max_sp_per_country <-
  round(max(country_species_count[!country_species_count<2]))

```


These investigations were undertaken for `r n_countries` of the 87 reef-associated countries that had more than one species with landings in the Sea Around Us reconstructed catch data. Note that these simulated scenarios occur completely within our modelled system, but using species and congenerics identified as caught in the Sea Around Us data (for the analysed `r n_countries` countries in the Sea Around Us data n_i = `r n_sp_per_country`± `r sd_sp_per_country` with a range of n_i = `r min_sp_per_country` to `r max_sp_per_country` species).


# Create plots for Figure 2 
 
These plots show the optimality gap between maximum nutrients available from 'n' species and those contained in 'n' fished species. 

### RNI for Figure 2

```{r}

# Join in nutrient simulation with social data
nutrient_sim_all_plot_RNI <- left_join(nutrient_sim_all_RNI, social %>% dplyr::select(GID_0, Country_GADM))

# Caclulate nutrient optimality
nutrient_sim_all_plot_RNI$nutrient_optimality <- nutrient_sim_all_plot_RNI$nutrient_trueFished_raw / nutrient_sim_all_plot_RNI$max_nutrient

# Caclulate mean across countries for ordering plots
nutrient_sim_all_plot_RNI <- nutrient_sim_all_plot_RNI %>% 
  group_by(Country_GADM) %>% 
  do(max_nutrient_mean = mean(.$max_nutrient, na.rm = T), 
     fished_nutrient_mean = mean(.$nutrient_trueFished_raw, na.rm = T), 
     optimality_nutrient_mean = mean(.$nutrient_optimality, na.rm = T)) %>% 
  unnest(max_nutrient_mean, 
         fished_nutrient_mean, 
         optimality_nutrient_mean) %>% 
  left_join(nutrient_sim_all_plot_RNI, .)

# Set levels of ordering
levels <- unique(nutrient_sim_all_plot_RNI$Country_GADM[order(nutrient_sim_all_plot_RNI$optimality_nutrient_mean)])

# Set levels of the countries by the mean null differences
nutrient_sim_all_plot_RNI$Country_GADM <- factor(nutrient_sim_all_plot_RNI$Country_GADM, 
                                             levels = levels)

# Join in regions to assign regions to different panels
RDA_optimality_mean <- left_join(nutrient_sim_all_plot_RNI, 
                                 reef_associated_nations %>% dplyr::select(Country_GADM, un.region.name) %>% unique()) %>% 
  dplyr::select(Country_GADM, un.region.name, nutrient, nutrient_optimality, nutrient_trueFished_raw, max_nutrient) %>% 
  unique() %>% 
  na.omit()

# Rename levels
RDA_optimality_mean$Country_GADM <- factor(RDA_optimality_mean$Country_GADM, levels = levels)

```

These investigations were undertaken for `r length(unique(RDA_optimality_mean$Country_GADM))` of the 87 reef-associated countries that had more than one species with landings in the Sea Around Us reconstructed catch data. Note that these simulated scenarios occur completely within our modelled system, but using species and congenerics identified as caught in the Sea Around Us data (for the analysed `r length(unique(RDA_optimality_mean$Country_GADM))` countries in the Sea Around Us data n_i = `r n_sp_per_country`± `r sd_sp_per_country` with a range of n_i = `r min_sp_per_country` to `r max_sp_per_country` species).


### Plot of optimality for RDA

```{r}

RDA_optimality <- ggplot(data = RDA_optimality_mean %>% 
         mutate(nutrient = factor(.$nutrient, 
                                  levels = rev(unique(.$nutrient))))) + 
  geom_bar(aes(y = Country_GADM, 
               x = (nutrient_optimality)*100, 
               fill = nutrient), 
           stat = 'identity',
           alpha = 0.9)  + 
  facet_grid(un.region.name~., scales = "free", space = 'free') + 
  geom_text(data = RDA_optimality_mean %>% dplyr::select(Country_GADM,
                                                         un.region.name, 
                                                         nutrient_optimality) %>% 
              group_by(Country_GADM, un.region.name) %>% 
              do(sum_no = sum(.$nutrient_optimality, na.rm = T)) %>% 
              unnest(cols = c(sum_no)) %>% 
              unique(), 
            aes(x = sum_no*101, 
                y = Country_GADM, 
                label = Country_GADM), 
            hjust = 0, size = 2) +
  geom_vline(aes(xintercept = 400), lty = 2) + 
  scale_fill_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) +    
  theme_bw() + 
  theme(#strip.text = element_blank(), 
        panel.grid = element_blank(), 
        legend.position = 'none', 
        plot.margin = margin(5,5,5,10),
        panel.background = element_blank(), 
        plot.background = element_blank(), 
        panel.border = element_blank(), 
        axis.line.x = element_line(), 
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank()) +
  scale_x_continuous(lim = c(0,400), labels = paste0(c(0, 100, 200, 300, 400), '%')) +
  xlab('Combined nutrient RNI optimality')+ 
  ylab(NULL)

# Plot for markdown document
RDA_optimality

# Save plot for manuscript
png(filename = 'figures-final-v4/05-nutrient-simulation/RDA-allNutrients_combined-v3.png', 
    width = 1000, height = 2000, res = 300, bg = 'transparent')
RDA_optimality
dev.off()

```



### Micronutrient mass optimality plots for Figure 2

```{r}

# Join with social data
nutrient_sim_all_plot_MASS <- left_join(nutrient_sim_all_MASS, social %>% dplyr::select(GID_0, Country_GADM))

# Calculate optimality
nutrient_sim_all_plot_MASS$nutrient_optimality <- nutrient_sim_all_plot_MASS$nutrient_trueFished_raw / nutrient_sim_all_plot_MASS$max_nutrient

# Aggregate to mean to order plots within regions
nutrient_sim_all_plot_MASS <- nutrient_sim_all_plot_MASS %>% 
  group_by(Country_GADM) %>% 
  do(max_nutrient_mean = mean(.$max_nutrient, na.rm = T), 
     fished_nutrient_mean = mean(.$nutrient_trueFished_raw, na.rm = T), 
     optimality_nutrient_mean = mean(.$nutrient_optimality, na.rm = T)) %>% 
  unnest(max_nutrient_mean, 
         fished_nutrient_mean, 
         optimality_nutrient_mean) %>% 
  left_join(nutrient_sim_all_plot_MASS, .)

# Levels
levels <- unique(nutrient_sim_all_plot_MASS$Country_GADM[order(nutrient_sim_all_plot_MASS$optimality_nutrient_mean)])

# Set levels of the countries by the mean null differences
nutrient_sim_all_plot_MASS$Country_GADM <- factor(nutrient_sim_all_plot_MASS$Country_GADM, 
                                                  levels = levels)

# Join with country data and regions for plotting in different panels
MASS_optimality_mean <- left_join(nutrient_sim_all_plot_MASS, 
                                 reef_associated_nations %>% dplyr::select(Country_GADM, un.region.name) %>% unique()) %>% 
  filter(nutrient != 'biomass_index_wide') %>% 
  dplyr::select(Country_GADM, un.region.name, nutrient, nutrient_optimality, nutrient_trueFished_raw, max_nutrient) %>% 
  unique() %>% 
  na.omit()

# Organise levels
MASS_optimality_mean$Country_GADM <- factor(MASS_optimality_mean$Country_GADM, 
                                           levels = levels)

```

```{r}

# Make optimality plot
MASS_optimality <- ggplot(data = MASS_optimality_mean %>% 
         mutate(nutrient = factor(.$nutrient, 
                                  levels = rev(unique(.$nutrient))))) + 
  geom_bar(aes(y = Country_GADM, 
               x = (nutrient_optimality)*100, 
               fill = nutrient), 
           stat = 'identity',
           alpha = 0.9)  + 
  facet_grid(un.region.name~., scales = "free", space = 'free') + 
  geom_text(data = MASS_optimality_mean %>% dplyr::select(Country_GADM,
                                                         un.region.name, 
                                                         nutrient_optimality) %>% 
              group_by(Country_GADM, un.region.name) %>% 
              do(sum_no = sum(.$nutrient_optimality, na.rm = T)) %>% 
              unnest() %>% 
              unique(), 
            aes(x = sum_no*101, 
                y = Country_GADM, 
                label = Country_GADM), 
            hjust = 0, size = 2) +
  geom_vline(aes(xintercept = 400), lty = 2) + 
  scale_fill_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) +    
  theme_bw() + 
  theme(#strip.text = element_blank(), 
    panel.grid = element_blank(), 
    legend.position = 'none', 
    plot.margin = margin(5,5,5,10),
    panel.background = element_blank(), 
    plot.background = element_blank(), 
    panel.border = element_blank(), 
    axis.line.x = element_line(), 
    axis.ticks.y = element_blank(),
    axis.text.y = element_blank()) +
  scale_x_continuous(lim = c(0,425), labels = paste0(c(0, 100, 200, 300, 400), '%'), 
                     breaks = c(0, 100, 200, 300, 400)) +
  xlab('Combined nutrient mass optimality')+ 
  ylab(NULL)

# Print for markdown
MASS_optimality

# Save mass optimality plot
png(filename = 'figures-final-v4/05-nutrient-simulation/MASS-allNutrients_combined-v3.png', 
    width = 1000, height = 2000, res = 300, bg = 'transparent')
MASS_optimality
dev.off()


```


# Generate percentages and numerical summaries for table 1 results

```{r Generate summary for table 1}

# RNI summary aggregated across all countries 

RNI_all_summary <- nutrient_sim_all_plot_RNI %>% 
  
  # select relevant columns
  dplyr::select(GID_0, nutrient, max_nutrient, nutrient_trueFished_raw, nutrient_nullFished_raw, nutrient_optimality, mean_nutrient_selectivity) %>%
  
  # group by country and nutrient, there are now 999 repetitions per country (downsampling to "n" species per country)
  group_by(GID_0, nutrient) %>% 
  
  # average micronutrient metrics over 999 simulationos
  do(Zmax = mean(.$max_nutrient, na.rm = T), 
     Zfished = mean(.$nutrient_trueFished_raw, na.rm = T),
     Znull = mean(.$nutrient_nullFished_raw, na.rm = T),
     optimality = mean(.$nutrient_optimality, na.rm = T)*100,
     selectivity = mean(.$mean_nutrient_selectivity, na.rm = T)*100) %>% 
  
  # post-process
  unnest() %>% 
  na.omit() %>% 
  ungroup() %>% 
  
  # group by nutrient and take the average values across all countries as well as standard deviation
  group_by(nutrient) %>% 
  do(Zmax = paste0(signif(mean(.$Zmax, na.rm = T),2), ' ± ', signif(sd(.$Zmax, na.rm = T), 2)),
     Zfished = paste0(signif(mean(.$Zfished, na.rm = T),2), ' ± ', signif(sd(.$Zfished, na.rm = T),2)),
     Znull = paste0(signif(mean(.$Znull, na.rm = T),2), ' ± ', signif(sd(.$Znull, na.rm = T),2)),
     optimality = paste0(signif(mean(.$optimality, na.rm = T),2), ' ± ', signif(sd(.$optimality, na.rm = T),2)),
     selectivity = paste0(signif(mean(.$selectivity, na.rm = T),2), ' ± ', signif(sd(.$selectivity, na.rm = T),2))) %>% 
  
  # post-process
  unnest() %>% 
  ungroup() %>% 
  dplyr::rename('Micronutrient' = nutrient) %>% 
  
  # rename for clean table
  mutate(Micronutrient = recode(.$Micronutrient, 
                                'calcium_wide' = 'Calcium (mg)', 
                                'iron_wide' = 'Iron (mg)',
                                'vitamina_wide' = 'Vitamin A (µg)',
                                'zinc_wide' = 'Zinc (mg)'))

# save RNI summary table
writexl::write_xlsx(RNI_all_summary, path = 'figures-final-v4/05-nutrient-simulation/RNI-all-metric-summary.xlsx')

RNI_all_summary


## Micronutrient mass summary aggregated across all countries

MASS_all_summary <- nutrient_sim_all_plot_MASS %>% 
  
  # filter and select relevant columns
  filter(nutrient != 'biomass_index_wide') %>% 
  dplyr::select(GID_0, nutrient, max_nutrient, nutrient_trueFished_raw, nutrient_nullFished_raw, nutrient_optimality, mean_nutrient_selectivity) %>% 
  
  # group by country and nutrient, there are now 999 repetitions per country (downsampling to "n" species per country
  group_by(GID_0, nutrient) %>% 
  
  # average micronutrient metrics over 999 simulationos
  do(Zmax = mean(.$max_nutrient, na.rm = T), 
     Zfished = mean(.$nutrient_trueFished_raw, na.rm = T),
     Znull = mean(.$nutrient_nullFished_raw, na.rm = T),
     optimality = mean(.$nutrient_optimality, na.rm = T)*100,
     selectivity = mean(.$mean_nutrient_selectivity, na.rm = T)*100) %>% 
  
  # post-process
  unnest() %>% 
  na.omit() %>% 
  ungroup() %>% 
  
  # group by nutrient and take the average values across all countries as well as standard deviation
  group_by(nutrient) %>% 
  do(Zmax = paste0(signif(mean(.$Zmax, na.rm = T),2), ' ± ', signif(sd(.$Zmax, na.rm = T), 2)),
     Zfished = paste0(signif(mean(.$Zfished, na.rm = T),2), ' ± ', signif(sd(.$Zfished, na.rm = T),2)),
     Znull = paste0(signif(mean(.$Znull, na.rm = T),2), ' ± ', signif(sd(.$Znull, na.rm = T),2)),
     optimality = paste0(signif(mean(.$optimality, na.rm = T),2), ' ± ', signif(sd(.$optimality, na.rm = T),2)),
     selectivity = paste0(signif(mean(.$selectivity, na.rm = T),2), ' ± ', signif(sd(.$selectivity, na.rm = T),2))) %>% 
  
  # post-process
  unnest() %>% 
  ungroup() %>% 
  dplyr::rename('Micronutrient' = nutrient) %>% 
  
  # rename for clean table
  mutate(Micronutrient = recode(.$Micronutrient, 
                                'calcium_wide' = 'Calcium (mg)', 
                                'iron_wide' = 'Iron (mg)',
                                'vitamina_wide' = 'Vitamin A (µg)',
                                'zinc_wide' = 'Zinc (mg)')) 

# save MASS summary table
writexl::write_xlsx(MASS_all_summary, path = 'figures-final-v4/05-nutrient-simulation/MASS-all-metric-summary.xlsx')

MASS_all_summary

```



## Optimality summary values for countries in the text 

```{r}

### extract values for countries of interest
RDA_optimality_outliers <- bind_rows(
  # get the high outliers
  RDA_optimality_mean %>% 
    group_by(nutrient) %>% 
    filter(nutrient_optimality > quantile(nutrient_optimality, 0.9, na.rm = T)) %>% 
    mutate(outlier = '>0.9'),
           
  # get the low outliers
  RDA_optimality_mean %>% 
    group_by(nutrient) %>% 
    filter(nutrient_optimality < quantile(nutrient_optimality, 0.1, na.rm = T)) %>% 
    mutate(outlier = '<0.1')) %>% 
  arrange(Country_GADM, nutrient_optimality) %>% 
  mutate(nutrient_optimality = round(nutrient_optimality, 2), 
         nutrient_trueFished_raw = round(nutrient_trueFished_raw), 
         max_nutrient = round(max_nutrient))

write.csv(RDA_optimality_outliers, 'figures-final-v4/05-nutrient-simulation/RNI-optimality-outliers.csv')

# print for manual insertion in manuscript
lookup <- abbreviate(names(RDA_optimality_outliers))

RDA_optimality_outliers %>% 
  dplyr::select(-un.region.name) %>% 
  rename(lookup) %>% 
  print(., n=nrow(.))

```



```{r}

### extract values for countries of interest
MASS_optimality_outliers <- bind_rows(
  # get the high outliers
  MASS_optimality_mean %>% 
    group_by(nutrient) %>% 
    filter(nutrient_optimality > quantile(nutrient_optimality, 0.9, na.rm = T)) %>% 
    mutate(outlier = '>0.9'),
           
  # get the low outliers
  MASS_optimality_mean %>% 
    group_by(nutrient) %>% 
    filter(nutrient_optimality < quantile(nutrient_optimality, 0.1, na.rm = T)) %>% 
    mutate(outlier = '<0.1')) %>% 
  arrange(Country_GADM, nutrient_optimality) %>% 
  mutate(nutrient_optimality = round(nutrient_optimality, 2), 
         nutrient_trueFished_raw = round(nutrient_trueFished_raw), 
         max_nutrient = round(max_nutrient))

write.csv(MASS_optimality_outliers, 'figures-final-v4/05-nutrient-simulation/MASS-optimality-outliers.csv')

# print for manual insertion in manuscript
lookup <- abbreviate(names(MASS_optimality_outliers))

MASS_optimality_outliers %>% 
  dplyr::select(-un.region.name) %>% 
  rename(lookup) %>% 
  print(., n=nrow(.))

```


# Micronutrient selectivity

## Selective for RNI 

```{r}
# join in the country names with gids
selectivity_plotdata_RNI <- left_join(nutrient_sim_all_RNI, social %>% dplyr::select(GID_0, Country_GADM))

# estimate averages across all nutrients for ordering
selectivity_plotdata_RNI <- selectivity_plotdata_RNI %>% 
  group_by(GID_0, nutrient) %>% 
  do(all_nutrient_mean_deviation = mean(.$nutrient_selectivity, na.rm = T)) %>% 
  unnest(all_nutrient_mean_deviation) %>% 
  left_join(selectivity_plotdata_RNI, .) %>% 
  ungroup() %>% 
  group_by(nutrient) %>% 
  nest() %>% 
  mutate(nutrient_selectivity_GID0_mean = purrr::map(data, ~mean(.$nutrient_selectivity, na.rm = T))) %>% 
  unnest(nutrient_selectivity_GID0_mean) %>% 
  unnest(data)

# set levels
levels <- unique(selectivity_plotdata_RNI$Country_GADM[order(selectivity_plotdata_RNI$all_nutrient_mean_deviation)])

# set levels of the countries by the mean null differences
selectivity_plotdata_RNI$Country_GADM <- factor(selectivity_plotdata_RNI$Country_GADM, 
                                             levels = levels)

# make selectivity data
selectivity_plotdata_RNI <- selectivity_plotdata_RNI %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0_mean, all_nutrient_mean_deviation) %>% 
  unique() %>% na.omit() %>% 
  mutate(nutrient_selectivity_globalmean = nutrient_selectivity_GID0_mean*100, 
         nutrient_selectivity_GID0 = all_nutrient_mean_deviation*100) %>% 
  filter(nutrient != 'biomass_index_wide')

# change factor labels
selectivity_plotdata_RNI <- selectivity_plotdata_RNI %>% 
  mutate(nutrient = as.character(factor(.$nutrient, labels = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'))))


# make selectivity plot
selectivity_plot_RNI <- ggplot(data = selectivity_plotdata_RNI) + 
  geom_hline(aes(yintercept = 0), lty = 2) + 
  geom_violin(aes(x = nutrient, y = nutrient_selectivity_GID0, fill = nutrient),  
              draw_quantiles = c(0.25,0.75), alpha = 1) +
  geom_point(aes(x = nutrient, y = nutrient_selectivity_GID0), pch = 1, col = 'black', position = position_jitter(width = 0.05, height = 0)) + 
  geom_violin(aes(x = nutrient, y = nutrient_selectivity_GID0, group = nutrient), 
              col = 'black',fill = 'transparent', draw_quantiles = c(0.5)) + 
  theme_bw() + 
  theme(strip.text = element_blank(), 
        panel.grid = element_blank(), 
        legend.position = 'none', 
        plot.margin = margin(5,5,5,10)) + 
  scale_colour_manual(breaks = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'), 
                      values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_fill_manual(breaks = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  xlab(NULL) + 
  ylab('RNI nutrient selectivity (%)')# + 
 # scale_y_continuous(breaks = seq(-30, 90, 30), limits = c(-30, 90))


# print for markdown
selectivity_plot_RNI
```


```{r, echo = F, results='hide'}
# save as output
png(filename = 'figures-final-v4/05-nutrient-simulation/RDA-nutrient-selectivity-v2.png', 
    width = 1000, height = 1500, res = 300)
selectivity_plot_RNI
dev.off()
```



## Selectivity for micronutrient mass

```{r}

# join in the country names with gids
selectivity_plotdata_MASS <- left_join(nutrient_sim_all_MASS, social %>% dplyr::select(GID_0, Country_GADM))

# estimate averages across all nutrients for ordering
selectivity_plotdata_MASS <- selectivity_plotdata_MASS %>% 
  group_by(GID_0, nutrient) %>% 
  do(all_nutrient_mean_deviation = mean(.$nutrient_selectivity, na.rm = T)) %>% 
  unnest(all_nutrient_mean_deviation) %>% 
  left_join(selectivity_plotdata_MASS, .) %>% 
  ungroup() %>% 
  group_by(nutrient) %>% 
  nest() %>% 
  mutate(nutrient_selectivity_GID0_mean = purrr::map(data, ~mean(.$nutrient_selectivity, na.rm = T))) %>% 
  unnest(nutrient_selectivity_GID0_mean) %>% 
  unnest(data)
  
# set levels
levels <- unique(selectivity_plotdata_MASS$Country_GADM[order(selectivity_plotdata_MASS$all_nutrient_mean_deviation)])

# set levels of the countries by the mean null differences
selectivity_plotdata_MASS$Country_GADM <- factor(selectivity_plotdata_MASS$Country_GADM, 
                                             levels = levels)

# make selectivity data
selectivity_plotdata_MASS <- selectivity_plotdata_MASS %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0_mean, all_nutrient_mean_deviation) %>% 
  unique() %>% na.omit() %>% 
  mutate(nutrient_selectivity_globalmean = nutrient_selectivity_GID0_mean*100, 
         nutrient_selectivity_GID0 = all_nutrient_mean_deviation*100) %>% 
  filter(nutrient != 'biomass_index_wide')

# change labels
selectivity_plotdata_MASS <- selectivity_plotdata_MASS %>% 
  mutate(nutrient = as.character(factor(.$nutrient, labels = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'))))


# country point plots
selectivity_plot_MASS <- ggplot(data = selectivity_plotdata_MASS) + 
  geom_hline(aes(yintercept = 0), lty = 2) + 
  geom_violin(aes(x = nutrient, y = nutrient_selectivity_GID0, fill = nutrient),  
              draw_quantiles = c(0.25,0.75), alpha = 1) +
  geom_point(aes(x = nutrient, y = nutrient_selectivity_GID0), 
             pch = 1, col = 'black', position = position_jitter(width = 0.05, height = 0)) + 
  geom_violin(aes(x = nutrient, y = nutrient_selectivity_GID0, group = nutrient), 
              col = 'black',fill = 'transparent', draw_quantiles = c(0.5)) + 
  theme_bw() + 
  theme(strip.text = element_blank(), 
        panel.grid = element_blank(), 
        legend.position = 'none', 
        plot.margin = margin(5,5,5,10)) + 
  scale_colour_manual(breaks = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'), 
                      values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_fill_manual(breaks = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  xlab(NULL) + 
  ylab('Yield nutrient selectivity (%)') + 
  scale_y_continuous(breaks = seq(-30, 90, 30), limits = c(-30, 90))

# print for markdown
selectivity_plot_MASS

```


```{r, echo = F, results='hide'}
png(filename = 'figures-final-v4/05-nutrient-simulation/MASS-nutrient-selectivity-v2.png', 
    width = 1000, height = 1500, res = 300)
selectivity_plot_MASS
dev.off()
```



# Summarise values for text

## Range of selectivity values for micronutrient RNI

```{r}

# get country values for selectivity based on micronutrient RNI
selectivity_country_RNI <- nutrient_sim_all_plot_RNI %>% 
    na.omit() %>% 
    group_by(nutrient, GID_0) %>% 
    dplyr::select(nutrient, GID_0, nutrient_selectivity) %>% 
    do(mean_sel = mean(.$nutrient_selectivity, na.rm = T)*100) %>%
    unnest() 

# get country values for selectivity based on micronutrient RNI
selectivity_country_MASS <- nutrient_sim_all_plot_MASS %>% 
    na.omit() %>% 
    group_by(nutrient, GID_0) %>% 
    dplyr::select(nutrient, GID_0, nutrient_selectivity) %>% 
    do(mean_sel = mean(.$nutrient_selectivity, na.rm = T)*100) %>%
    unnest() 

```

Text in manuscript:
> Although selectivity was low in general, we found substantial variation between countries, ranging from `r round(min(selectivity_country_RNI$mean_sel, na.rm = T))`% to `r round(max(selectivity_country_RNI$mean_sel, na.rm = T))`% for micronutrient RNI and from `r round(min(selectivity_country_MASS$mean_sel, na.rm = T))`% to `r round(max(selectivity_country_MASS$mean_sel, na.rm = T))`% for micronutrient mass (Figure 3, Table 1). 



## Create excel tables with example countries that are outliers for selectivity

```{r}

### extract RNI selectivity values for countries of interest
RNI_selectivity_outliers <- bind_rows(
  # get the high outliers
  selectivity_plotdata_RNI %>% 
  group_by(nutrient) %>% 
  filter(nutrient_selectivity_GID0 > quantile(nutrient_selectivity_GID0, 0.9, na.rm = T)), 
  # get the low outliers
  selectivity_plotdata_RNI %>% 
    group_by(nutrient) %>% 
    filter(nutrient_selectivity_GID0 < quantile(nutrient_selectivity_GID0, 0.1, na.rm = T))) %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0) %>% 
  arrange(Country_GADM)

write.csv(RNI_selectivity_outliers, 'figures-final-v4/05-nutrient-simulation/RNI-selectivity-outliers.csv')


### extract MASS selectivity values for countries of interest
MASS_selectivity_outliers <- bind_rows(
  # get the high outliers
  selectivity_plotdata_MASS %>% 
  group_by(nutrient) %>% 
  filter(nutrient_selectivity_GID0 > quantile(nutrient_selectivity_GID0, 0.9, na.rm = T)), 
  # get the low outliers
  selectivity_plotdata_MASS %>% 
    group_by(nutrient) %>% 
    filter(nutrient_selectivity_GID0 < quantile(nutrient_selectivity_GID0, 0.1, na.rm = T))) %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0) %>% 
  arrange(Country_GADM)

write.csv(MASS_selectivity_outliers, 'figures-final-v4/05-nutrient-simulation/MASS-selectivity-outliers.csv')

```


# Trade offs in selectivity

## Trades offs for micronutrient RNI selectivity

```{r}
selectivity_tradeoff_RNI <- selectivity_plotdata_RNI %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0) %>% 
  
  # get mean selectivity per country
  group_by(Country_GADM) %>% 
  nest() %>% 
  mutate(mean_selectivity = purrr::map(data, ~mean(.$nutrient_selectivity_GID0, na.rm = T))) %>% 
  unnest() %>% 
  
  # get difference between nutrient and selectivity
  mutate(selectivity_difference =  .$nutrient_selectivity_GID0 - .$mean_selectivity) %>% 
  unnest() %>% 
  
  # estimate the variation in selectivity as the trade off
  group_by(Country_GADM) %>% 
  nest() %>% 
  mutate(selectivity_difference_sd = purrr::map(data, ~sd(.$selectivity_difference, na.rm = T))) %>% 
  unnest() %>% 
  ungroup()

# order countries by variation in selectivity differences
selectivity_tradeoff_RNI <- left_join(selectivity_tradeoff_RNI, 
                                      reef_associated_nations %>%
                                        dplyr::select(Country_GADM, un.region.name))

# set factor levels to the magintude of the trade-off
selectivity_tradeoff_RNI$Country_GADM <- factor(selectivity_tradeoff_RNI$Country_GADM,
                                            levels = unique(
                                              selectivity_tradeoff_RNI$Country_GADM[order(
                                                selectivity_tradeoff_RNI$selectivity_difference_sd
                                                )]))

# join with regions as above

selectivity_tradeoff_plot_RNI <- ggplot(data = selectivity_tradeoff_RNI) + 
  geom_tile(aes(x = nutrient, y = Country_GADM, fill = selectivity_difference)) + 
  geom_text(aes(x = nutrient, y = Country_GADM, label = round(nutrient_selectivity_GID0))) + 
  scale_fill_gradientn(colours = c('#00D1CD', '#00D1CD', 'white', '#ff8a00', '#ff8a00'), 
                       limits = c(-abs(max(selectivity_tradeoff_RNI$selectivity_difference)), 
                                  abs(max(selectivity_tradeoff_RNI$selectivity_difference))), 
                       name = 'selectivity difference') + 
  facet_grid(un.region.name~., scales = "free", space = 'free') + 
  theme_bw() + 
  theme(#strip.text = element_blank(), 
    panel.grid = element_blank(), 
    legend.position = 'none', 
    plot.margin = margin(5,5,5,10),
    panel.background = element_blank(), 
    plot.background = element_blank(), 
    #panel.border = element_blank(), 
    axis.line.x = element_line(), 
    axis.ticks.y = element_blank()) +
  xlab(NULL) + 
  ylab(NULL) + 
  theme(panel.grid = element_blank())

# print for markdown document
selectivity_tradeoff_plot_RNI
```


```{r, results = 'hide', echo = F}
png('figures-final-v4/05-nutrient-simulation/RDA-selectivity-trade-off.png', res = 300, width = 2000*0.8, height = 3000)
selectivity_tradeoff_plot_RNI
dev.off()

```




## Trades offs for micronutrient MASS selectivity


```{r}
selectivity_tradeoff_MASS <- selectivity_plotdata_MASS %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0) %>% 
  
  # get mean selectivity per country
  group_by(Country_GADM) %>% 
  nest() %>% 
  mutate(mean_selectivity = purrr::map(data, ~mean(.$nutrient_selectivity_GID0, na.rm = T))) %>% 
  unnest() %>% 
  
  # get difference between nutrient and selectivity
  mutate(selectivity_difference =  .$nutrient_selectivity_GID0 - .$mean_selectivity) %>% 
  unnest() %>% 
  
  # estimate the variation in selectivity as the trade off
  group_by(Country_GADM) %>% 
  nest() %>% 
  mutate(selectivity_difference_sd = purrr::map(data, ~sd(.$selectivity_difference, na.rm = T))) %>% 
  unnest() %>% 
  ungroup()

# order countries by variation in selectivity differences
selectivity_tradeoff_MASS <- left_join(selectivity_tradeoff_MASS, 
                                      reef_associated_nations %>%
                                        dplyr::select(Country_GADM, un.region.name))

# set factor levels to the magintude of the trade-off
selectivity_tradeoff_MASS$Country_GADM <- factor(selectivity_tradeoff_MASS$Country_GADM,
                                            levels = unique(
                                              selectivity_tradeoff_MASS$Country_GADM[order(
                                                selectivity_tradeoff_MASS$selectivity_difference_sd
                                                )]))

# join with regions as above

selectivity_tradeoff_plot_MASS <- ggplot(data = selectivity_tradeoff_MASS) + 
  geom_tile(aes(x = nutrient, y = Country_GADM, fill = selectivity_difference)) + 
  geom_text(aes(x = nutrient, y = Country_GADM, label = round(nutrient_selectivity_GID0))) + 
  scale_fill_gradientn(colours = c('#00D1CD', '#00D1CD', 'white', '#ff8a00', '#ff8a00'), 
                       limits = c(-abs(max(selectivity_tradeoff_MASS$selectivity_difference)), 
                                  abs(max(selectivity_tradeoff_MASS$selectivity_difference))), 
                       name = 'selectivity difference') + 
  facet_grid(un.region.name~., scales = "free", space = 'free') + 
  theme_bw() + 
  theme(#strip.text = element_blank(), 
    panel.grid = element_blank(), 
    legend.position = 'none', 
    plot.margin = margin(5,5,5,10),
    panel.background = element_blank(), 
    plot.background = element_blank(), 
    #panel.border = element_blank(), 
    axis.line.x = element_line(), 
    axis.ticks.y = element_blank()) +
  xlab(NULL) + 
  ylab(NULL) + 
  theme(panel.grid = element_blank())

# print for markdown document
selectivity_tradeoff_plot_MASS
```


```{r, results = 'hide', echo = F}

png('figures-final-v4/05-nutrient-simulation/MASS-selectivity-trade-off.png', res = 300, width = 2000*0.8, height = 3000)
selectivity_tradeoff_plot_MASS
dev.off()

```


# Assess trade-off in RNI when optimising for biomass and vice-versa

```{r}

png(filename = 'figures-final-v4/05-nutrient-simulation/RDA-optimize-biomass-difference.png', 
        width = 1500, height = 1500, res = 300, bg = 'transparent')
ggplot(data = nutrient_sim_all_plot_RNI %>% 
         dplyr::select(Country_GADM, max_nutrient, nutrient_trueFished_raw, nutrient, biomass_trueFished_raw, biomass_nutrient_optimal) %>% 
         unique() %>% 
         na.omit()) + 
  geom_abline(lty = 2) + 
  geom_point(aes(x = exp(biomass_trueFished_raw), y = exp(biomass_nutrient_optimal), fill = nutrient), 
             pch = 21, size = 2) + 
  stat_smooth(aes(x = exp(biomass_trueFished_raw), y = exp(biomass_nutrient_optimal), fill = nutrient), 
              col = 'black',size = 0.5, method = lm) + 
  scale_fill_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                      values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_colour_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  facet_wrap(~nutrient) + 
  scale_x_log10(limits = c(1,10000), breaks = c(1,10,100,1000,10000)) + 
  scale_y_log10(limits = c(1,10000), breaks = c(1,10,100,1000,10000)) + 
  theme_bw() + 
  theme(strip.text = element_blank(), 
        panel.grid = element_blank(), 
        axis.text.x = element_text(angle = 45, hjust = 1, margin = margin(t = 0, r = 10, b = 0, l = 10, unit = "pt")), 
        legend.position = 'none', 
        plot.margin = margin(5,5,5,10)) + 
  xlab('biomass \n (current fishing practice)') + 
  ylab('biomass \n (nutrient RNI optimised fishing)')
dev.off()

png(filename = 'figures-final-v4/05-nutrient-simulation/MASS-optimize-biomass-difference.png', 
        width = 1500, height = 1500, res = 300, bg = 'transparent')
ggplot(data = nutrient_sim_all_plot_MASS %>% 
         dplyr::select(Country_GADM, max_nutrient, nutrient_trueFished_raw, nutrient, biomass_trueFished_raw, biomass_nutrient_optimal) %>% 
         unique() %>% 
         na.omit()) + 
  geom_abline(lty = 2) + 
  geom_point(aes(x = exp(biomass_trueFished_raw), y = exp(biomass_nutrient_optimal), fill = nutrient), 
             pch = 21, size = 2) + 
  stat_smooth(aes(x = exp(biomass_trueFished_raw), y = exp(biomass_nutrient_optimal), fill = nutrient), 
              col = 'black',size = 0.5, method = lm) + 
  scale_fill_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                      values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  scale_colour_manual(breaks = c('calcium_wide', 'iron_wide', 'vitamina_wide', 'zinc_wide'), 
                    values = c('#00D1CD', '#ff8a00', '#00ad0b', '#FF76C5')) + 
  facet_wrap(~nutrient) + 
  scale_x_log10(limits = c(1,10000), breaks = c(1,10,100,1000,10000)) + 
  scale_y_log10(limits = c(1,10000), breaks = c(1,10,100,1000,10000)) + 
  theme_bw() + 
  theme(strip.text = element_blank(), 
        panel.grid = element_blank(), 
        axis.text.x = element_text(angle = 45, hjust = 1, margin = margin(t = 0, r = 10, b = 0, l = 10, unit = "pt")), 
        legend.position = 'none', 
        plot.margin = margin(5,5,5,10)) + 
  xlab('biomass \n (current fishing practice)') + 
  ylab('biomass \n (nutrient MASS optimised fishing)')
dev.off()

```


