---
title: "02-optimality-and-selectivity"
output: html_document
date: "`r Sys.Date()`"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Analysis of optimality and selectivity for RDA 

This script reproduces figures 2, 3, and 4

### Read in preamble

```{r load packages, echo = F, results = 'hide'}

my_packages <-  
  c('tidyverse', 'plyr', 'raster', 'sp', 'sf','tmap', 'tmaptools', 'scico', 'ggExtra',
    'factoextra', 'FactoMineR', 'corrplot', 'matrixStats', 'ggrepel', 'GGally', 'ncdf4',
    'scales')
not_installed <- my_packages[!(my_packages %in% installed.packages()[ , 'Package'])]   
if(length(not_installed)) install.packages(not_installed)  
lapply(my_packages, function(x) library(x, character.only = T))

```

Outputs:
```{r}
dir.create('figures-final-v4/05-nutrient-simulation/', recursive = T)
```


Pre-loaded data:
```{r load in data}

# load in preamble containing multiple datasets
load('scripts/results-final/01-main-analysis/preamble.RData')

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

```


Nutrient SDM model data for presence (micronutrient concentrations):
```{r load in micronutrient RNI data}

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

# load in species x site matrix for biomass and nutrients
calcium_wide_RNI            <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/calcium_wide_RNI.RDS')
iron_wide_RNI               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/iron_wide_RNI.RDS')
vitamina_wide_RNI           <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/vitamina_wide_RNI.RDS')
zinc_wide_RNI               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/zinc_wide_RNI.RDS')

# process nutrients to remove 0 values
calcium_wide_RNI[calcium_wide_RNI==0]   <- NA
iron_wide_RNI[iron_wide_RNI==0]         <- NA
vitamina_wide_RNI[vitamina_wide_RNI==0] <- NA
zinc_wide_RNI[zinc_wide_RNI==0]         <- NA

# subset the matrix to only fished species
calcium_wide_RNI       <- cbind(cell = calcium_wide_RNI[,'cell'],       calcium_wide_RNI[,colnames(calcium_wide_RNI) %in% fished_genus])
iron_wide_RNI          <- cbind(cell = iron_wide_RNI[,'cell'],          iron_wide_RNI[,colnames(iron_wide_RNI) %in% fished_genus])
vitamina_wide_RNI      <- cbind(cell = vitamina_wide_RNI[,'cell'],      vitamina_wide_RNI[,colnames(vitamina_wide_RNI) %in% fished_genus])
zinc_wide_RNI          <- cbind(cell = zinc_wide_RNI[,'cell'],          zinc_wide_RNI[,colnames(zinc_wide_RNI) %in% fished_genus])

```

Nutrient SDM model data for biomass and micronutrient mass (micronutrient concentrations):
```{r load in biomass and micronutrient mass data}

# subset to fished and non-conservation concern species 
fished_genus <- gsub(' ', '_', fished_list$fished_genus)
fished_genus <- fished_genus[which(fished_genus %in% keep_species$valid_name_FishBase)]

# load in species x site matrix for biomass and nutrients
biomass_index_wide      <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/biomass_index_wide.RDS')
calcium_wide_MASS            <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/calcium_wide_MASS.RDS')
iron_wide_MASS               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/iron_wide_MASS.RDS')
vitamina_wide_MASS           <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/vitamina_wide_MASS.RDS')
zinc_wide_MASS               <- readRDS('processed-models/sdm-run-june2021/final-outputs-QC2024/zinc_wide_MASS.RDS')

# process nutrients to remove 0 values
calcium_wide_MASS[calcium_wide_MASS==0]   <- NA
iron_wide_MASS[iron_wide_MASS==0]         <- NA
vitamina_wide_MASS[vitamina_wide_MASS==0] <- NA
zinc_wide_MASS[zinc_wide_MASS==0]         <- NA

# subset the matrix to only fished species
biomass_index_wide <- cbind(cell = biomass_index_wide[,'cell'], biomass_index_wide[,colnames(biomass_index_wide) %in% fished_genus])
calcium_wide_MASS       <- cbind(cell = calcium_wide_MASS[,'cell'],       calcium_wide_MASS[,colnames(calcium_wide_MASS) %in% fished_genus])
iron_wide_MASS          <- cbind(cell = iron_wide_MASS[,'cell'],          iron_wide_MASS[,colnames(iron_wide_MASS) %in% fished_genus])
vitamina_wide_MASS      <- cbind(cell = vitamina_wide_MASS[,'cell'],      vitamina_wide_MASS[,colnames(vitamina_wide_MASS) %in% fished_genus])
zinc_wide_MASS          <- cbind(cell = zinc_wide_MASS[,'cell'],          zinc_wide_MASS[,colnames(zinc_wide_MASS) %in% fished_genus])

```

Sea around us project data:

```{r}

# finally, obtain the species that contribute the most to direct consumption reported in the SAUP
saup_country_tonnes <- readRDS('processed-data/fisheries-data/saup_country_tonnes.RDS')

# bind together, get the countries of interest, and remove non-fished species
saup_reef_tonnes <- bind_rows(saup_country_tonnes) %>% 
  
  # clean names
  dplyr::rename(., ISO_3 = iso_3, valid_name_FishBase = species_corrected) %>% 
  
  # clean species names to match with site x species nutrient matrix
  mutate(valid_name_FishBase = gsub(' ', '_', .$valid_name_FishBase)) %>% 
  
  # join in social data 
  left_join(social %>% dplyr::select(ISO_3, GID_0), .) %>% 
  
  # filter to focal countries and fishes consumed for direct consumption
  filter(GID_0 %in% reef_associated_nations$GID_0,
         direct_consumption == 1) %>% 
  
  # split by countries to loop over
  split(., .$GID_0)

```

Species nutrient data:

```{r}
# read in the raw specices list information
species_list <- read.csv('processed-data/nutrient-content/Spp_NutrientPred_REEF_FUTURESJune2021.csv')

species_list$valid_name_FishBase <- gsub(' ','_',species_list$valid_name_FishBase)

# keep only valid species 
species_list <- species_list %>% 
  filter(valid_name_FishBase %in% keep_species$valid_name_FishBase, 
         valid_name_FishBase %in% fished_genus)

```


### Convert to Reference Nutrient Intakes (RDA in code) 

Here we convert back to 100g portions (x100) from g, and then convert to proportions of daily reference intakes for each nutrient. 

```{r}

# convert back to per 100g portion
calcium_wide_RNI[,-1]  <- calcium_wide_RNI[,-1]*100
iron_wide_RNI[,-1]     <- iron_wide_RNI[,-1]*100
vitamina_wide_RNI[,-1] <- vitamina_wide_RNI[,-1]*100
zinc_wide_RNI[,-1]     <- zinc_wide_RNI[,-1]*100

# express each as percentage of RNI per species
calcium_wide_RNI[,-1] <- (calcium_wide_RNI[,-1]/700) * 100
iron_wide_RNI[-1] <- (iron_wide_RNI[,-1] / 7) * 100
vitamina_wide_RNI[,-1] <- (vitamina_wide_RNI[,-1] / 300)*100
zinc_wide_RNI[,-1] <- (zinc_wide_RNI[,-1] / 3)*100

```


Combine the species x site nutrient matrix into a list for application of function over.

```{r}

# set up as a list of objects for the later loop to work over
nutrient_list_MASS <- list(calcium_wide  = calcium_wide_MASS, 
                           iron_wide     = iron_wide_MASS, 
                           vitamina_wide = vitamina_wide_MASS, 
                           zinc_wide     = zinc_wide_MASS)


# set up as a list of objects for the later loop to work over
nutrient_list_RNI <- list(calcium_wide = calcium_wide_RNI, 
                      iron_wide        = iron_wide_RNI, 
                      vitamina_wide    = vitamina_wide_RNI, 
                      zinc_wide        = zinc_wide_RNI)

```

# The main aim here is to check if the results would be similar if we aggregate country-scale proxies based on sums rather than means
This is to check a minor comment from reviewer 1.

## Analyse optimality and selectivity for mass based nutrient values

Here the key difference from the RDA assessment is that we sum nutrient values for mass rather than taking the mean values.

```{r, results = 'hide'}

## Create loop across all countries in the SAUP dataset
country_nutrient_simulation_MASS <- list() 
country_species_MASS <- list()
for(i in seq_along(saup_reef_tonnes)){

   # 1. Get the species list for the GID_0 based on the nutrient maps
   test_saup <- saup_reef_tonnes[[i]]
   
   # 2. Get the taxonomic namese of valid species
   test_taxa <- na.omit(unique(c(test_saup$valid_name_FishBase, test_saup$genus, test_saup$family)))
   
   # 3. Read in the species list 
   test_country_fished <- species_list$valid_name_FishBase[which(species_list$valid_name_FishBase %in% test_taxa | 
                                                                 species_list$Genus_FishBase %in% test_taxa)]
   test_country_fished <- gsub(' ', '_', test_country_fished)
   
   # 4. Obtain the country cells that are of interest
   test_country_cells <- country_cells[[which(names(country_cells) %in% unique(test_saup$GID_0))]]
   
   # 5. Loop through each nutrient
   nutrient_output_country <- lapply(nutrient_list_MASS, function(x){
     
     # 5a Filter the nutrient and nutrients down to the country
     nutrient_country  <- 
       x[which(x[,1] %in% test_country_cells),-1]
     biomass_country   <- 
       biomass_index_wide[which(x[,1] %in% test_country_cells), -1] 
     
     # 5b. Remove species that don't have any occurrences in the countries to make the code later more streamlined
     nutrient_country <- nutrient_country[ , which(colSums(nutrient_country, na.rm = T) != 0)]
     biomass_country  <- biomass_country[ , which(colSums(biomass_country, na.rm = T) != 0)]
     
     # 5c. Filter the nutrient and nutrient information down to the identified potentially fished species (defined above)
     # ensure also that only systems with > 1 fishable species are considered in these simulations
     if(length(which(colnames(nutrient_country) %in% test_country_fished)) < 2){  
       # Output if species are fewer than 2
       return(data.frame(GID_0 = unique(test_saup$GID_0), 
                         n_fished_species = NA,
                         max_nutrient = NA, 
                         nutrient_trueFished_raw = NA, 
                         nutrient_nullFished_raw = NA, 
                         nutrient_trueFished = NA,
                         nutrient_nullFished = NA, 
                         nutrient_selectivity = NA, 
                         mean_nutrient_selectivity = NA, 
                         sd_nutrient_selectivity = NA, 
                         biomass_trueFished_raw = NA, 
                         biomass_nutrient_optimal = NA))
       
     }
     
     # 5d. Get the fished species
     test_nutrient_trueFished  <- nutrient_country[, which(colnames(nutrient_country) %in% test_country_fished)] 
     test_biomass_trueFished   <- biomass_country[, which(colnames(biomass_country) %in% test_country_fished)] 
     
     # 5e. Get the number of species which are classified as fished
     n_fished_species <- sum(colSums(test_nutrient_trueFished, na.rm = T) != 0)
     
     # 5f. Get the maximum potential of the system when fished at n_fished_species
     max_nutrient  <- sum(sort(colSums(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species], na.rm = T)
     optimal_species <- names(sort(colSums(nutrient_country, na.rm = T),  decreasing = T)[1:n_fished_species])
     
     # 5g. Get true values of nutrients for country-specific fished species
     nutrient_trueFished_raw  <- sum(colSums(test_nutrient_trueFished, na.rm = T), na.rm = T) 
     nutrient_trueFished  <- nutrient_trueFished_raw / max_nutrient 
     
     # 5h. Get true values of the biomass for country-specific fished species
     biomass_trueFished_raw   <- mean(unlist(test_biomass_trueFished), na.rm = T)
     biomass_nutrient_optimal <- mean(unlist(biomass_country[,optimal_species]), na.rm = T)
     
     # 5i. Get distribution of random values
     nutrient_nullFished_raw  <- sapply(1:999, 
                                        function(x){
                                          sum(
                                            colSums(nutrient_country[,sample(seq_along(colnames(nutrient_country)), 
                                                                                n_fished_species)],
                                                     na.rm=T), 
                                            na.rm = T)}
                                        )
     
     # 5j. Calculate randomised fishing as a % of maximum
     nutrient_nullFished  <- nutrient_nullFished_raw / max_nutrient
     
     
     # 5k. Return outputs
     return(data.frame(GID_0 = unique(test_saup$GID_0), 
                       n_fished_species = n_fished_species,
                       max_nutrient = max_nutrient, 
                       nutrient_trueFished_raw = nutrient_trueFished_raw, 
                       nutrient_nullFished_raw = nutrient_nullFished_raw, 
                       nutrient_trueFished = nutrient_trueFished,
                       nutrient_nullFished = nutrient_nullFished, 
                       nutrient_selectivity = nutrient_trueFished - nutrient_nullFished, 
                       mean_nutrient_selectivity = mean(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       sd_nutrient_selectivity = sd(nutrient_trueFished - nutrient_nullFished, na.rm = T), 
                       biomass_trueFished_raw = biomass_trueFished_raw, 
                       biomass_nutrient_optimal = biomass_nutrient_optimal))
     
   })
   
   # 6. Combine outputs
   country_nutrient_simulation_MASS[[i]] <- bind_rows(nutrient_output_country, .id = 'nutrient')

   # 7. Return country catches
   country_species_MASS[[i]] <- test_country_fished
   
}


# combine outputs from the simulation
nutrient_sim_all_MASS <- bind_rows(country_nutrient_simulation_MASS)

```


#### Save image of the nutrient optimality and selectivity runs

Remember, if running with different set up, then delete the old data to recrete new optimality and selectivity simulations.

```{r load in runs of data}

saveRDS(nutrient_sim_all_MASS, 'figures-final-v4/05-nutrient-simulation/nutrient_sim_all_MASS_AGG.RDS')

```


```{r}

nutrient_sim_all_SUM  <- readRDS('figures-final-v4/05-nutrient-simulation/nutrient_sim_all_MASS_AGG.RDS')
nutrient_sim_all_MEAN <- readRDS('figures-final-v4/05-nutrient-simulation/nutrient_sim_all_MASS.RDS')

```




### Micronutrient mass optimality plots for Figure 2

```{r nutrient mass aggregated by mean average}

# Join with social data
nutrient_sim_all_plot_SUM <- left_join(nutrient_sim_all_SUM, social %>% dplyr::select(GID_0, Country_GADM))

# Calculate optimality
nutrient_sim_all_plot_SUM$nutrient_optimality <- nutrient_sim_all_plot_SUM$nutrient_trueFished_raw / nutrient_sim_all_plot_SUM$max_nutrient

# Aggregate to mean to order plots within regions
nutrient_sim_all_plot_SUM <- nutrient_sim_all_plot_SUM %>% 
  group_by(Country_GADM) %>% 
  do(max_nutrient_mean = mean(.$max_nutrient, na.rm = T), 
     fished_nutrient_mean = mean(.$nutrient_trueFished_raw, na.rm = T), 
     optimality_nutrient_mean = mean(.$nutrient_optimality, na.rm = T)) %>% 
  unnest(max_nutrient_mean, 
         fished_nutrient_mean, 
         optimality_nutrient_mean) %>% 
  left_join(nutrient_sim_all_plot_SUM, .)

# Levels
levels <- unique(nutrient_sim_all_plot_SUM$Country_GADM[order(nutrient_sim_all_plot_SUM$optimality_nutrient_mean)])

# Set levels of the countries by the mean null differences
nutrient_sim_all_plot_SUM$Country_GADM <- factor(nutrient_sim_all_plot_SUM$Country_GADM, 
                                                  levels = levels)



# Join with country data and regions for plotting in different panels
MASS_optimality_mean_SUM <- left_join(nutrient_sim_all_plot_SUM, 
                                 reef_associated_nations %>% dplyr::select(Country_GADM, un.region.name) %>% unique()) %>% 
  filter(nutrient != 'biomass_index_wide') %>% 
  dplyr::select(Country_GADM, un.region.name, nutrient, nutrient_optimality, nutrient_trueFished_raw, max_nutrient) %>% 
  unique() %>% 
  na.omit()

# Organise levels
MASS_optimality_mean_SUM$Country_GADM <- factor(MASS_optimality_mean_SUM$Country_GADM, 
                                           levels = levels)

```

```{r nutrient mass aggregated by sums}

# Join with social data
nutrient_sim_all_plot_MEAN <- left_join(nutrient_sim_all_MEAN, social %>% dplyr::select(GID_0, Country_GADM))

# Calculate optimality
nutrient_sim_all_plot_MEAN$nutrient_optimality <- nutrient_sim_all_plot_MEAN$nutrient_trueFished_raw / nutrient_sim_all_plot_MEAN$max_nutrient

# Aggregate to mean to order plots within regions
nutrient_sim_all_plot_MEAN <- nutrient_sim_all_plot_MEAN %>% 
  group_by(Country_GADM) %>% 
  do(max_nutrient_mean = mean(.$max_nutrient, na.rm = T), 
     fished_nutrient_mean = mean(.$nutrient_trueFished_raw, na.rm = T), 
     optimality_nutrient_mean = mean(.$nutrient_optimality, na.rm = T)) %>% 
  unnest(max_nutrient_mean, 
         fished_nutrient_mean, 
         optimality_nutrient_mean) %>% 
  left_join(nutrient_sim_all_plot_MEAN, .)

# Levels
levels <- unique(nutrient_sim_all_plot_MEAN$Country_GADM[order(nutrient_sim_all_plot_MEAN$optimality_nutrient_mean)])

# Set levels of the countries by the mean null differences
nutrient_sim_all_plot_MEAN$Country_GADM <- factor(nutrient_sim_all_plot_MEAN$Country_GADM, 
                                                  levels = levels)


# Join with country data and regions for plotting in different panels
MASS_optimality_mean_MEAN <- left_join(nutrient_sim_all_plot_MEAN, 
                                 reef_associated_nations %>% dplyr::select(Country_GADM, un.region.name) %>% unique()) %>% 
  filter(nutrient != 'biomass_index_wide') %>% 
  dplyr::select(Country_GADM, un.region.name, nutrient, nutrient_optimality, nutrient_trueFished_raw, max_nutrient) %>% 
  unique() %>% 
  na.omit()

# Organise levels
MASS_optimality_mean_MEAN$Country_GADM <- factor(MASS_optimality_mean_MEAN$Country_GADM, 
                                           levels = levels)

```


Join together outputs and see the correlation between two aggregation types
```{r}

MASS_optim_compare <- left_join(MASS_optimality_mean_MEAN, MASS_optimality_mean_SUM, by = c('Country_GADM', 'nutrient'), suffix = c('.MEAN', '.SUM'))

MASS_optim_compare %>% filter(abs((MASS_optim_compare$nutrient_optimality.MEAN - MASS_optim_compare$nutrient_optimality.SUM)) > 0.01)


ggplot(data = MASS_optim_compare) + 
  geom_point(aes(x = nutrient_optimality.SUM, y = nutrient_optimality.MEAN))

ggplot(data = MASS_optim_compare) + 
  geom_point(aes(x = log10(nutrient_trueFished_raw.SUM), y = log10(nutrient_trueFished_raw.MEAN)))

ggplot(data = MASS_optim_compare) + 
  geom_point(aes(x = log10(max_nutrient.SUM), y = log10(max_nutrient.MEAN)))

ggplot(data = MASS_optim_compare) + 
  geom_point(aes(x = nutrient_optimality.SUM, y = nutrient_optimality.MEAN)) + 
  xlab('Optimality (sum across cells)') + 
  ylab('Optimality (mean across cells)')



```

# Check selectivity results


## Selectivity for micronutrient mass

```{r selectivity when mean averaged of cells in countries}

# join in the country names with gids
selectivity_plotdata_MEAN <- left_join(nutrient_sim_all_MEAN, social %>% dplyr::select(GID_0, Country_GADM))

# estimate averages across all nutrients for ordering
selectivity_plotdata_MEAN <- selectivity_plotdata_MEAN %>% 
  group_by(GID_0, nutrient) %>% 
  do(all_nutrient_mean_deviation = mean(.$nutrient_selectivity, na.rm = T)) %>% 
  unnest(all_nutrient_mean_deviation) %>% 
  left_join(selectivity_plotdata_MEAN, .) %>% 
  ungroup() %>% 
  group_by(nutrient) %>% 
  nest() %>% 
  mutate(nutrient_selectivity_GID0_mean = purrr::map(data, ~mean(.$nutrient_selectivity, na.rm = T))) %>% 
  unnest(nutrient_selectivity_GID0_mean) %>% 
  unnest(data)
  
# set levels
levels <- unique(selectivity_plotdata_MEAN$Country_GADM[order(selectivity_plotdata_MEAN$all_nutrient_mean_deviation)])

# set levels of the countries by the mean null differences
selectivity_plotdata_MEAN$Country_GADM <- factor(selectivity_plotdata_MEAN$Country_GADM, 
                                             levels = levels)

# make selectivity data
selectivity_plotdata_MEAN <- selectivity_plotdata_MEAN %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0_mean, all_nutrient_mean_deviation) %>% 
  unique() %>% na.omit() %>% 
  mutate(nutrient_selectivity_globalmean = nutrient_selectivity_GID0_mean*100, 
         nutrient_selectivity_GID0 = all_nutrient_mean_deviation*100) %>% 
  filter(nutrient != 'biomass_index_wide')

# change labels
selectivity_plotdata_MEAN <- selectivity_plotdata_MEAN %>% 
  mutate(nutrient = as.character(factor(.$nutrient, labels = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'))))

# print for markdown
selectivity_plot_MEAN

```




```{r selectivity when mean averaged of cells in countries}

# join in the country names with gids
selectivity_plotdata_SUM <- left_join(nutrient_sim_all_SUM, social %>% dplyr::select(GID_0, Country_GADM))

# estimate averages across all nutrients for ordering
selectivity_plotdata_SUM <- selectivity_plotdata_SUM %>% 
  group_by(GID_0, nutrient) %>% 
  do(all_nutrient_mean_deviation = mean(.$nutrient_selectivity, na.rm = T)) %>% 
  unnest(all_nutrient_mean_deviation) %>% 
  left_join(selectivity_plotdata_SUM, .) %>% 
  ungroup() %>% 
  group_by(nutrient) %>% 
  nest() %>% 
  mutate(nutrient_selectivity_GID0_mean = purrr::map(data, ~mean(.$nutrient_selectivity, na.rm = T))) %>% 
  unnest(nutrient_selectivity_GID0_mean) %>% 
  unnest(data)
  
# set levels
levels <- unique(selectivity_plotdata_SUM$Country_GADM[order(selectivity_plotdata_SUM$all_nutrient_mean_deviation)])

# set levels of the countries by the mean null differences
selectivity_plotdata_SUM$Country_GADM <- factor(selectivity_plotdata_SUM$Country_GADM, 
                                             levels = levels)

# make selectivity data
selectivity_plotdata_SUM <- selectivity_plotdata_SUM %>% 
  dplyr::select(Country_GADM, nutrient, nutrient_selectivity_GID0_mean, all_nutrient_mean_deviation) %>% 
  unique() %>% na.omit() %>% 
  mutate(nutrient_selectivity_globalmean = nutrient_selectivity_GID0_mean*100, 
         nutrient_selectivity_GID0 = all_nutrient_mean_deviation*100) %>% 
  filter(nutrient != 'biomass_index_wide')

# change labels
selectivity_plotdata_SUM <- selectivity_plotdata_SUM %>% 
  mutate(nutrient = as.character(factor(.$nutrient, labels = c('Calcium', 'Iron', 'Vitamin A', 'Zinc'))))

```

```{r}
cols <- c('Country_GADM', 'nutrient', 'nutrient_selectivity_GID0') 

comp_selectivity <- left_join(selectivity_plotdata_SUM %>% ungroup() %>% select_at(cols) %>% unique(),
          selectivity_plotdata_MEAN %>% ungroup() %>% select_at(cols) %>% unique(), 
          by = c('Country_GADM', 'nutrient'), suffix = c('.SUM', '.MEAN'))

ggplot(data = comp_selectivity) + 
  geom_point(aes(x = nutrient_selectivity_GID0.SUM, y = nutrient_selectivity_GID0.MEAN)) + 
  xlab('Selectivity (sum across cells)') + 
  ylab('Selectivity (mean across cells)')


```





